### 2020-02-11 tex/MO-Ga-G_Dec_28_2019.tex
update

\documentclass[12pt,a4paper]{article} %437
\usepackage{indentfirst}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\makeatletter
\makeatother
\usepackage[brazilian]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{pdflscape}
%\usepackage[dvips]{graphicx, color}
\usepackage{subfigure}
%TCIDATA{OutputFilter=latex2.dll}
%TCIDATA{LastRevised=Friday, February 01, 2008 17:54:39}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}

\setlength\topmargin{-1.5cm} \setlength\oddsidemargin{0.0cm}
\setlength\evensidemargin{0.0cm} \setlength{\textwidth}{16cm}
\setlength{\textheight}{25cm}

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newenvironment{proof}{{\bf Proof:\ \ }}{\qed}
\newcommand{\qed}{\rule{0.5em}{1.5ex}}
\newcommand{\bfg}[1]{\mbox{\boldmath $#1$\unboldmath}}
\newcommand{\dse} {\displaystyle}
\newcommand{\real}{{I\!\!R}}
\newcommand{\zern}{{\bf 0}}
\newcommand{\Cn}{{\bf C}}
\newcommand{\dn}{{\bf d}}
\newcommand{\Dn}{{\bf D}}
\newcommand{\Pn}{{\bf P}}
\newcommand{\xn}{{\bf x}}
\newcommand{\Un}{{\bf U}}
\newcommand{\Kn}{{\bf K}}
\newcommand{\Xn}{{\bf X}}
\newcommand{\Vn}{{\bf V}}
\newcommand{\vn}{{\bf v}}
\newcommand{\bn}{{\bf b}}
\newcommand{\an}{{\bf a}}
\newcommand{\cn}{{\bf c}}
\newcommand{\en}{{\bf e}}
\newcommand{\sn}{{\bf s}}
\newcommand{\Bn}{{\bf B}}
\newcommand{\An}{{\bf A}}
\newcommand{\yn}{{\bf y}}
\newcommand{\Yn}{{\bf Y}}
\newcommand{\Zn}{{\bf Z}}
\newcommand{\zn}{{\bf z}}
\newcommand{\Hn}{{\bf H}}
\newcommand{\Gn}{{\bf G}}
\newcommand{\Mn}{{\bf M}}
\newcommand{\fn}{{\bf f}}
\newcommand{\hn}{{\bf h}}
\newcommand{\In}{{\bf I}}
\newcommand{\Fn}{{\bf F}}
\newcommand{\En}{{\bf E}}
\newcommand{\Jn}{{\bf J}}
\newcommand{\Ln}{{\bf L}}
\newcommand{\mn}{{\bf m}}
\newcommand{\rn}{{\bf r}}
\newcommand{\un}{{\bf u}}
\newcommand{\Rn}{{\bf R}}
\newcommand{\Sn}{{\bf S}}
\newcommand{\Tn}{{\bf T}}
\newcommand{\GLn}{{\bf G \bf L}}
\newcommand{\tn}{{\bf t}}
\newcommand{\alpn}{{\mbox{\boldmath $\alpha$}}}
\newcommand{\epsiln}{{\mbox{\boldmath $\epsilon$}}}
\newcommand{\rhn}{{\mbox{\boldmath $\rho$}}}
\newcommand{\betn}{{\mbox{\boldmath $\beta$}}}
\newcommand{\deltn}{{\mbox{\boldmath $\delta$}}}
\newcommand{\sigmn}{{\mbox{\boldmath $\beta$}}}
\newcommand{\gamn}{{\mbox{\boldmath $\gamma$}}}
\newcommand{\Gamn}{{\mbox{\boldmath $\Gamma$}}}
\newcommand{\lamn}{{\mbox{\boldmath $\lambda$}}}
\newcommand{\Lamn}{{\mbox{\boldmath $\Lambda$}}}
\newcommand{\mun}{{\mbox{\boldmath $\mu$}}}
\newcommand{\etn}{{\mbox{\boldmath $\eta$}}}
\newcommand{\tetn}{{\mbox{\boldmath $\theta$}}}
\newcommand{\Tetn}{{\mbox{\boldmath $\Theta$}}}
\newcommand{\Deltn}{{\mbox{\boldmath $\Delta$}}}
\newcommand{\Phin}{{\mbox{\boldmath $\Phi$}}}
\newcommand{\phin}{{\mbox{\boldmath $\phi$}}}
\newcommand{\Psin}{{\mbox{\boldmath $\Psi$}}}
\newcommand{\psin}{{\mbox{\boldmath $\psi$}}}
\newcommand{\Upin}{{\mbox{\boldmath $\Upsilon$}}}
\newcommand{\upin}{{\mbox{\boldmath $\upsilon$}}}
\newcommand{\Sign}{{\mbox{\boldmath $\Sigma$}}}
\newcommand{\Omegn}{{\mbox{\boldmath $\Omega$}}}
\newcommand{\omegn}{{\mbox{\boldmath $\omega$}}}
\newcommand{\eln}{{\mbox{\boldmath $\ell$}}}
\newcommand{\taun}{{\mbox{\boldmath $\tau$}}}

\hyphenation{ge-ne-ra-ted  hy-per-geo-me-tric  cha-rac-te-ri-ze}

\begin{document}

\begin{center}
\section*{\centerline {A new family of continuous distributions: properties and applications}}
\vspace{0.3in}
{\large Gauss M. Cordeiro$^a$ and Maria do Carmo$^a$}\\
%\vspace{0.3in}
%First Version: 27 July 2010\\
%\vspace{0.1in}
%This Version: 27 January 2011\\
\end{center}

\begin{abstract}\noindent
This article introduces generalized beta-generated (GBG) distributions. Sub-models
include all classical beta-generated, Kumaraswamy-generated and exponentiated
distributions. They are maximum entropy distributions under three intuitive
conditions, which show that the classical beta generator skewness parameters
only control tail entropy and an additional shape parameter is needed to add entropy
to the center of the parent distribution. This parameter controls skewness
without necessarily differentiating tail weights. The GBG class also
has tractable properties: we present various expansions for moments,
generating function and quantiles. The model parameters
are estimated by maximum likelihood and the usefulness of the new class
is illustrated by means of some real data sets.
\end{abstract}

\vspace{0.5in}
\noindent {\bf Key Words}: \\ \\
%\noindent {\bf JEL Codes}: C16, G1 \\ \\
\noindent $^{a}$ Departamento de Estat\'{\i}stica, Universidade Federal de Pernambuco, Brazil.\\
e-mail:\emph{gausscordeiro@de.ufpe.br, maria@de.ufpe.br} \\

\section{Introduction}

There has been an increased interest in developing generalized families of distributions by
introducing additional shape parameters to a baseline cumulative distribution. This mechanism has
proved to be useful to make the generated distributions more flexible especially for studying tail properties
than existing distributions and for improving their goodness-of-fit statistics
to the data under study.

Let $G(x)$ be the cumulative distribution function (CDF) of a
baseline distribution and $g(x)=dG(x)/dx$ be the associated
probability density function (PDF) depending on a parameter vectot $\eta$. We present a generalized family
with two additional shape parameters by transforming the CDF $G(x)$
according to two sequential important gene\-rators. These families are important for modeling data
in several engineering areas. Many special distributions in these families are discussed by Tahir
and Nadarajah (2015).

Marshall and Olkin (1997) pioneered a general method to expand
a distribution G by adding an extra shape parameter.
The CDF of their family (for $\theta>0$) is
\begin{equation}\label{CDF_MO}
F_{\text{MO-G}}(x)=\frac{G(x)}{\theta+(1-\theta)G(x)}=\frac{G(x)}{1-(1-\theta)[1-G(x)]},\quad x \in \mathbb{R}.
\end{equation}

The density function corresponding to (\ref{CDF_MO}) is
\begin{equation}\label{densityMO}
f_{\text{MO-G}}(x)=\frac{\theta g(x)}{[\theta+(1-\theta)G(x)]^{2}},\quad x \in \mathbb{R}.
\end{equation}
For $\theta = 1$, $f_{\text{MO-G}}(x)$ is equal to $g(x)$ and, for different values of
$\theta$, $f_{\text{MO-G}}(x)$ can be more flexible than $g(x)$.
The extra parameter $\theta$ is called ``tilt parameter'', since
the HRF of the MO-G family is shifted below ($\theta> 1$)
or above ($0<\theta<1$) of the baseline HRF. Equation \eqref{densityMO} provides a useful
mechanism to generate new distributions from existing ones. The advantage of this approach
for constructing new distributions lies in its flexibility to model
both monotonic and non-monotonic HRFs even when the baseline HRF may be
monotonic. Tahir and Nadarajah (2015, Table 2) presented thirty distributions belonging to
the $\text{MO-G}$ family. Further, this family is easily generated from the baseline QF by
$Q_{\text{MO-G}}(u)=Q_{G}\left(\theta u \left[\theta u+1-u\right]\right)$ for $u\in(0,1)$.

Marshall and Olkin considered the exponential and Weibull distributions for the baseline G and derived some
structural properties of the generated distributions. The special case that G is an exponential distribution
refers to a two-parameter competitive model to the Weibull and gamma distributions.
A simple interpretation of (\ref{CDF_MO}) can be given as follows. Let $T_1,\ldots,T_N$ be a sequence
of independent and identically distributed (i.i.d.)~random variables with survival function (SF)
$\overline{G}(x)=1-G(x)$, and let $N$ be a positive integer
random variable independent of the $T_i$'s defined by the probability generating function (PGF) of a
geometric distribution with parameter $\theta$, say $\tau(z;\theta)=\theta z\,[1-(1-\theta)z]^{-1}$.
Then, the inverse of $\tau(z;\theta)$ becomes $\tau^{-1}(z;\theta)=\tau(z;\theta^{-1})$. We can verify that
equation \eqref{CDF_MO} comes from $1 - F_{\text{MO-G}}(x)=\tau(\overline{G}(x);\theta)$ for $0<\theta<1$ and
$1-F_{\text{MO-G}}(x)=\tau(\overline{G}(x);\theta^{-1})$ for $\theta>1$. For both cases, $1-F_{\text{MO-G}}(x)$
re\-presents the SF of $\min\{T_1,\ldots,T_N\}$, where $N$ has
PGF $\tau(z;\cdot)$ with probability parameters $\theta$ or $\theta^{-1}$.

Zografos and Balakrishnan (2009) and Risti\'{c} and Balakrishnan (2011)
defined the gamma-G ($\Gamma$-G) family with an extra shape parameter $a>0$ by
the CDF (for $x \in \mathbb{R}$)
\begin{eqnarray}\label{CDF_Ga}
F_{\Gamma\text{-G}}(x)=\gamma_1\left( a, -\log \left[1-G(x)\right]\right)
=\frac{\displaystyle 1}{\displaystyle \Gamma(a)}\,\gamma\left( a, -\log \left[1-G(x)\right]\right),
\end{eqnarray}
where $\gamma(a,z)=\int_0^{z} t^{a-1}\,\rm{e}^{-t}dt$ is the incomplete gamma function and
 $\gamma_1(a,z)= \gamma(a,z)/\Gamma(a)$ is the incomplete gamma function ratio.
The PDF of the $\Gamma$-G family takes the form
\begin{eqnarray}\label{PDF_Ga}
\displaystyle
f_{\Gamma\text{-G}}(x)=\frac{\displaystyle 1}{\displaystyle \Gamma(a)} \left\{ -\log[1-G(x)] \right\}^{a-1}\, g(x),
\quad x \in \mathbb{R}.
\end{eqnarray}
Each new $\Gamma$-G distribution can be determined from a given baseline distribution.
For $a=1$, the G distribution is a basic exemplar of the $\Gamma$-G family.

Zografos and Balakrishnan (2009) and Risti\'{c} and Balakrishnan (2011)
presented a physical motivation for the $\Gamma$-G family: if $X_{L(1)},\ldots, X_{L(n)}$ are lower record values
from a sequence of independent random variables with common PDF $g (\cdot)$, then the PDF of the $n$th lower
record value has the form (\ref{PDF_Ga}). If $Z$ is a gamma random variable with unit scale
parameter and shape parameter $a>0$, then $X=Q_G(1-\rm{e}^{Z})$ has density (\ref{PDF_Ga}). So,
the $\Gamma$-G distribution is easily generated from the gamma distribution and the QF of G.

The rest of the paper is organized as follows. Section \ref{sec:MOGaG} describes the distribution and density
of the new class of distributions called the {\it Marshall and Olkin-Gamma-G} (MO-$\Gamma$-G) family  by combining the above generators.
We also present some special models. The maximum likelihood estimation of the model parameters of the new family is
described in Section \ref{estimation}. In Section \ref{applications}, we provide some empirical applications to illustrate
the potentiality of the proposed family. A variety of theoretical properties are considered in Section \ref{properties}.
Finally, conclusions are noted in Section \ref{conclusions}.

\section{The New Family}\label{sec:MOGaG}

Let $X\sim$MO-$\Gamma$-G denote a random variable having the MO-$\Gamma$-G family with two extra shape parameters $\theta>0$ and $a>0$
and the baseline vector $\eta$. By combining Equations (\ref{CDF_MO}) and (\ref{CDF_Ga}), the CDF of $X$ has the form
\begin{equation}\label{CDF_MO-Gamma-G}
F_{X}(x)=\frac{\gamma_1\left( a, -\log \left[1-G(x)\right]\right)}{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-G(x)\right]\right)},\quad x \in \mathbb{R}.
\end{equation}

By differentiating (\ref{CDF_MO-Gamma-G}), we can write the PDF of $X$ as
\begin{equation}\label{CDF_MO-Gamma-G}
f_{X}(x)=\frac{\theta  \left\{ -\log[1-G(x)] \right\}^{a-1}\, g(x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-G(x)\right]\right)\right\}^{2}},\quad x \in \mathbb{R}.
\end{equation}

\begin{landscape}
\begin{table}[htbp]\label{tabspecial1}
\centering
\begin{tabular}{c|c|c}
\hline
\textbf{Distribution} & \textbf{Baseline CDF} & \textbf{Generated PDF}  \\
\hline
{} & {} & {} \\
\textbf{Normal} &  $G(x)=\Phi(x)$ & $f_{X}(x)=\frac{\theta  \left\{ -\log[1-\Phi(x)] \right\}^{a-1}\, \phi(x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\Phi(x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Logistic} &  $G(x)=\frac{1}{1+\rm{e}^{-x}}$ & $f_{X}(x)=\frac{\theta\,\rm{e}^{-x}\, \left\{ -\log[1-(1+\rm{e}^{-x})^{-1}] \right\}^{a-1}}{\Gamma(a)\,(1+\rm{e}^{-x})^{2}\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-(1+\rm{e}^{-x})^{-1}\right]\right)\right\}^{2}}$\\
{} & {} & {} \\
\hline
\textbf{Gumbel} &  $G(x)=1-\exp(-\rm{e}^x)$ & $f_{X}(x)=\frac{\theta \, \exp(a \,x-  \rm{e}^x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left(a, \rm{e}^{x}\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Log-Normal} &  $G(x)=\Phi(\log x)$ & $f_{X}(x)=\frac{\theta\,\phi(\log x)\,  \left\{ -\log[1-\Phi(\log x)] \right\}^{a-1}}{\Gamma(a)\,x\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\Phi(\log x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Exponential} &  $G(x)=1-\exp(-\lambda x),\,\lambda>0$ & $f_{X}(x)=\frac{\theta\,\lambda^{a}\,x^{(a-1)}\, }{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left(a,\lambda x\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Weibull} &  $G(x)=1-\exp(-(\lambda x)^\gamma),\,\lambda,\gamma>0$ & $f_X(x)=\frac{\theta\,\gamma\lambda^{a\,\gamma}x^{a\,\gamma-1}\exp\{-(\lambda\,\gamma)^\gamma\}}{\Gamma (a)\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x)^\gamma]\}^2}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Gamma} &  $G(x)=\gamma_1(\alpha,\beta x),\,\alpha,\,\beta>0$ & $f_{X}(x)=\frac{\theta\,\beta^{\alpha}\,x^{\alpha-1}\,\rm{e}^{-\beta x}\,\left\{ -\log[1-\gamma_1(\alpha,\beta x)] \right\}^{a-1}}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\gamma_1(\alpha,\beta x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\                                                                                                                                                                                                                                                                           \hline
\textbf{Pareto} &  $G(x)=1-\frac{1}{(1+x)^\nu},\,\nu>0$ & $f_{X}(x)=\frac{\theta \, \rm{e}^{-x}\, \left[\nu\log(1+x)\right]^{a-1}\, g(x)}{\Gamma(a)\,(1+\rm{e}^{-x})^2\,\left\{\theta+(1-\theta)\gamma_1\left( a, \nu\log[1+x]\right)\right\}^{2}}$\\
{} & {} & {} \\
\hline
{} & {} & {} \\
\hline
\end{tabular}
\caption{Special Distributions in the  MO-$\Gamma$-G family.}
($\Phi(x)$ and $\phi(x)$ denote the standard normal distribution and density\\ functions and $\gamma_1(a,z)$ is the incomplete gamma function ratio).
\end{table}
\end{landscape}

Figure \ref{formas} shows the performance of the density and hazard functions of the Marshall-Olkin Gamma Weibull (MO-$\Gamma$-W, for short). Note that this extension of the Weibull distribution provides more flexibility for density and hazard shapes.

\begin{figure}[h!]
\begin{center}
(a)\hspace{3.5cm} (b)\\
\includegraphics[scale=.3]{density.pdf}
\includegraphics[scale=.3]{hazard.pdf}\\
\vspace{-0.5cm}
\caption{(a) Curves for the MO-$\Gamma$-W density; (b) Curves for the MO-$\Gamma$-W hazard;\label{formas}}
\end{center}
\end{figure}

\subsection{Quantile Function}\label{QuantFunc}

We can easily invert the cdf \eqref{CDF_MO-Gamma-G} to express the MOGa-G
quantile function (qf), say $x=Q_{X}(u)=G^{-1}(u)$, in terms of the baseline 
qf $Q_G(u)$. Let $u$ be a uniform $U(0,1)$ random variate. By using \eqref{CDF_MO-Gamma-G}
and letting $z=\gamma_{1}\left(a, -\log[1-G(x)]\right)$, we obtain $z=z(u)=\theta u/[1-(1-\theta)u]$. 
Then, the qf of $X$ has the form $x=Q_G\left(1-\rm{e}^{-v}\right)$, where $v=v(z)$ is a random variate generated
from a gamma distribution (with shape parameter $\alpha$ and unit scale parameter) corresponding to the quantile $z$. 
This scheme is useful because of the existence of fast generators for uniform and gamma 
random variables.

\section{Estimation}\label{estimation}

The  MO-$\Gamma$-G family mentioned previously can be  fitted to real data sets using the {\it AdequacyModel}
package for the {\sf R} statistical computing environment ({\tt https://www.r-project.org/}).
An important advantage of this packa\-ge is that it is not necessary to define
the log-likelihood function and that it computes the maximum likelihood estimates (MLE), their standard errors and the formal statistics
presented in the nest section. We only need to provide the PDF and CDF of the distribution to be fitted to a data set.
This {\it AdequacyModel} package uses the PSO (particle swarm optimization) method obtained by traditional global search approaches
such as the quasi-Newton BFGS, Nelder-Mead and simulated-annealing methods to maximized the log-likelihood function. This
method does not require initial values. More
details are available at {\tt https://rdrr.io/cran/AdequacyModel/}.

Here, we consider estimation of unknown parameters of the MO-$\Gamma$-$G$ distribution by the method of maximum likelihood. If $x$ is one observation from \ref{} and $\etn$ a q-vector parameter vector specifying $G(.)$, thus the log-likelihood function, say $\log L=\log L(a,\theta,\etn)$ is
\begin{align}\ell (\boldsymbol{\Theta})=&\,n\log (\theta)+n\log(\gamma)+n\, a\, \gamma \log(\lambda)+(a\gamma-1)\sum_{i=1}^n{\log(x_i)}-\lambda^\gamma\sum_{i=1}^n{\log(x_i)}-n\log[\Gamma(a)] \nonumber \\ & -2\sum_{i=1}^n{\log\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x_i)^\gamma]\}}
\end{align}

\section{Applications}\label{applications}

In this section, we provide two applications in order to show the performance of our proposed family with another ones. To do this, we consider the Weibull distribution as baseline and for competitive distributions, we consider: beta-Weibull ($\beta$-W), proposed by Famoye {\it et al.} (2005); Kumaraswamy Weibull (KW-W), see Cordeiro and Nadarajah (2010); Marshall-Olkin Weibull (MO-W), studied by Ahmed {\it et al.} (2017); Marshall-Olkin Extented Weibull (MOE-W), see the family proposed by Cordeiro {\it et al.} (2019)
Exponentiated Weibull (exp-W), introduced by Mudholkar and Srivastava (1993); gamma Weibull (gamma-W), see Cordeiro {\it et al.} (2016) and exponentiated generalized Weibull (EG-W), see Oguntunde {\it et al.} (2015), with $a=1$.

The log-likelihood for the Marshall-Olkin Gamma Weibull (MO-$\Gamma$-W) and considering one observation is given by
\begin{align}
\ell (\boldsymbol{\Theta})=& \log (\theta)+\log (\gamma)+(a\,\gamma)\log (\lambda)+(a\,\gamma-1)\log(x)-(\gamma\, x)^\gamma-\log[\Gamma(a)]\nonumber \\ &-2\log\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x)^\gamma]\}
\end{align}
where $\boldsymbol{\Theta}=(a,\theta,\lambda,\gamma)^T$. Besides that, the components of the score is given by

\begin{equation*}
U_{a}(\boldsymbol{\Theta})=\gamma  \log (\lambda )+\gamma  \log (x)-\psi ^{(0)}(a)-\frac{2\left\{(1-\theta ) A-(1-\theta ) \psi ^{(0)}(a) \gamma_1 \left[a,(x \lambda
   )^{\gamma }\right]\right\}}{\theta\,\Gamma(a)+(1-\theta)\gamma_1\left[a,(x \lambda
   )^{\gamma }\right]},
\end{equation*}

\begin{equation*}
U_{\theta}(\boldsymbol{\Theta})=\frac{1}{\theta}-\frac{2\left\{\Gamma(a)-\gamma_1\left[a,(\lambda\,x)^\gamma\right]\right\}}{\theta\,\Gamma(a)+(1-\theta)\gamma_1\left[a,(\lambda\,x)^\gamma\right]},
\end{equation*}

\begin{equation*}
U_{\lambda}(\boldsymbol{\Theta})=\frac{\gamma }{\lambda }\left[a-(\lambda\,x)^\gamma\right]+\frac{2 \gamma \,\lambda^{-1}(\lambda\,x)^{a\,\gamma} (1-\theta )\exp\{-(\lambda\,x)^\gamma\} }{\theta \,\Gamma(a)+(1-\theta )
   \gamma_1 \left[a,(x \lambda )^{\gamma }\right]}
\end{equation*}
and
\begin{equation*}		
U_{\gamma}\boldsymbol{\Theta}=\frac{1}{\gamma }+a \log (\lambda )+a \log (x)-(\lambda  x)^{\gamma } \log
   (\lambda  x)+\frac{2 (1-\theta )(\lambda 
   x)^{\gamma\,a } \log (\lambda  x)\exp\{-(\lambda  x)^{\gamma }\}  }{\theta \,\Gamma(a)+(1-\theta )
   \gamma_1 \left[a,(x \lambda )^{\gamma }\right]},
\end{equation*}
where
\begin{align*}
A=G_{2,3}^{3,0}\left[(x \lambda )^{\gamma }\Big{|}
\begin{array}{c}
 1,1 \\
 0,0,a \\
\end{array}
\right]+\log \left[(\lambda  x)^{\gamma }\right] \gamma_1 \left[a,(x \lambda )^{\gamma
   }\right].
\end{align*}
where $\psi^{(n)}(x)$ is the $n$-th derivative of the digamma function and
\begin{eqnarray*}
A=\psi^{(0)}(a) - \log\left[(\lambda x)^{\gamma}\right]-G^{3,0}_{2,3}\,\left((\lambda x)^{\gamma} \Big{|}	\stackrel{1,1}{0,0,a}\right),
\end{eqnarray*}
where $G^{m,n}_{p,q}\,\left(z \Big{|}	\stackrel{a_{1},\ldots,a_{p}}{b_{1},\ldots,b_{q}}\right)$ is the Meijer G function.%exp-W Mudholkar, G. S. and Srivastava, D. K. (1993). Exponentiatel Weibull family for analyzing bathtub failure-rate data. {\it IEEE Transactions on Reliability}, {\bf 42}, 299--302.

% kw-w Codeiro, G. M. and Nadarajah, S. (2010). The Kumaraswamy Weibull distribution with application to failure data. {\it Journal of the Franklin Institute}, {\bf 347}, 1399--1429.

%MO-W Ahmed, H. H., Bdair, O. M. and Ahsanullah, M. (2017). On Marshall-Olkin Extended Weibull distribution. {\it Journal of Statistical Theory and Methods}, {\bf 16}, 1--17.

%VER GAMMA WEIBULL (REFERENCIA MEU TRABALHO GAMMA EXTENDED WEIBULL CNO Journal of Statistical Distributions and Applications)

%EG-W Oguntunde, P. E., Odetunmibi, O. A. and Adejumo, A. O. (2015). On the Exponentiated Generalized Weibull Distribution: A Generalized of the Weibull Distribution. {\it Indian Journal of Science and Technology}, {\bf 8}, 1--7.

To provide the results, in this section we use the {\sf R} software. In order to adjust the data sets consider here, we use the {\it AdequacyModel} package mentioned in Section \ref{estimation}. The method used here was the SANN method, that is a variant of simulated annealing (Belisle, 1992). To compare our proposed model with the other ones mentioned above, we use the Anderson Darling (A$^{*}$) and Cramer Von Mises (W$^{*}$) statistics, given by the {\it goodness.fit} function.

For the first data set, we consider a modification of the ``FoodExpenditure'' from the {\it betareg} package in {\sf R} software, that refers  on proportion of income spent on food for a random sample of 38 households in a large US city, according to the package information. Here, we consider the household expenditures for food. The modification is
\begin{eqnarray*}
data = FoodExpenditure_{food} / \#(FoodExpenditure_{food}),
\end{eqnarray*}
where $FoodExpenditure_{food}$ is the random variable about the household expenditures for food and $\#(.)$ indicates the number of observations on the variable in question. The maximum likelihood estimators (MLE's) and their related standard errors (in parenthesis) are given in Table \ref{tab-ex1}. Besides that, the (W$^{*}$) and (A$^{*}$) statistics are described in this table too. The results indicate that the proposed model has better performance than the other ones.

\begin{table}[!htb]
\scriptsize
\center
\caption{  \small Application 1}
\label{tab-ex1}
\begin{tabular}{lcccccc}
\hline\noalign{\smallskip}
Model & $a$ & $\theta$ & $\lambda$ & $\gamma$ &  $W^*$ & $A^*$   \\
\hline \\
 & & & & &  \\
MO-$\Gamma$-W$(a,\theta,\lambda,\gamma)$    &  0.926134 & 1.379664 & 33.323073 & 25.398809 & 0.0339 &  0.2376 \\                            &    (0.02626926) & (0.22381086) & (0.28530971) & (0.08259864)  & & \\

 & & & & &  \\
$\beta-$W$(a,\theta,\lambda,\gamma)$ &   9.92882 &  0.1700880 & 9.759469 & 1.530541  & 0.043567 & 0.2594618\\
                                    &    (0.02908181) & (0.02049663) & ($<$0.0001) & ($<$0.0001)  && \\
                                                                                & & & & &  \\
KW-W$(a,\theta,\lambda,\gamma)$ &    0.04987575 & 99.99989793 &  1.07602954 & 23.40287099 & 1.330915 & 6.742609\\
                                       &    (0.008090352) & (16.225905058) &  (0.003156126) &  (0.014646102) && \\																						 & & & & &  \\
                                       MOE-W$(a,\theta,\lambda,\gamma)$  &  0.1366666 & 2.020436 & 62.72201 & 4.2956659  &0.03541554 & 0.2579222 \\
 & (0.1599182) & ($<$0.0001) &($<$0.0001) & (0.7365535)    &  & \\
                                                                              & & & & &  \\
EGW$(a,b,\lambda,\gamma)$    &  5.6189861421 &  6.1833138579 &  1.2870816760  & 1.3798562942  &  0.03715255 & 0.2518879 \\
& (0.0028147823) & (0.0009807091) & (0.1159810838) & (0.1480747352)    &  & \\
                                                           & & & & &  \\                                                           MO-W$(a,\lambda,\gamma)$  & 0.15920715  & - &  1.58609458  & 4.26713785  &  0.03456333   & 0.257339\\ 
&    (0.07170351) & (-) & (0.13353716) & (0.16650667)  &  & \\

 & & & & &  \\
exp-W$(a,\lambda,\gamma)$   &    6.1102948   & - &   4.4680469 &  1.3858740 &   0.03726684   & 0.2523749 \\
&   (0.4222173) & (-) & (0.3175876) & (0.1677722)   &  & \\

 & & & & &  \\
 gamma-W$(a,\lambda,\gamma)$    & 5.751546  & - &  10.0000 & 1.208773&  0.0879 & 0.6599  \\ 
&  (0.0015006)&  (-)&  (0.0001163185) &(0.00822782)    &  & \\

 & & & & &  \\

%GammaBS$(a,b,\alpha)$     &  1.2354 & 40.4438 &  0.1379 &       & 0.4931 &   2.7656 &  0.3725 & $1.765x10^{-12}$\\
                          %&  ( 0.0025)& ( 14.6913)& (0.0446) &      & &&  && \\
                                                     \hline
\end{tabular}
\end{table}

As a second application, we consider a data set that can be found in http://biostat.mc.vanderbilt.\\
edu/wiki/
Main/DataSets. This data was collected in a pilot study about hypertension in the Dominican Republic
in 1997. The observations are the systolic blood pressure of persons who came to medical clinics in
several villages, for a variety of complaints. The MLEs of the model parameters and standard errors
and the values of the statistics are listed in Table \ref{tab-ex2} for the previous models. Overall, by
comparing the measures of these formal goodness-of-fit statistics, we conclude that the proposed distribution
outperforms all distributions considered in Table \ref{tab-ex2}.

\begin{table}[htb!]
\scriptsize
\center
\caption{  \small Application 2}
\label{tab-ex2}
\begin{tabular}{lcccccc}
\hline\noalign{\smallskip}
Model & $a$ & $\theta$ & $\lambda$ & $\gamma$ &  $W^*$ & $A^*$   \\
\hline
 & & & & &  \\
MO-$\Gamma$-W$(a,\theta,\lambda,\gamma)$    &  9.629304 & 3.640779 & 6.260826 & 12.823429 &0.5093&  2.8076 \\
                                       &    (0.006217876) & (0.182495785) & (0.024446563) & (0.007965221)  && \\

 & & & & &  \\
 $\beta-$W$(a,\theta,\lambda,\gamma)$ &   31.08471 &  47.14636 &   0.01698383 &  2.054037 & 0.7540428 & 4.279418\\
&    (0.01279570) & ($<$0.0001) & (0.00014535) & ($<$0.0001)  && \\

 & & & & &  \\
KW-W$(a,\theta,\lambda,\gamma)$ &   7363.281 & 0.03925762 &  1.467640 &   0.6146940 & 0.5351 & 2.9617\\
                                       &    (0.04194304) & (0.0004194304)& ($<$0.0001)& ($<$0.0001) && \\

 & & & & &  \\
 MOE-W$(a,\theta,\lambda,\gamma)$  &  101.13471834 &  0.42386507  & 0.03095935 &  1.70240332  &1.14418 & 6.644617 \\
                            & (46.782882038) &  (0.100832102) &  (0.003644092) &  (0.168142275)   &  & \\

 & & & & &  \\
 EGW$(a,b,\lambda,\gamma)$    &  0.2351691 &  140.0000 &   0.4576370 &   0.7425738 &  0.8925 & 5.3338 \\
                            & (0.002540837) & (3.278565) & ($<$0.0001) & ($<$0.0001)   &  & \\

 & & & & &  \\
 MO-W$(a,\lambda,\gamma)$  & 173.2139  & - &  0.02125455 &  1.601970  &  1.476088   & 8.58705\\
                                       &    (0.00016394) & (-) & (0.000212794) & (0.0001398109)  &  & \\

 & & & & &  \\
 exp-W$(a,\lambda,\gamma)$   &    69.02916  & - &   0.02405120 & 1.345536 &   0.8899261   & 5.094141 \\
                          &   (0.08389090) & (-) & (0.0002249256) & ($<$0.0001)   &  & \\

 & & & & &  \\
 gamma-W$(a,\lambda,\gamma)$    & 9.11229459   & - &  0.02617729 & 1.74641178 &    0.6227098 & 3.488268  \\ 
                             &  (0.96330688)&  (-)&  (0.00291875) & (0.08030313)     &  & \\

 & & & & &  \\

%GammaBS$(a,b,\alpha)$     &  1.2354 & 40.4438 &  0.1379 &       & 0.4931 &   2.7656 &  0.3725 & $1.765x10^{-12}$\\
                          %&  ( 0.0025)& ( 14.6913)& (0.0446) &      & &&  && \\
                                                    \hline
\end{tabular}
\end{table}

\section{Mathematical properties}\label{properties}

In this section, we present some main mathematical properties for the MO-$\Gamma$-G family
based on a general linear representation for its density given in the next section.

\subsection{Linear Representation}

A linear representation for the PDF the new family defined previously
can be derived using the concept of exponentiated distributions.
For an arbitrary baseline CDF $G(x)$, the exponentiated-G (exp-G)
distribution with parameter $a>0$, has CDF and PDF in the forms
\begin{eqnarray*}
\Pi_a(x)=G(x)^a\qquad\text{and}\qquad\pi_a(x)=a\,g(x)\,G(x)^{a-1},
\end{eqnarray*}
respectively. The properties of the exponentiated distributions have been studied
by many authors in recent years, see Mudholkar and Srivastava (1995) for exponentiated
Weibull, Gupta {\it et al.} (1998) for exponentiated Pareto, Gupta and
Kundu (2001) for exponentiated exponential and Nadarajah and Gupta (2007)
for exponentiated gamma distribution. Tahir and Nadarajah (2015) cited almost
thirty exponentiated distributions in their Table 1.

A linear representation for the PDF of the MO-$\Gamma$-G family in terms of exp-G densities is important
to determine its mathematical properties from those of the exp-G distributions. They can follow from the papers
described below.

First, the MO-G density (\ref{densityMO}) admits the
linear combination  (Barreto-Souza \emph{et al.}, 2013)
\begin{equation*}
f_{\text{MO-G}}(x)
\,=\,
\sum^{\infty}_{i=0}\,w_i^{\text{MO-G}}\,\pi_{i+1}(x),
\label{EXP44}
\end{equation*}
where the coefficients are (for $i=0,1,\ldots$)
\[
w_i^{\text{MO-G}}=w_i^{\text{MO-G}}(\theta) =
\begin{cases}
\dfrac{(-1)^i\,\theta}{(i+1)} \sum\limits^{\infty}_{j=i}\dbinom{j}{i}(j+1) \bar{\theta}^j,& \quad \theta\in (0,1),\\
\theta^{-1} (1-\theta^{-1})^i,& \quad \theta>1,
\end{cases}
\]
and $\bar{\theta}=1-\theta$.

Second, the linear combination for the $\Gamma\text{-G}$ density (\ref{PDF_Ga}) was
derived by Castellares and Lemonte (2015) as
\begin{equation*}\label{EXP33}
f_{\Gamma\text{-G}}(x)\,=\,\sum_{i=0}^\infty w_i^{\Gamma\text{-G}}\,\,\pi_{a+i}(x),
\end{equation*}
where
$$w_i^{\Gamma\text{-G}}=w_i^{\Gamma\text{-G}}(a)=\frac{\varphi_{i}(a)}{(a+i)},$$
\begin{equation*}\label{coeficientes}
\varphi_0(a)=\frac{1}{\Gamma(a)},
\quad\,
\varphi_i(a)=\frac{(a-1)}{\Gamma(a)}\,\psi_{i-1}(i+a-2),\quad i\geq 1,
\end{equation*}
and
$\psi_{i-1}(\cdot)$ are the {\color{green}Stirling polynomials} defined by
\begin{align*}\label{polinomios_ward}
\begin{split}
\psi_{n-1}(x)&=\frac{(-1)^{n-1}}{(n+1)!}\Biggl[H^{n-1}_{n}-\frac{x+2}{n+2}H^{n-2}_{n}
+ \frac{(x+2)(x+3)}{(n+2)(n+3)}H^{n-3}_{n}- \cdots\\
&\qquad+ (-1)^{n-1}\frac{(x+2)(x+3)\cdots(x+n)}{(n+2)(n+3)\cdots(2n)}H^{0}_{n}\Biggr],
\end{split}
\end{align*}
where $H^{m}_{n}$ are positive integers given recursively by
$H^{m}_{n+1}=(2n+1-m)H^{m}_{n} + (n-m+1)H^{m-1}_{n}$, with
$H^0_0=1$, $H^{0}_{n+1}=1\times 3\times 5\times\cdots\times(2n+1)$, $H^{n}_{n+1}=1$.

\section{Conclusions}\label{conclusions}

\section*{References}

\begin{description}

\item
A. Alzaatreh, F. Famoye, C. Lee:
A new method for generating families of continuous distributions.
Metron {\bf 71}(1) 63-79 (2013).

\item
W. Barreto-Souza, A.J. Lemonte, G.M. Cordeiro:
General results for the Marshall and Olkin's family of distributions.
Anais da Academia Brasileira de Ci\^{e}ncias {\bf 85}(1) 3-21 (2013).

\item
Z.W. Birnbaum, S.C. Saunders:
A new family of life distributions.
Journal of Applied Probability {\bf 6}(2) 319-327 (1969).

\item
F. Castellares, A.J. Lemonte:
A new generalized Weibull distribution gene\-rated by gamma random variables.
Journal of the Egyptian Mathematical Society {\bf 23}(2) 382-390 (2015).

\item
G.M. Cordeiro, M. de Castro:
A new family of generalized distributions.
Journal of Statistical Computation and Simulation {\bf 81}(7) 883-898 (2011).

\item
N. Eugene, C. Lee, F. Famoye:
Beta-normal distribution and its applications.
Communications in Statistics -- Theory and Methods {\bf 31}(4) 497-512 (2002).

\item
R.C. Gupta, R.D. Gupta, P.L. Gupta:
Modeling failure time data by Lehmann alternatives.
Communications in Statistics -- Theory and Methods {\bf 27}(4) 887-904 (1998).

\item
R.D. Gupta, D. Kundu:
Exponentiated exponential family: an alternative to gamma and Weibull distributions.
Biometrical Journal {\bf 43}(1) 117-130 (2001).

%\item
%P. Kumaraswamy:
%Generalized probability density-function for double-bounded
%random-processes. Journal of Hydrology {\bf 46}(1-2) 79-88 (1980).

\item
A.J. Lemonte, G.M. Cordeiro, G. Moreno-Arenas:
A new useful three-parameter extension of the exponential distribution.
Statistics {\bf 50}(2) 312-337 (2016).

\item
A.W. Marshall, I. Olkin:
A new method for adding a parameter to a family of distributions with
application to the exponential and Weibull families.
Biometrika {\bf 84}(3) 641-652 (1997).

\item
G.S. Mudholkar, D.K. Srivastava:
The exponentiated Weibull family: a reanalysis of the bus-motor-failure data.
Technometrics {\bf 37}(4) 436-445 (1995).

\item
S. Nadarajah, G.M. Cordeiro, E.M.M. Ortega:
Some general results for the beta-modified Weibull distribution.
Journal of Statistical Computation and Simulation {\bf 81}(10) 1211-1232 (2011).

\item
S. Nadarajah, G.M. Cordeiro, E.M.M. Ortega:
General results for the Kumaraswamy G distribution.
Journal of Statistical Computation and Simulation {\bf 87}(7) 951-979 (2012).

\item
S. Nadarajah, A.K. Gupta:
The exponentiated gamma distribution with application to drought data.
Calcutta Statistical Association Bulletin {\bf 59}(1-2) 29-54 (2007).

\item
S. Nadarajah, F. Haghighi:
An extension of the exponential distribution.
Statistics {\bf 45}(6) 543-558 (2011).

\item
S. Nadarajah, S. Kotz:
The exponentiated-type distributions.
Acta Applicandae Mathematicae {\bf 92}(2) 97-111 (2006).

\item
M.D. Nichols, W.J. Padgett:
A Bootstrap control chart for Weibull percentiles.
Quality and Reliability Engineering International {\bf 22}(2) 141-151 (2006).

\item
F. Proschan:
Theoretical explanation of observed decreasing failure rate.
Technometrics {\bf 5}(3) 375-383 (1963).

\item
M.M. Risti\'{c}, N. Balakrishnan:
The gamma-exponentiated exponential distribution.
Journal of Statistical Computation and Simulation {\bf 82}(8) 1191-1206 (2012).

\item
E.W. Stacy: A Generalization of the Gamma Distribution. Annals of Mathematical Statistics {\bf 33}(3) 1187-1192 (1962).

\item
M.H. Tahir, S. Nadarajah:
Parameter induction in continuous univariate distributions: Well-established G families.
Anais da Academia Brasileira de Ci\^{e}ncias {\bf 87}(2) 539-568 (2015).

\item
K. Zografos, N. Balakrishnan:
On families of beta-and generalized gamma-generated distribution and
associate inference.  Statistical Methodology {\bf 6}(4) 344-362 (2009).

\end{description}

\end{document}

### 2020-02-11 code/new_code_dagum.R
update

@@ -2,11 +2,19 @@
 # Author: Pedro Rafael D. Marinho
 
 # Loading libraries. ------------------------------------------------------
-library(purrr)
+library(parallel)
+library(tibble)
+library(pbmcapply)
+library(magrittr)
 
 # Baseline functions. -----------------------------------------------------
-pdf_w <- function(x, alpha, beta) dweibull(x = x, shape = alpha, scale = beta)
-cdf_w <- function(x, alpha, beta) pweibull(q = x, shape = alpha, scale = beta)
+pdf_dagum <- function(x, alpha, beta, p) 
+  alpha * p / x * (x / beta) ^ (alpha * p) / ((x / beta) ^ alpha + 1) ^ (p + 1)
+# integrate(f = pdf_dagum, lower = 0, upper = Inf, alpha = 1.2, beta = 1.6, p = 2.2)
+
+cdf_dagum <- function(x, alpha, beta, p) 
+  (1 + (x / beta) ^ (-alpha)) ^ (-p)
+# cdf_dagum(x = Inf, alpha = 1, beta = 4, p = 1)
 
 # This function creates MOGG functions. ----------------------------------
 pdf_mogg <- function(g, G){
@@ -20,30 +28,36 @@ pdf_mogg <- function(g, G){
   }
 }
 
-# MOGW --------------------------------------------------------------------
-rmogw <- function(n = 1L, theta, a, alpha, beta){
+rdagum <- function(n = 1L, alpha, beta, p) {
+  beta * (runif(n = n, min = 0, max = 1) ^ (-1 / p) - 1) ^ (-1 / alpha)
+}
+
+pdf_mogdagum <- pdf_mogg(g = pdf_dagum, G = cdf_dagum)
+
+# MOG-Dagum --------------------------------------------------------------------
+rmogdagum <- function(n = 1L, theta, a, alpha, beta, p){
   
-  cond_c <- function(x, theta, a, alpha, beta){
-    num <- pdf_mogw(x, theta, a, alpha, beta)
-    den <- dweibull(x, shape = 1, scale = 1)
-    -num/den
+  cond_c <- function(x, theta, a, alpha, beta, p){
+    num <- pdf_mogdagum(x, theta, a, alpha, beta, p)
+    den <- pdf_dagum(x, alpha = alpha, beta = beta , p = p)
+    -num / den
   }
   
[…]

### 2020-02-11 code/new_code_weibull.R

@@ -33,7 +33,7 @@ rmogw <- function(n = 1L, theta, a, alpha, beta){
                  alpha = alpha, beta = beta)$par
   
   c <- pdf_mogw(x_max, theta, a, alpha, beta)/dweibull(x_max, shape = alpha, scale = beta)
-
+  
   criterion <- function(y, u){
     num <- pdf_mogw(y, theta, a, alpha, beta)
     den <- dweibull(y, shape = alpha, scale = beta)

### 2020-02-11 code/new_code_dagum.R
update

@@ -6,6 +6,7 @@ library(parallel)
 library(tibble)
 library(pbmcapply)
 library(magrittr)
+library(purrr)
 
 # Baseline functions. -----------------------------------------------------
 pdf_dagum <- function(x, alpha, beta, p) 
@@ -149,16 +150,6 @@ mc <- function(n = 250L, M = 1e3L, par_true, method = "BFGS") {
   result
 }
 
-# Sample Size -------------------------------------------------------------
-n <- 10L
-
-# True parameters (theta, a, alpha, beta and p) -------------------------------------
-true_parameters <- c(5, 1, 5, 1, 1)
-
-set.seed(1L, kind = "L'Ecuyer-CMRG")
-result_mc <- mc(n = n, M = 100L, par_true = true_parameters, method = "BFGS")
-mc.reset.stream()
-
 bias_function <- function(x, par_true){
   x - par_true
 }
@@ -167,12 +158,23 @@ mse_function <- function(x, par_true) {
   (x - par_true) ^ 2
 }
 
-# Average Bias of Estimators ----------------------------------------------
-bias <- apply(X = result_mc, MARGIN = 1L, FUN = bias_function, par_true = true_parameters) %>% 
-  apply(MARGIN = 1L, FUN = mean)
-paste0("bias_", n, ".RData") %>% save(file = ., bias)
+simular <- function(n) {
+  # True parameters (theta, a, alpha, beta and p) -------------------------------------
+  true_parameters <- c(1, 1, 1, 1, 1)
+  
+  set.seed(1L, kind = "L'Ecuyer-CMRG")
+  result_mc <- mc(n = n, M = 1e4L, par_true = true_parameters, method = "BFGS")
+  mc.reset.stream()
+  
+  # Average Bias of Estimators ----------------------------------------------
+  bias <- apply(X = result_mc, MARGIN = 1L, FUN = bias_function, par_true = true_parameters) %>% 
+    apply(MARGIN = 1L, FUN = mean)
+  paste0("bias_", n, ".RData") %>% save(file = ., bias)
+  
+  # Mean Square Error -------------------------------------------------------
+  mse <- apply(X = result_mc, MARGIN = 1L, FUN = mse_function, par_true = true_parameters) %>% 
+    apply(MARGIN = 1L, FUN = mean)
+  paste0("mse_", n, ".RData") %>% save(file = ., mse)
+}
 
[…]

### 2020-02-12 code/new_code_dagum.R
update

@@ -158,7 +158,7 @@ mse_function <- function(x, par_true) {
   (x - par_true) ^ 2
 }
 
-simular <- function(n) {
+simulate <- function(n) {
   # True parameters (theta, a, alpha, beta and p) -------------------------------------
   true_parameters <- c(1, 1, 1, 1, 1)
   
@@ -177,4 +177,4 @@ simular <- function(n) {
   paste0("mse_", n, ".RData") %>% save(file = ., mse)
 }
 
-walk(.x = c(10, 20, 60, 100, 200, 400, 600, 1000, 2000, 5000, 10000), .f = simular)
+walk(.x = c(10, 20, 60, 100, 200, 400, 600, 1000, 2000, 5000, 10000, 20000, 30000, 50000), .f = simulate)

### 2020-02-12 code/new_code_dagum.R
update

@@ -163,18 +163,31 @@ simulate <- function(n) {
   true_parameters <- c(1, 1, 1, 1, 1)
   
   set.seed(1L, kind = "L'Ecuyer-CMRG")
+  t0 <- Sys.time()
   result_mc <- mc(n = n, M = 1e4L, par_true = true_parameters, method = "BFGS")
+  total_time <- Sys.time() - t0
+    
   mc.reset.stream()
   
   # Average Bias of Estimators ----------------------------------------------
-  bias <- apply(X = result_mc, MARGIN = 1L, FUN = bias_function, par_true = true_parameters) %>% 
-    apply(MARGIN = 1L, FUN = mean)
-  paste0("bias_", n, ".RData") %>% save(file = ., bias)
+  eval(parse(text = glue("bias_{n} <- apply(X = result_mc, MARGIN = 1L, FUN = bias_function, par_true = true_parameters) %>% 
+        apply(MARGIN = 1L, FUN = mean)"))) 
+  eval(parse(text = glue("save(file = \"bias_{n}.RData\", bias_{n})")))
+  
   
   # Mean Square Error -------------------------------------------------------
-  mse <- apply(X = result_mc, MARGIN = 1L, FUN = mse_function, par_true = true_parameters) %>% 
-    apply(MARGIN = 1L, FUN = mean)
-  paste0("mse_", n, ".RData") %>% save(file = ., mse)
+  eval(parse(text = glue("mse_{n} <- apply(X = result_mc, MARGIN = 1L, FUN = mse_function, par_true = true_parameters) %>% 
+        apply(MARGIN = 1L, FUN = mean)"))) 
+  eval(parse(text = glue("save(file = \"mse_{n}.RData\", mse_{n})")))
+  
+  # Total Time --------------------------------------------------------------
+  eval(parse(text = glue("time_{n} <- total_time")))
+  eval(parse(text = glue("save(file = \"time_{n}.RData\", time_{n})")))
+  
+  # Result MC
+  eval(parse(text = glue("result_{n} <- result_mc")))
+  eval(parse(text = glue("save(file = \"result_{n}.RData\", result_{n})")))
+  
 }
 
 walk(.x = c(10, 20, 60, 100, 200, 400, 600, 1000, 2000, 5000, 10000, 20000, 30000, 50000), .f = simulate)

### 2020-02-12 code/new_code_dagum.R
update

@@ -174,7 +174,6 @@ simulate <- function(n) {
         apply(MARGIN = 1L, FUN = mean)"))) 
   eval(parse(text = glue("save(file = \"bias_{n}.RData\", bias_{n})")))
   
-  
   # Mean Square Error -------------------------------------------------------
   eval(parse(text = glue("mse_{n} <- apply(X = result_mc, MARGIN = 1L, FUN = mse_function, par_true = true_parameters) %>% 
         apply(MARGIN = 1L, FUN = mean)"))) 

### 2020-02-13 code/new_code_dagum.R
update

@@ -7,6 +7,7 @@ library(tibble)
 library(pbmcapply)
 library(magrittr)
 library(purrr)
+library(xtable)
 
 # Baseline functions. -----------------------------------------------------
 pdf_dagum <- function(x, alpha, beta, p) 
@@ -190,3 +191,29 @@ simulate <- function(n) {
 }
 
 walk(.x = c(10, 20, 60, 100, 200, 400, 600, 1000, 2000, 5000, 10000, 20000, 30000, 50000), .f = simulate)
+
+first_col <- c(10, 20, 60, 100, 200, 400, 600, 1000, 5000, 10000, 20000, 30000, 50000)
+
+tabela <- rbind(bias_10, bias_20, bias_60, bias_100, bias_200, bias_400, bias_600, bias_1000, bias_5000, bias_10000,
+                bias_20000, bias_30000, bias_50000)
+tabela <- cbind(n = first_col, tabela)
+rownames(tabela) <- NULL
+
+tabela <- tibble::as_tibble(tabela)
+
+latex <- print.xtable(xtable(tabela,  caption = "Mean bias of EMV obtained by the BFGS method in 10,000 Monte Carlo repetitions.",
+                      digits = 4L), print.results = FALSE)
+
+writeLines(
+  c(
+    "\\documentclass[12pt]{article}",
+    "\\begin{document}",
+    "\\thispagestyle{empty}",
+    latex,
+    "\\end{document}"
+  ),
+  "mc_simulation.tex"
+)
+
+tools::texi2pdf("mc_simulation.tex", clean = TRUE)
+

### 2020-08-10 tex/paper.tex
escrita das secao das simulacoes

--- 2020-02-11 tex/MO-Ga-G_Dec_28_2019.tex
@@
 \usepackage{pdflscape}
+\usepackage{bm}
+\usepackage{float}
 %\usepackage[dvips]{graphicx, color}
 \usepackage{subfigure}
+\usepackage[skins,listings,breakable]{tcolorbox}
+
+\usepackage{color}
+\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
+
 %TCIDATA{OutputFilter=latex2.dll}
@@
 
+\section{Simulation}\label{sec:simulation}
+
+Due to the probable absence of maximum likelihood estimators - MLE in closed form for distributions belonging to the MO-$\Gamma $-G family, it is necessary to understand the precision of the estimates obtained numerically.
+For that, we chose to study the bias of the estimators of the MO-$\Gamma$-Dagum($\theta$, $a$, $\alpha$, $\beta$, $p$) distribution, in which $ G \sim \mathrm {Dagum} (\alpha, \beta, p) $, for different sample sizes, being (10, 20, 60, 100, 200, 400, 600, 1000, 2000, 5000, 10000, 20000, 30000 and 500000).
+
+The simulations considered 10,000 Monte-Carlo - MC iterations for each of the sample sizes to which the numerical estimates were obtained by the BFGS method.
+Table \ref{tab:bias} shows that the BFGS method behaves well as the sample size grows.
+This is theoretically expected, however, in practice, difficulties can be faced in other families of distributions due to complications in the likelihood function.
+
+All simulations can be reproduced using the code in Annex \ref {ap:simulation}.
+The MC simulations are parallelized and are able to use all threads available by a multicore processor, thus making them more computationally efficient and consequently requiring less time to complete.
+The simulations were performed on a computer with an Intel Core i5-8265U processor with 8 threads working at a maximum frequency of 3.90 GHz, requiring, on these hardware, a time of 14.36 hours to perform all simulations.
+
+\begin{table}[H]
+	\centering
+	\caption{Mean bias of EMV obtained by the BFGS method in 10,000 Monte Carlo repetitions.} \label{tab:bias}
+	\begin{tabular}{rrrrrrr}
+		\hline
+		$\bm n$ & $\bm B(\bm \hat{\bm \theta})$ & $\bm B(\bm \hat{\bm a})$ & $\bm B(\bm \hat{\bm \alpha})$ & $\bm B(\bm \hat{\bm \beta})$ & $\bm B(\bm \hat{\bm p})$ & \textbf{Time (mins)}\\ 
+		\hline
+		10 & 0.2376 & 2.1635 & 2.7557 & 1.6282 & 1.3057 & 1.1430\\ 
+		20 & 0.4154 & 2.4639 & 1.5728 & 1.8082 & 0.7383 & 1.6248\\ 
+		60 & 0.7214 & 2.2432 & 0.5667 & 1.8815 & 0.2872 & 3.3954\\ 
+		100 & 0.6146 & 1.9579 & 0.3253 & 1.6148 & 0.2651 & 4.9628\\ 
+		200 & 0.3838 & 1.3894 & 0.1827 & 1.1773 & 0.3701 & 8.1457\\ 
+		400 & 0.2166 & 0.9635 & 0.1076 & 0.6181 & 0.3957 & 13.7370\\ 
+		600 & 0.1269 & 0.7242 & 0.0772 & 0.3968 & 0.3637 & 17.9310\\ 
+		1000 & 0.0553 & 0.4885 & 0.0521 & 0.2328 & 0.2636 & 22.8784 \\
+		2000  &  0.0456 & 0.3087 &  0.0334 &  0.0990 & 0.1722 &  38.4593\\
+		5000 & -0.0058 & 0.1307 & 0.0146 & 0.0117 & 0.0171 & 52.8098\\ 
+		10000 & -0.0146 & 0.0842 & 0.0095 & 0.0095 & 0.0031 & 95.8380\\ 
+		20000 & -0.0090 & 0.0330 & 0.0038 & 0.0005 & -0.0099 & 126.4260\\ 
+		30000 & -0.0028 & 0.0183 & 0.0012 & -0.0036 & -0.0029 & 182.0760\\ 
+		50000 & -0.0057 & 0.0124 & 0.0015 & 0.0016 & -0.0021 & 291.9300\\ 
+		\hline
+	\end{tabular}
+\end{table}
+
 \section{Applications}\label{applications}
@@
 
+Falta escrever ...
+
+\appendix
+
+\section{Simulation code}\label{ap:simulation}
+
+The code below was used to perform the simulations whose results are found in Table \ref{tab:bias} of Section \ref{sec:simulation}.
+The code was developed using the programming language R and is available to be reused in other simulations or even to check the results presented in this paper.
+
+\lstinputlisting[language=R, caption={Monte-Carlo simulations for different sample sizes.}, numbers=left,
+stepnumber=1,
+showspaces=false,
+tabsize=4,  
+basicstyle=\scriptsize,
+backgroundcolor=\color{lbcolor},
+showstringspaces=false]{new_code_dagum.R}
+
 \section*{References}

### 2020-08-10 tex/new_code_dagum.R

@@ -1,0 +1,326 @@
+# Title: Marshall Olkin Gamma-G (MOGG)
+# Author: Pedro Rafael D. Marinho
+
+# Loading libraries. ------------------------------------------------------
+library(parallel)
+library(tibble)
+library(pbmcapply)
+library(magrittr)
+library(purrr)
+library(xtable)
+
+# Baseline functions. -----------------------------------------------------
+pdf_dagum <- function(x, alpha, beta, p)
+  alpha * p / x * (x / beta) ^ (alpha * p) / ((x / beta) ^ alpha + 1) ^ (p + 1)
+# integrate(f = pdf_dagum, lower = 0, upper = Inf, alpha = 1.2,
+#           beta = 1.6, p = 2.2)
+
+cdf_dagum <- function(x, alpha, beta, p)
+  (1 + (x / beta) ^ (-alpha)) ^ (-p)
+# cdf_dagum(x = Inf, alpha = 1, beta = 4, p = 1)
+
+# This function creates MOGG functions. ----------------------------------
+pdf_mogg <- function(g, G) {
+  # Using Closures.
+  function(x, theta, a, ...) {
+    if (theta <= 0 || a <= 0)
+      warning("The \"a\" and \"theta\" parameters must be greater than zero.")
+    num <-
+      theta * (-log(1 - G(x = x, ...))) ^ (a - 1) * g(x = x, ...)
+    den <-
+      gamma(a) *
+      (theta + (1 - theta) *
+         pgamma(-log(1 - G(x = x, ...)), a, 1L)) ^ 2
+    num / den
+  }
+}
+
+rdagum <- function(n = 1L, alpha, beta, p) {
+  beta * (runif(n = n, min = 0, max = 1) ^ (-1 / p) - 1) ^ (-1 / alpha)
+}
+
+pdf_mogdagum <- pdf_mogg(g = pdf_dagum, G = cdf_dagum)
+
+# MOG-Dagum --------------------------------------------------------------------
+rmogdagum <- function(n = 1L, theta, a, alpha, beta, p) {
+  cond_c <- function(x, theta, a, alpha, beta, p) {
+    num <- pdf_mogdagum(x, theta, a, alpha, beta, p)
+    den <- pdf_dagum(x,
+                     alpha = alpha,
+                     beta = beta ,
+                     p = p)
+    - num / den
+  }
+  
+  x_max <-
+    optim(
+      fn = cond_c,
+      method = "BFGS",
[…]

### 2020-08-10 tex/paper.tex
escrita das secao das simulacoes

@@
 \vspace{0.3in}
-{\large Gauss M. Cordeiro$^a$ and Maria do Carmo$^a$}\\
+{\large Gauss M. Cordeiro$^a$ , Maria do Carmo$^a$ and Pedro Rafael D. Marinho$^b$}\\
 %\vspace{0.3in}
@@
 %\noindent {\bf JEL Codes}: C16, G1 \\ \\
-\noindent $^{a}$ Departamento de Estat\'{\i}stica, Universidade Federal de Pernambuco, Brazil.\\
-e-mail:\emph{gausscordeiro@de.ufpe.br, maria@de.ufpe.br} \\
+\noindent $^{a}$  Department of Statistics, Federal University of Pernambuco, Recife, Brazil.\\
+\noindent $^{b}$ Department of Statistics, Federal University of Paraíba, João Pessoa, Brazil.\\
+E-mail:\emph{gausscordeiro@de.ufpe.br, maria@de.ufpe.br, pedro.rafael.marinho@gmail.com} \\
 

### 2020-09-28 paper_27_09_2020/paper_27_09_2020.tex
update

--- 2020-02-11 tex/MO-Ga-G_Dec_28_2019.tex
@@
 \usepackage{graphicx}
+\usepackage{hyperref}
 \usepackage{color}
@@
 \makeatother
-\usepackage[brazilian]{babel}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{pdflscape}
+\usepackage{bm}
+\usepackage{float}
+\usepackage{listings}
 %\usepackage[dvips]{graphicx, color}
-\usepackage{subfigure}
+%\usepackage{subfigure}
+%\usepackage[skins,listings,breakable]{tcolorbox}
+
+\usepackage{color}
+\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
+
 %TCIDATA{OutputFilter=latex2.dll}
@@
 \setlength\topmargin{-1.5cm} \setlength\oddsidemargin{0.0cm}
-\setlength\evensidemargin{0.0cm} \setlength{\textwidth}{16cm}
+\setlength\evensidemargin{0.0cm} \setlength{\textwidth}{15cm}
 \setlength{\textheight}{25cm}
@@
 
+\hypersetup{
+	colorlinks=true,
+	linkcolor=blue,
+	filecolor=magenta,      
+	urlcolor=cyan,
+}
+
+\urlstyle{same}
+
 \begin{document}
@@
 \begin{center}
-\section*{\centerline {A new family of continuous distributions: properties and applications}}
+\section*{\centerline {A new family of distributions: properties and applications}}
 \vspace{0.3in}
-{\large Gauss M. Cordeiro$^a$ and Maria do Carmo$^a$}\\
+{\large Gauss M. Cordeiro$^a$ , Maria do Carmo S. Lima$^a$ and Pedro Rafael D. Marinho$^b$}\\
 %\vspace{0.3in}
@@
 \begin{abstract}\noindent
-This article introduces generalized beta-generated (GBG) distributions. Sub-models
-include all classical beta-generated, Kumaraswamy-generated and exponentiated
-distributions. They are maximum entropy distributions under three intuitive
-conditions, which show that the classical beta generator skewness parameters
-only control tail entropy and an additional shape parameter is needed to add entropy
-to the center of the parent distribution. This parameter controls skewness
-without necessarily differentiating tail weights. The GBG class also
-has tractable properties: we present various expansions for moments,
-generating function and quantiles. The model parameters
-are estimated by maximum likelihood and the usefulness of the new class
-is illustrated by means of some real data sets.
+This article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes. The family has only two
+extra shape parameters and can be a better alternative than other existing classes of distributions. Simulations are performed to verify the
+consistency of the estimators. Its flexibility is shown using two real data sets.
 \end{abstract}
@@
 \vspace{0.5in}
-\noindent {\bf Key Words}: \\ \\
+\noindent {\bf Key Words}:  Distribution family;  mathematical properties; simulations; applications.\\ \\
 %\noindent {\bf JEL Codes}: C16, G1 \\ \\
-\noindent $^{a}$ Departamento de Estat\'{\i}stica, Universidade Federal de Pernambuco, Brazil.\\
-e-mail:\emph{gausscordeiro@de.ufpe.br, maria@de.ufpe.br} \\
+\noindent $^{a}$  Department of Statistics, Federal University of Pernambuco, Recife, Brazil.\\
+\noindent $^{b}$ Department of Statistics, Federal University of Paraíba, João Pessoa, Brazil.\\
+E-mail:\emph{gausscordeiro@de.ufpe.br, maria@de.ufpe.br, pedro.rafael.marinho@gmail.com} \\
 
@@
 
-There has been an increased interest in developing generalized families of distributions by
-introducing additional shape parameters to a baseline cumulative distribution. This mechanism has
-proved to be useful to make the generated distributions more flexible especially for studying tail properties
-than existing distributions and for improving their goodness-of-fit statistics
+The mechanism by adding shape parameters to a baseline distribution has
+proved to be useful to make the generated distributions more flexible especially for studying tail
+properties than existing distributions and for improving their goodness-of-fit statistics
 to the data under study.
@@
 Let $G(x)$ be the cumulative distribution function (CDF) of a
-baseline distribution and $g(x)=dG(x)/dx$ be the associated
-probability density function (PDF) depending on a parameter vectot $\eta$. We present a generalized family
+baseline distribution and $g(x)=dG(x)/dx$ be the corresponding  probability density function (PDF) depending on a
+parameter vectot $\eta$. A generalized family are presented
 with two additional shape parameters by transforming the CDF $G(x)$
@@
 
-Marshall and Olkin (1997) pioneered a general method to expand
-a distribution G by adding an extra shape parameter.
-The CDF of their family (for $\theta>0$) is
+The CDF of the Marshall and Olkin's (1997) ($\text{MO-G}$) family (for $\theta>0$) is
 \begin{equation}\label{CDF_MO}
@@
 
-The density function corresponding to (\ref{CDF_MO}) is
+The density function corresponding to (\ref{CDF_MO}) has the form
 \begin{equation}\label{densityMO}
-f_{\text{MO-G}}(x)=\frac{\theta g(x)}{[\theta+(1-\theta)G(x)]^{2}},\quad x \in \mathbb{R}.
+f_{\text{MO-G}}(x)=\frac{\theta\, g(x)}{[\theta+(1-\theta)G(x)]^{2}}.
 \end{equation}
-For $\theta = 1$, $f_{\text{MO-G}}(x)$ is equal to $g(x)$ and, for different values of
-$\theta$, $f_{\text{MO-G}}(x)$ can be more flexible than $g(x)$.
-The extra parameter $\theta$ is called ``tilt parameter'', since
-the HRF of the MO-G family is shifted below ($\theta> 1$)
-or above ($0<\theta<1$) of the baseline HRF. Equation \eqref{densityMO} provides a useful
-mechanism to generate new distributions from existing ones. The advantage of this approach
-for constructing new distributions lies in its flexibility to model
-both monotonic and non-monotonic HRFs even when the baseline HRF may be
-monotonic. Tahir and Nadarajah (2015, Table 2) presented thirty distributions belonging to
-the $\text{MO-G}$ family. Further, this family is easily generated from the baseline QF by
+
+For $\theta=1$, $f_{\text{MO-G}}(x)$ is equal to $g(x)$. 
+Equation \eqref{densityMO} represents the PDF of the minimum of $n$ iid random variables having density $g(x)$, say $T_1,\cdots,T_N$, 
+where $N$ has a geometric distribution with probability parameters $\theta$ and $\theta^{-1}$ if $0<\theta<1$ and $\theta>1$, 
+respectively.
+
+Tahir and Nadarajah (2015, Table 2) presented thirty distributions
+belonging to this family. It is easily generated from the baseline quantile function (QF) by
 $Q_{\text{MO-G}}(u)=Q_{G}\left(\theta u \left[\theta u+1-u\right]\right)$ for $u\in(0,1)$.
@@
 refers to a two-parameter competitive model to the Weibull and gamma distributions.
-A simple interpretation of (\ref{CDF_MO}) can be given as follows. Let $T_1,\ldots,T_N$ be a sequence
-of independent and identically distributed (i.i.d.)~random variables with survival function (SF)
-$\overline{G}(x)=1-G(x)$, and let $N$ be a positive integer
-random variable independent of the $T_i$'s defined by the probability generating function (PGF) of a
-geometric distribution with parameter $\theta$, say $\tau(z;\theta)=\theta z\,[1-(1-\theta)z]^{-1}$.
-Then, the inverse of $\tau(z;\theta)$ becomes $\tau^{-1}(z;\theta)=\tau(z;\theta^{-1})$. We can verify that
-equation \eqref{CDF_MO} comes from $1 - F_{\text{MO-G}}(x)=\tau(\overline{G}(x);\theta)$ for $0<\theta<1$ and
-$1-F_{\text{MO-G}}(x)=\tau(\overline{G}(x);\theta^{-1})$ for $\theta>1$. For both cases, $1-F_{\text{MO-G}}(x)$
-re\-presents the SF of $\min\{T_1,\ldots,T_N\}$, where $N$ has
-PGF $\tau(z;\cdot)$ with probability parameters $\theta$ or $\theta^{-1}$.
 
-Zografos and Balakrishnan (2009) and Risti\'{c} and Balakrishnan (2011)
-defined the gamma-G ($\Gamma$-G) family with an extra shape parameter $a>0$ by
-the CDF (for $x \in \mathbb{R}$)
+The CDF of the gamma-G ($\Gamma$-G) family (Zografos and Balakrishnan, 2009) is
 \begin{eqnarray}\label{CDF_Ga}
-F_{\Gamma\text{-G}}(x)=\gamma_1\left( a, -\log \left[1-G(x)\right]\right)
-=\frac{\displaystyle 1}{\displaystyle \Gamma(a)}\,\gamma\left( a, -\log \left[1-G(x)\right]\right),
+F_{\Gamma\text{-G}}(x)=\gamma_1\left( a, -\log \left[1-G(x)\right]\right), \quad x \in \mathbb{R},
 \end{eqnarray}
-where $\gamma(a,z)=\int_0^{z} t^{a-1}\,\rm{e}^{-t}dt$ is the incomplete gamma function and
- $\gamma_1(a,z)= \gamma(a,z)/\Gamma(a)$ is the incomplete gamma function ratio.
-The PDF of the $\Gamma$-G family takes the form
+where $a>0$ is an extra shape parameter,  $\gamma_1(a,z)= \gamma(a,z)/\Gamma(a)$ is the incomplete gamma function ratio
+and $\gamma(a,z)=\int_0^{z} t^{a-1}\,\rm{e}^{-t}dt$.
+
+Then, the PDF of the $\Gamma$-G family can be expressed as
 \begin{eqnarray}\label{PDF_Ga}
 \displaystyle
-f_{\Gamma\text{-G}}(x)=\frac{\displaystyle 1}{\displaystyle \Gamma(a)} \left\{ -\log[1-G(x)] \right\}^{a-1}\, g(x),
-\quad x \in \mathbb{R}.
+f_{\Gamma\text{-G}}(x)=\frac{\displaystyle 1}{\displaystyle \Gamma(a)} \left\{ -\log[1-G(x)] \right\}^{a-1}\, g(x).
 \end{eqnarray}
-Each new $\Gamma$-G distribution can be determined from a given baseline distribution.
-For $a=1$, the G distribution is a basic exemplar of the $\Gamma$-G family.
 
-Zografos and Balakrishnan (2009) and Risti\'{c} and Balakrishnan (2011)
-presented a physical motivation for the $\Gamma$-G family: if $X_{L(1)},\ldots, X_{L(n)}$ are lower record values
-from a sequence of independent random variables with common PDF $g (\cdot)$, then the PDF of the $n$th lower
-record value has the form (\ref{PDF_Ga}). If $Z$ is a gamma random variable with unit scale
-parameter and shape parameter $a>0$, then $X=Q_G(1-\rm{e}^{Z})$ has density (\ref{PDF_Ga}). So,
+Each new $\Gamma$-G distribution follows from a given baseline G.
+For $a=1$, the $\Gamma$-G family reduces to G.
+If $Z$ is a gamma random variable with unit scale
+parameter and shape parameter $a>0$, then $W=Q_G(1-\rm{e}^{Z})$ has density (\ref{PDF_Ga}). So,
 the $\Gamma$-G distribution is easily generated from the gamma distribution and the QF of G.
 
-The rest of the paper is organized as follows. Section \ref{sec:MOGaG} describes the distribution and density
-of the new class of distributions called the {\it Marshall and Olkin-Gamma-G} (MO-$\Gamma$-G) family  by combining the above generators.
-We also present some special models. The maximum likelihood estimation of the model parameters of the new family is
-described in Section \ref{estimation}. In Section \ref{applications}, we provide some empirical applications to illustrate
-the potentiality of the proposed family. A variety of theoretical properties are considered in Section \ref{properties}.
-Finally, conclusions are noted in Section \ref{conclusions}.
+The remaining of the paper is addressed as follows. Section \ref{sec:MOGaG} introduces the {\it Marshall and Olkin-Gamma-G} (MO-$\Gamma$-G)
+family and presents some special models. The maximum likelihood estimates (MLEs) of the parameters of the new family is addressed
+in Section \ref{estimation}. Some simulations ate performed in Section \ref{sec:simulation} to estimate the biases of the MLEs. Two
+empirical applications illustrate the potentiality of the proposed family in Section \ref{applications}. A variety of theoretical properties are derived
+in Section \ref{properties}. Some conclusions remarks are offered in Section \ref{conclusions}.
 
@@
 
-Let $X\sim$MO-$\Gamma$-G denote a random variable having the MO-$\Gamma$-G family with two extra shape parameters $\theta>0$ and $a>0$
-and the baseline vector $\eta$. By combining Equations (\ref{CDF_MO}) and (\ref{CDF_Ga}), the CDF of $X$ has the form
+By combining Equations (\ref{CDF_MO}) and (\ref{CDF_Ga}), the CDF of the random variable $X\sim$MO-$\Gamma$-G
+representing the new family is defined by
 \begin{equation}\label{CDF_MO-Gamma-G}
@@
 
-By differentiating (\ref{CDF_MO-Gamma-G}), we can write the PDF of $X$ as
-\begin{equation}\label{CDF_MO-Gamma-G}
-f_{X}(x)=\frac{\theta  \left\{ -\log[1-G(x)] \right\}^{a-1}\, g(x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-G(x)\right]\right)\right\}^{2}},\quad x \in \mathbb{R}.
+By differentiating (\ref{CDF_MO-Gamma-G}), the PDF of $X$ follows as
+\begin{equation}\label{PDF_MO-Gamma-G}
+f_{X}(x)=\frac{\theta  \left\{ -\log[1-G(x)] \right\}^{a-1}\, g(x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-G(x)\right]\right)\right\}^{2}}.
 \end{equation}
+
+The density (\ref{PDF_MO-Gamma-G}) can be interpreted from a sequence of $N$ iid random variables, say $Z_1,\cdots,Z_N$,
+each one having a gamma density unit scale and shape $a>0$, assuming that $N$ (is not fixed) has a geometric 
+distribution with probabilities $\theta$ and $\theta^{-1}$ for $0<\theta<1$ and $\theta>1$,
+respectively. By transforming the $Z_i$'s via the baseline QF by $W_i=Q_G(1-\rm{e}^{Z_i})$
+(for $i-1,\ldots,N$), Equation \eqref{densityMO} is defined the PDF of the minimum $W_1,\cdots,W_n$. 
+Making this double composition of the two generators, the proposed family absorbs the impacts of two different flexibilities 
+on applications.
+
+Table \ref{tabspecial1} provides some special cases of (\ref{PDF_MO-Gamma-G}), where
+$\Phi(x)$ and $\phi(x)$ are the CDF and PDF of the standard normal distribution. The density and hazard functions
+of the Marshall-Olkin-$\Gamma$-Weibull (MO-$\Gamma$-W) are displayed in Figure \ref{formas}, which provide
+more flexibility for these functions in relation to the baseline ones.
+
+\vspace{0.6cm}
+
+\begin{figure}[H]
+\begin{center}
+(a)\hspace{3.5cm} (b)\\
+\includegraphics[scale=.3]{density.pdf}
+\includegraphics[scale=.3]{hazard.pdf}\\
+\vspace{-0.5cm}
+\caption{(a) Curves for the MO-$\Gamma$-W density. (b) Curves for the MO-$\Gamma$-W hazard.\label{formas}}
+\end{center}
+\end{figure}
+
+\vspace{0.6cm}
+
+The CDF \eqref{CDF_MO-Gamma-G} can be easily inverted to determine the quantile function (QF) of the MO-$\Gamma$-G distribution,
+say $x=Q_{X}(u)$, in terms of the baseline QF $Q_G(u)$. Let $u$ be a uniform $U(0,1)$ random variate. By using \eqref{CDF_MO-Gamma-G}
+and letting $z=\gamma_{1}\left(a, -\log[1-G(x)]\right)$, it follows $z=z(u)=\theta u/[1-(1-\theta)u]$.
+Then, the QF of $X$ takes the form $x=Q_G\left(1-\rm{e}^{-v}\right)$, where $v=v(z)$ is an upper point
+corresponding to the quantile $z$ of a gamma density (with unit scale and shape $\alpha$).
 
@@
 \caption{Special Distributions in the  MO-$\Gamma$-G family.}
-($\Phi(x)$ and $\phi(x)$ denote the standard normal distribution and density\\ functions and $\gamma_1(a,z)$ is the incomplete gamma function ratio).
 \end{table}
@@
 
-Figure \ref{formas} shows the performance of the density and hazard functions of the Marshall-Olkin Gamma Weibull (MO-$\Gamma$-W, for short).
-Note that this extension of the Weibull distribution provides more flexibility for density and hazard shapes.
-
-\begin{figure}[h!]
-\begin{center}
-(a)\hspace{3.5cm} (b)\\
-\includegraphics[scale=.3]{density.pdf}
-\includegraphics[scale=.3]{hazard.pdf}\\
-\vspace{-0.5cm}
-\caption{(a) Curves for the MO-$\Gamma$-W density; (b) Curves for the MO-$\Gamma$-W hazard;\label{formas}}
-\end{center}
-\end{figure}
-
-\subsection{Quantile Function}\label{QuantFunc}
-
-We can easily invert the cdf \eqref{CDF_MO-Gamma-G} to express the MOGa-G
-quantile function (qf), say $x=Q_{X}(u)=G^{-1}(u)$, in terms of the baseline 
-qf $Q_G(u)$. Let $u$ be a uniform $U(0,1)$ random variate. By using \eqref{CDF_MO-Gamma-G}
-and letting $z=\gamma_{1}\left(a, -\log[1-G(x)]\right)$, we obtain $z=z(u)=\theta u/[1-(1-\theta)u]$. 
-Then, the qf of $X$ has the form $x=Q_G\left(1-\rm{e}^{-v}\right)$, where $v=v(z)$ is a random variate generated
-from a gamma distribution (with shape parameter $\alpha$ and unit scale parameter) corresponding to the quantile $z$. 
-This scheme is useful because of the existence of fast generators for uniform and gamma 
-random variables.
-
 \section{Estimation}\label{estimation}
 
-The  MO-$\Gamma$-G family mentioned previously can be  fitted to real data sets using the {\it AdequacyModel}
-package for the {\sf R} statistical computing environment ({\tt https://www.r-project.org/}).
-An important advantage of this packa\-ge is that it is not necessary to define
-the log-likelihood function and that it computes the maximum likelihood estimates (MLE), their standard errors and the formal statistics
-presented in the nest section. We only need to provide the PDF and CDF of the distribution to be fitted to a data set.
-This {\it AdequacyModel} package uses the PSO (particle swarm optimization) method obtained by traditional global search approaches
-such as the quasi-Newton BFGS, Nelder-Mead and simulated-annealing methods to maximized the log-likelihood function. This
-method does not require initial values. More
-details are available at {\tt https://rdrr.io/cran/AdequacyModel/}.
+The  MO-$\Gamma$-G family can be  fitted to real data using the {\bf AdequacyModel} package in the {\sf R} software.
+This packa\-ge does not require to define the log-likelihood function and it computes the MLEs, their standard errors (SEs)
+and the formal statistics defined in Section \ref{applications}. It is necessary to provide the
+PDF and CDF of the distribution to be fitted to a data set.
 
-Here, we consider estimation of unknown parameters of the MO-$\Gamma$-$G$ distribution by the method of maximum likelihood.
-If $x$ is one observation from \ref{} and $\etn$ a q-vector parameter vector specifying $G(.)$, thus the log-likelihood function, say $\log L=\log L(a,\theta,\etn)$ is
-\begin{align}\ell (\boldsymbol{\Theta})=&\,n\log (\theta)+n\log(\gamma)+n\, a\, \gamma \log(\lambda)+(a\gamma-1)\sum_{i=1}^n{\log(x_i)}-\lambda^\gamma\sum_{i=1}^n{\log(x_i)}-n\log[\Gamma(a)] \nonumber \\ & -2\sum_{i=1}^n{\log\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x_i)^\gamma]\}}
+For example, if $x_i$ is one observation from (\ref{PDF_MO-Gamma-G}) and $\etn$ is a $q$-parameter vector specifying $G(\cdot)$,
+the log-likelihood function for $\boldsymbol{\theta}^\top=(a,\theta,\etn^\top)$ from $n$ observations is
+\begin{align}\label{loglik}
+\ell (\boldsymbol{\theta})=&\,n\log (\theta)+n\log(\gamma)+n\, a\, \gamma \log(\lambda)+(a\gamma-1)\sum_{i=1}^n{\log(x_i)}-\lambda^\gamma\sum_{i=1}^n{\log(x_i)}\nonumber \\ &
+-n\log[\Gamma(a)]-2\sum_{i=1}^n{\log\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x_i)^\gamma]\}}.
 \end{align}
+
+Due to the impossibility of obtaining the MLEs in closed form, numerical methods to obtain the estimates that maximize $ \ell (\cdot) $ are necessary.
+Several programming languages and statistical software distributes functions and routines that make it easy to obtain numerical estimates by various interactive methods.
+In practice, obtaining the MLEs for the parameters that index a probability distribution are commonly obtained in this way, since the Newton and quasi-Newton methods produce satisfactory results under reasonable conditions of the object function, that is, when they do not impose conditions that disturb the convergence of the algorithms.
+
+To obtain the MLEs, the package {\bf AdequacyModel} of the programming language {\sf R} was used, see R Core Team (2020).
+This library, created and maintained by one of the authors of this paper, is widely cited by several papers in the field of statistics and serves as a basis for other library implementations available on the Comprehensive R Archive Network - CRAN.
+With it, in particular using the function {\tt goodness.fit} it is possible to pass an implementation {\sf R} of (\ref {PDF_MO-Gamma-G}), being in charge of the function {\tt goodness.fit} obtain $\ell (\cdot)$ by returning several measures of fit adequacy as well as MLEs.
+Further details regarding the {\bf AdequacyModel} package can be obtained from Marinho et al.
+(2019).
+
+\section{Simulations}\label{sec:simulation}
+
+Due to the probable absence of MLEs in closed-form for distributions belonging to the MO-$\Gamma $-G family, it is necessary to examine the
+precision of the estimates calculated numerically. For doing that, the biases of the estimators of the parameters of the
+MO-$\Gamma$-Dagum($\theta$, $a$, $\alpha$, $\beta$, $p$) distribution are determined, where $G\sim \mathrm {Dagum} (\alpha, \beta, p)$
+is the baseline distribution. All parameters are taken equal to one for different sample sizes reported in Table \ref{tab:bias}.
+
+Ten thousand Monte Carlo simulations are performed for each sample size to examine the numerical estimates calculated by the
+BFGS method. The figures in Table \ref{tab:bias} indicate that this method behaves well when the sample size increases.
+This is theoretically expected. However, in practice, difficulties can be faced in other families of distributions
+due to the flatness of the log-likelihood function.
+
+All simulations can be reproduced using the script in Appendix \ref{ap:simulation}. The simulations are parallelized and able to use all threads
+available by a multicore processor, thus making them more computationally efficient and consequently requiring less time to complete.
+The simulations are performed on a computer with an Intel Core i5-8265U processor with 8 threads working at a maximum frequency of 3.90 GHz,
+requiring, on these hardware, a time of 14.36 hours to perform all simulations. The figures in Table \ref{tab:bias} reveal that the average
+biases of the MLEs could be very reduced only for $n> 2,000$.
+
+\begin{table}[H]
+	\centering
+	\caption{Average biases of the MLEs obtained using the BFGS method.}\label{tab:bias}
+	\begin{tabular}{rrrrrrr}
+		\hline
+		$n$ & $B(\hat{\theta})$ & $B(\hat{a})$ & $B(\hat{\alpha})$ & $B(\hat{\beta})$ & $B(\hat{p})$ & Time (mins)\\
+		\hline
+		10 & 0.2376 & 2.1635 & 2.7557 & 1.6282 & 1.3057 & 1.1430\\
+		20 & 0.4154 & 2.4639 & 1.5728 & 1.8082 & 0.7383 & 1.6248\\
+		60 & 0.7214 & 2.2432 & 0.5667 & 1.8815 & 0.2872 & 3.3954\\
+		100 & 0.6146 & 1.9579 & 0.3253 & 1.6148 & 0.2651 & 4.9628\\
+		200 & 0.3838 & 1.3894 & 0.1827 & 1.1773 & 0.3701 & 8.1457\\
+		400 & 0.2166 & 0.9635 & 0.1076 & 0.6181 & 0.3957 & 13.7370\\
+		600 & 0.1269 & 0.7242 & 0.0772 & 0.3968 & 0.3637 & 17.9310\\
+		1,000 & 0.0553 & 0.4885 & 0.0521 & 0.2328 & 0.2636 & 22.8784 \\
+		2,000  &  0.0456 & 0.3087 &  0.0334 &  0.0990 & 0.1722 &  38.4593\\
+		5,000 & -0.0058 & 0.1307 & 0.0146 & 0.0117 & 0.0171 & 52.8098\\
+		10,000 & -0.0146 & 0.0842 & 0.0095 & 0.0095 & 0.0031 & 95.8380\\
+		20,000 & -0.0090 & 0.0330 & 0.0038 & 0.0005 & -0.0099 & 126.4260\\
+		30,000 & -0.0028 & 0.0183 & 0.0012 & -0.0036 & -0.0029 & 182.0760\\
+		50,000 & -0.0057 & 0.0124 & 0.0015 & 0.0016 & -0.0021 & 291.9300\\
+		\hline
+	\end{tabular}
+\end{table}
 
@@
 
-In this section, we provide two applications in order to show the performance of our proposed family with another ones.
-To do this, we consider the Weibull distribution as baseline and for competitive distributions, we consider: beta-Weibull ($\beta$-W), proposed by Famoye {\it et al.} (2005); Kumaraswamy Weibull (KW-W), see Cordeiro and Nadarajah (2010); Marshall-Olkin Weibull (MO-W), studied by Ahmed {\it et al.} (2017); Marshall-Olkin Extented Weibull (MOE-W), see the family proposed by Cordeiro {\it et al.} (2019)
-Exponentiated Weibull (exp-W), introduced by Mudholkar and Srivastava (1993); gamma Weibull (gamma-W), see Cordeiro {\it et al.} (2016) and exponentiated generalized Weibull (EG-W), see Oguntunde {\it et al.} (2015), with $a=1$.
+Consider the Weibull baseline. Two applications are provided to compare the new generated model with seven extended Weibull
+distributions, namely the beta-Weibull ($\beta$-W) (Famoye {\it et al.}, 2005), Kumaraswamy Weibull (Kw-W) (Cordeiro and Nadarajah, 2010),
+Marshall-Olkin Weibull (MO-W) (Ahmed {\it et al.}, 2017), Marshall-Olkin Extended Weibull (MOE-W) (Cordeiro {\it et al.}, 2019),
+exponentiated Weibull (exp-W) (Mudholkar and Srivastava, 1993), gamma Weibull ($\Gamma$-W) Cordeiro {\it et al.}, 2016) and exponentiated
+generalized Weibull (EG-W) (Oguntunde {\it et al.}, 2015) (with $a=1$). Some of these distributions are widely used in practice.
 
-The log-likelihood for the Marshall-Olkin Gamma Weibull (MO-$\Gamma$-W) and considering one observation is given by
+The log-likelihood for the Marshall-Olkin-Gamma-Weibull (MO-$\Gamma$-W) from one observation is
 \begin{align}
-\ell (\boldsymbol{\Theta})=& \log (\theta)+\log (\gamma)+(a\,\gamma)\log (\lambda)+(a\,\gamma-1)\log(x)-(\gamma\, x)^\gamma-\log[\Gamma(a)]\nonumber \\ &-2\log\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x)^\gamma]\}
+\ell (\boldsymbol{\theta})=& \log (\theta)+\log (\gamma)+(a\,\gamma)\log (\lambda)+(a\,\gamma-1)\log(x)-(\gamma\, x)^\gamma-\log[\Gamma(a)]\nonumber \\ &-2\log\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x)^\gamma]\},
 \end{align}
-where $\boldsymbol{\Theta}=(a,\theta,\lambda,\gamma)^T$. Besides that, the components of the score is given by
+where $\boldsymbol{\theta}=(a,\theta,\lambda,\gamma)^\top$. The components of the score function are
 
 \begin{equation*}
-U_{a}(\boldsymbol{\Theta})=\gamma  \log (\lambda )+\gamma  \log (x)-\psi ^{(0)}(a)-\frac{2\left\{(1-\theta ) A-(1-\theta ) \psi ^{(0)}(a) \gamma_1 \left[a,(x \lambda
+U_{a}(\boldsymbol{\theta})=\gamma  \log (\lambda )+\gamma  \log (x)-\psi ^{(0)}(a)-\frac{2\left\{(1-\theta ) A-(1-\theta ) \psi ^{(0)}(a) \gamma_1 \left[a,(x \lambda
    )^{\gamma }\right]\right\}}{\theta\,\Gamma(a)+(1-\theta)\gamma_1\left[a,(x \lambda
@@
 \begin{equation*}
-U_{\theta}(\boldsymbol{\Theta})=\frac{1}{\theta}-\frac{2\left\{\Gamma(a)-\gamma_1\left[a,(\lambda\,x)^\gamma\right]\right\}}{\theta\,\Gamma(a)+(1-\theta)\gamma_1\left[a,(\lambda\,x)^\gamma\right]},
+U_{\theta}(\boldsymbol{\theta})=\frac{1}{\theta}-\frac{2\left\{\Gamma(a)-\gamma_1\left[a,(\lambda\,x)^\gamma\right]\right\}}{\theta\,\Gamma(a)+(1-\theta)\gamma_1\left[a,(\lambda\,x)^\gamma\right]},
 \end{equation*}
@@
 \begin{equation*}
-U_{\lambda}(\boldsymbol{\Theta})=\frac{\gamma }{\lambda }\left[a-(\lambda\,x)^\gamma\right]+\frac{2 \gamma \,\lambda^{-1}(\lambda\,x)^{a\,\gamma} (1-\theta )\exp\{-(\lambda\,x)^\gamma\} }{\theta \,\Gamma(a)+(1-\theta )
+U_{\lambda}(\boldsymbol{\theta})=\frac{\gamma }{\lambda }\left[a-(\lambda\,x)^\gamma\right]+\frac{2 \gamma \,\lambda^{-1}(\lambda\,x)^{a\,\gamma} (1-\theta )\exp\{-(\lambda\,x)^\gamma\} }{\theta \,\Gamma(a)+(1-\theta )
    \gamma_1 \left[a,(x \lambda )^{\gamma }\right]}
@@
 \begin{equation*}		
-U_{\gamma}\boldsymbol{\Theta}=\frac{1}{\gamma }+a \log (\lambda )+a \log (x)-(\lambda  x)^{\gamma } \log
+U_{\gamma}\boldsymbol{\theta}=\frac{1}{\gamma }+a \log (\lambda )+a \log (x)-(\lambda  x)^{\gamma } \log
    (\lambda  x)+\frac{2 (1-\theta )(\lambda
@@
 \right]+\log \left[(\lambda  x)^{\gamma }\right] \gamma_1 \left[a,(x \lambda )^{\gamma
-   }\right].
+   }\right],
 \end{align*}
-where $\psi^{(n)}(x)$ is the $n$-th derivative of the digamma function and
+$\psi^{(n)}(x)$ is the $n$-th derivative of the digamma function,
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-where $G^{m,n}_{p,q}\,\left(z \Big{|}	\stackrel{a_{1},\ldots,a_{p}}{b_{1},\ldots,b_{q}}\right)$ is the Meijer G function.%exp-W Mudholkar, G.
-S.
-and Srivastava, D.
-K.
-(1993).
-Exponentiatel Weibull family for analyzing bathtub failure-rate data.
-{\it IEEE Transactions on Reliability}, {\bf 42}, 299--302.
+and $G^{m,n}_{p,q}\,\left(z \Big{|}	\stackrel{a_{1},\ldots,a_{p}}{b_{1},\ldots,b_{q}}\right)$ is the Meijer G function.
 
-% kw-w Codeiro, G. M. and Nadarajah, S. (2010). The Kumaraswamy Weibull distribution with application to failure data. {\it Journal of the Franklin Institute}, {\bf 347}, 1399--1429.
+The {\bf AdequacyModel} is used to fit the distributions cited before to two real data sets. The SANN method, which is a
+variant of simulated annealing (Belisle, 1992), is considered. The distributions are compared via the Anderson
+Darling (A$^{*}$) and Cram\'er Von Mises (W$^{*}$) statistics reported in the {\tt goodness.fit} function.
 
-%MO-W Ahmed, H. H., Bdair, O. M. and Ahsanullah, M. (2017). On Marshall-Olkin Extended Weibull distribution. {\it Journal of Statistical Theory and Methods}, {\bf 16}, 1--17.
-
-%VER GAMMA WEIBULL (REFERENCIA MEU TRABALHO GAMMA EXTENDED WEIBULL CNO Journal of Statistical Distributions and Applications)
-
-%EG-W Oguntunde, P.
-E., Odetunmibi, O.
-A.
-and Adejumo, A.
-O.
-(2015).
-On the Exponentiated Generalized Weibull Distribution: A Generalized of the Weibull Distribution.
-{\it Indian Journal of Science and Technology}, {\bf 8}, 1--7.
-
-To provide the results, in this section we use the {\sf R} software.
-In order to adjust the data sets consider here, we use the {\it AdequacyModel} package mentioned in Section \ref{estimation}.
-The method used here was the SANN method, that is a variant of simulated annealing (Belisle, 1992).
-To compare our proposed model with the other ones mentioned above, we use the Anderson Darling (A$^{*}$) and Cramer Von Mises (W$^{*}$) statistics, given by the {\it goodness.fit} function.
-
-For the first data set, we consider a modification of the ``FoodExpenditure'' from the {\it betareg} package in {\sf R} software, that refers  on proportion of income spent on food for a random sample of 38 households in a large US city, according to the package information.
-Here, we consider the household expenditures for food.
-The modification is
+For the first data set, a modification of the ``FoodExpenditure'' data from the {\bf betareg} package  is considered, which refers
+to the proportions of income spent on food for a random sample of 38 households in a large US city (according to the package information).
+Here, the household expenditures for food are considered and is given by
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-where $FoodExpenditure_{food}$ is the random variable about the household expenditures for food and $\#(.)$ indicates the number of observations on the variable in question.
-The maximum likelihood estimators (MLE's) and their related standard errors (in parenthesis) are given in Table \ref{tab-ex1}.
-Besides that, the (W$^{*}$) and (A$^{*}$) statistics are described in this table too.
-The results indicate that the proposed model has better performance than the other ones.
+where $FoodExpenditure_{food}$ is the random variable corresponding to the household expenditures for food and $\#(\cdot)$ indicates the number of
+observations on this variable. The MLEs and their standard errors (SEs) (in parentheses) are listed in Table \ref{tab-ex1}.
+The statistics  W$^{*}$ and A$^{*}$ are also given in this table. The results indicate that the proposed model has better performance than the other
+seven fitted models.
 
@@
  & & & & &  \\
- gamma-W$(a,\lambda,\gamma)$    & 5.751546  & - &  10.0000 & 1.208773&  0.0879 & 0.6599  \\ 
+$\gamma$-W$(a,\lambda,\gamma)$    & 5.751546  & - &  10.0000 & 1.208773&  0.0879 & 0.6599  \\
 &  (0.0015006)&  (-)&  (0.0001163185) &(0.00822782)    &  & \\
@@
 
-As a second application, we consider a data set that can be found in http://biostat.mc.vanderbilt.\\
-edu/wiki/
-Main/DataSets. This data was collected in a pilot study about hypertension in the Dominican Republic
-in 1997. The observations are the systolic blood pressure of persons who came to medical clinics in
-several villages, for a variety of complaints. The MLEs of the model parameters and standard errors
-and the values of the statistics are listed in Table \ref{tab-ex2} for the previous models. Overall, by
-comparing the measures of these formal goodness-of-fit statistics, we conclude that the proposed distribution
-outperforms all distributions considered in Table \ref{tab-ex2}.
+As a second application, consider a data set collected in a pilot study about hypertension in the Dominican Republic
+in 1997 found in \url{http://biostat.mc.vanderbilt.edu/wiki/
+Main/DataSets}. The observations are the systolic blood pressure of persons who came to medical clinics in
+several villages for a variety of complaints. The MLEs of the parameters, their SEs and the values of the statistics are
+listed in Table \ref{tab-ex2} for the previous distributions. By comparing the measures of these formal statistics,
+we conclude that the proposed distribution outperforms the rest of them.
 
@@
  & & & & &  \\
- gamma-W$(a,\lambda,\gamma)$    & 9.11229459   & - &  0.02617729 & 1.74641178 &    0.6227098 & 3.488268  \\ 
+ $\Gamma$-W$(a,\lambda,\gamma)$    & 9.11229459   & - &  0.02617729 & 1.74641178 &    0.6227098 & 3.488268  \\
                              &  (0.96330688)&  (-)&  (0.00291875) & (0.08030313)     &  & \\
@@
 
-In this section, we present some main mathematical properties for the MO-$\Gamma$-G family
-based on a general linear representation for its density given in the next section.
+In this section, some main mathematical properties are presented for the MO-$\Gamma$-G family
+based on a general linear representation for its density function, which are important
+to determine its mathematical properties from those of exponentiated-G (exp-G) distributions.
 
@@
 
-A linear representation for the PDF the new family defined previously
-can be derived using the concept of exponentiated distributions.
-For an arbitrary baseline CDF $G(x)$, the exponentiated-G (exp-G)
-distribution with parameter $a>0$, has CDF and PDF in the forms
+For an arbitrary CDF $G(x)$, the CDF and PDF of the exponentiated-G (exp-G) distribution with power parameter $a>0$ are
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-respectively. The properties of the exponentiated distributions have been studied
-by many authors in recent years, see Mudholkar and Srivastava (1995) for exponentiated
-Weibull, Gupta {\it et al.} (1998) for exponentiated Pareto, Gupta and
-Kundu (2001) for exponentiated exponential and Nadarajah and Gupta (2007)
-for exponentiated gamma distribution. Tahir and Nadarajah (2015) cited almost
-thirty exponentiated distributions in their Table 1.
+respectively. This class of distributions is quite useful in several applications. In fact, Tahir and Nadarajah (2015)
+cited more than seventy papers on exponentiated distributions in their Table 1.
 
-A linear representation for the PDF of the MO-$\Gamma$-G family in terms of exp-G densities is important
-to determine its mathematical properties from those of the exp-G distributions. They can follow from the papers
-described below.
-
-First, the MO-G density (\ref{densityMO}) admits the
+First, the MO-G cumulative distriution (\ref{densityMO}) admits the
 linear combination (Barreto-Souza \emph{et al.}, 2013)
-\begin{equation*}
-f_{\text{MO-G}}(x)
+\begin{equation}
+F_{\text{MO}-\Gamma}(x)
 \,=\,
-\sum^{\infty}_{i=0}\,w_i^{\text{MO-G}}\,\pi_{i+1}(x),
+\sum^{\infty}_{i=0}\,w_i^{\text{MO-G}}\,\Pi_{i+1}(x)\,=\,\sum^{\infty}_{i=0}\,w_i^{\text{MO-G}}\,G(x)^{i+1},
 \label{EXP44}
-\end{equation*}
+\end{equation}
 where the coefficients are (for $i=0,1,\ldots$)
 \[
-w_i^{\text{MO-G}}=w_i^{\text{MO-G}}(\theta) =
+w_i^{\text{MO}-\Gamma}=w_i^{\text{MO}-\Gamma}(\theta) =
 \begin{cases}
-\dfrac{(-1)^i\,\theta}{(i+1)} \sum\limits^{\infty}_{j=i}\dbinom{j}{i}(j+1) \bar{\theta}^j,& \quad \theta\in (0,1),\\
+\dfrac{(-1)^i\,\theta}{(i+1)} \sum\limits^{\infty}_{j=i}(j+1)\,\dbinom{j}{i}\,\bar{\theta}^j,& \quad \theta\in (0,1),\\
 \theta^{-1} (1-\theta^{-1})^i,& \quad \theta>1,
@@
 
-Second, the linear combination for the $\Gamma\text{-G}$ density (\ref{PDF_Ga}) was
-derived by Castellares and Lemonte (2015) as
-\begin{equation*}\label{EXP33}
-f_{\Gamma\text{-G}}(x)\,=\,\sum_{i=0}^\infty w_i^{\Gamma\text{-G}}\,\,\pi_{a+i}(x),
-\end{equation*}
-where
-$$w_i^{\Gamma\text{-G}}=w_i^{\Gamma\text{-G}}(a)=\frac{\varphi_{i}(a)}{(a+i)},$$
+Second, the linear combination for the $\Gamma\text{-G}$ cumulative distribution (\ref{PDF_Ga}) follows from Castellares and Lemonte (2015) as
+\begin{equation}\label{EXP33}
+F_{\Gamma\text{-G}}(x)\,=\,\sum_{j=0}^\infty w_{j}^{\Gamma\text{-G}}\,\,\Pi_{a+j}(x).
+\end{equation}
+Here,
+$$w_j^{\Gamma\text{-G}}=w_j^{\Gamma\text{-G}}(a)=\frac{\varphi_{j}(a)}{(a+j)},$$
 \begin{equation*}\label{coeficientes}
@@
 \quad\,
-\varphi_i(a)=\frac{(a-1)}{\Gamma(a)}\,\psi_{i-1}(i+a-2),\quad i\geq 1,
+\varphi_j(a)=\frac{(a-1)}{\Gamma(a)}\,\psi_{j-1}(j+a-2),\quad j\geq 1,
 \end{equation*}
 and
-$\psi_{i-1}(\cdot)$ are the {\color{green}Stirling polynomials} defined by
 \begin{align*}\label{polinomios_ward}
@@
 \end{align*}
-where $H^{m}_{n}$ are positive integers given recursively by
-$H^{m}_{n+1}=(2n+1-m)H^{m}_{n} + (n-m+1)H^{m-1}_{n}$, with
-$H^0_0=1$, $H^{0}_{n+1}=1\times 3\times 5\times\cdots\times(2n+1)$, $H^{n}_{n+1}=1$.
+is the Stirling polynomial, $H^{m}_{n+1}=(2n+1-m)H^{m}_{n} + (n-m+1)H^{m-1}_{n}$ is a positive integer,
+$H^0_0=1$, $H^{0}_{n+1}=1\times 3\times 5\times\cdots\times(2n+1)$ and $H^{n}_{n+1}=1$.
+
+By inserting \eqref{EXP33} in Equation \eqref{EXP44} and via a result for a power series raised to a positive integer (Gradshteyn and
+Ryzhik, 2000), the expansion for the cdf of the MO-$\Gamma$-G distribution reduces to
+\begin{align*}
+F_{\text{MO}-\Gamma\text{-G}}(x)&=\sum_{i=0}^{\infty}\,w_{i}^{\text{MO-}\Gamma}\,G(x)^{(i+1)a}\,\left[\sum_{j=0}^{\infty}\,w_{j}^{\Gamma\text{-G}}\,G(x)^{j}\right]^{i+1}\\
+&=\sum_{i=0}^{\infty}\,w_{i}^{\text{MO-}\Gamma}\,G(x)^{(i+1)a}\,\sum_{j=0}^{\infty}\,c_{i+1,j}\,G(x)^{j} =\sum_{i,j=0}^\infty d_{i,j}\,\Pi_{(i+1)a+j}(x),
+\end{align*}
+where $d_{i,j}=d_{i,j}(a,\theta)=w_{i}^{\text{MO-G}}\,c_{i+1,j}(a)$, $c_{i+1,0}(a)=(w_{0}^{\Gamma\text{-G}})^{i+1}$ and, for $m \ge 1$,
+$c_{i+1,m}(a)=\frac{1}{m w_{0}^{\Gamma\text{-G}}}\,\sum^{m}_{r=1}\,\left[r(i+2)-m\right]\,w_{r}^{\Gamma\text{-G}}\,c_{i+1,m-r}(a)$.
+
+By differentiating the last equation, the expansion for the MO-$\Gamma$-G density follows as
+\begin{equation}\label{lcom}
+f_{\text{MO}-\Gamma\text{-G}}(x)=\sum_{i,j=0}^\infty d_{i,j}\,\pi_{(i+1)a+j}(x).
+\end{equation}
+
+So, some structural properties of the proposed family can be determined from the double linear combination (\ref{lcom})
+and those properties of the exp-G distribution. In most applications, the indices $i$ and $j$ can vary up to five.
+
+\subsection{Some quantities}
+
+Hereafter, let $T_{i,j}\sim$exp-G$[(i+1)a+j]$. The $n$th moment of $X$ can be obtained from (\ref{lcom}) as
+\begin{eqnarray}\label{moment}
+\displaystyle
+\mu_n^{\prime}=E(X^n)=\sum_{i,j=0}^\infty d_{i,j}\,E(T_{i,j})=\sum_{i,j=0}^\infty \,[(i+1)a+j-1]\,d_{i,j}\,\tau[n,(i+1)a+j-1],
+\end{eqnarray}
+where
+\begin{eqnarray*}
+\tau(n,a)=\int_{-\infty}^{\infty} x^n\,G(x)^{a}\,g(x)dx=\int_{0}^{1} Q_G(u)^n\,u^a d u.
+\end{eqnarray*}
+
+Expressions for moments of several exponentiated distributions can be found in the papers
+cited in Tahir and Nadarajah (2015, Table 1). We give just one example from Equation (\ref{moment})
+by taking the exponential distribution with rate $\lambda>0$ for the baseline G.
+It follows easily as
+\begin{eqnarray*}
+\mu_n^{\prime}= n!\,\lambda^n\,\sum_{i,j,m=0}^\infty \,\frac{(-1)^{n+m}\,[(i+1)a+j]\,d_{i,j}}{(m+1)^{n+1}}\,\binom{(i+1)a+j-1}{m}.
+\end{eqnarray*}
+
+A general expansion for the moment generating function (MGF) $M(t)=E(\rm{e}^{t\,X})$ of $X$ can be expressed from (\ref{lcom})
+\begin{eqnarray}\label{mgf}
+\displaystyle
+M(t)=\sum_{i,j=0}^{\infty} \,d_{i,j}\,M_{i,j}(t)=\sum_{i,j=0}^{\infty}\, [(i+1)a+j]\,d_{i,j}\,\rho(t,(i+1)a+j-1),
+\end{eqnarray}
+where $M_{i,j}(t)$ is the MGF of $Y_{i,j}$ and
+\begin{eqnarray*}
+\rho(t,a)=\int_{-\infty}^{\infty}\,\rm{e}^{t x}\,G(x)^{a}\,g(x) dx=\int_{0}^{1}\exp\left\{t\,Q_G(u)\right\}\,u^a d u.
+\end{eqnarray*}
+
+The MGFs of many MO-$\Gamma$-G distributions can be determined from Equation (\ref{mgf}).
+For example, the generating function of the MO-$\Gamma$-exponential with parameter $\lambda$
+(if $t<\lambda^{-1}$) is
+\begin{eqnarray*}
+\displaystyle
+M(t)=\sum_{i,j=0}^{\infty} [(i+1)a+j]\,d_{i,j}\,\,B((i+1)a+j,1-\lambda t).
+\end{eqnarray*}
+
+For empirical purposes, the shape of many distributions can be usefully described by
+the incomplete moments. These moments play an important role for measuring
+inequa\-lity. For example, the mean deviations and Lorenz and Bonferroni curves depend upon the first incomplete moment of the distribution.
+The $n$th incomplete moment of $X$ can be expressed as
+{\small
+\begin{eqnarray}\label{incomplete}
+\displaystyle
+\qquad
+m_{n}(y)=\int_{-\infty}^y x^n\,f_{X}(x) dx = \sum_{i,j=0}^{\infty} [(i+1)a+j]\,d_{i,j}\,\int_{0}^{G(y)}\,Q_G(u)^n\, u^{(i+1)a+j-1}\,du.
+\end{eqnarray}
+}
+The definite integral in (\ref{incomplete}) can be evaluated for most baseline G distributions.
 
 \section{Conclusions}\label{conclusions}
+
+A new family of distributions called the Marshall and Olkin-Gamma-G family with two shape parameters is introduced. The estimation of the unknown
+parameters is done via the maximum likelihood method and a simulation study is conducted to verify its adequacy. Additionally, the usefulness
+of the proposed family is shown empirically by means of two applications to real data.
+
+\appendix
+
+\section{Appendix: Simulation code}\label{ap:simulation}
+
+The script below is used to perform the simulations whose results are given in Table \ref{tab:bias} of Section \ref{sec:simulation}.
+It is developed a script using the programming language {\sf R} to be used in other simulations or even to check the results presented in this paper.
+
+\lstinputlisting[language=R, caption={Monte-Carlo simulations for different sample sizes.}, numbers=left,
+stepnumber=1,
+showspaces=false,
+tabsize=4,
+basicstyle=\scriptsize,
+backgroundcolor=\color{lbcolor},
+showstringspaces=false]{new_code_dagum.R}
 
@@
 \item
+
+Gradshteyn IS, Ryzhik IM: Table of Integrals, Series and Products. Sixth edition. San Diego: Academic Press (2000).
+
+\item
 R.C. Gupta, R.D. Gupta, P.L. Gupta:
@@
 Technometrics {\bf 37}(4) 436-445 (1995).
+
+\item 
+P.
+R.
+D.
+Marinho,  R.
+B.
+Silva,  M.
+Bourguignon, G.
+M.
+Cordeiro,  S.
+Nadarajah.
+AdequacyModel: An R package for probability distributions and general purpose optimization.
+PloS one, {\bf 14}(8), e0221487 (2019).
+
+\item
+R Core Team. R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL
+\url{https://www.R-project.org/} (2020).
 

### 2020-09-29 quantilica.tex
update

--- 2020-09-28 paper_27_09_2020/paper_27_09_2020.tex
@@
 \usepackage{graphicx}
-\usepackage{hyperref}
 \usepackage{color}
@@
 \usepackage{float}
-\usepackage{listings}
 %\usepackage[dvips]{graphicx, color}
@@
 \setlength\topmargin{-1.5cm} \setlength\oddsidemargin{0.0cm}
-\setlength\evensidemargin{0.0cm} \setlength{\textwidth}{15cm}
+\setlength\evensidemargin{0.0cm} \setlength{\textwidth}{16cm}
 \setlength{\textheight}{25cm}
@@
 
-\hypersetup{
-	colorlinks=true,
-	linkcolor=blue,
-	filecolor=magenta,      
-	urlcolor=cyan,
-}
-
-\urlstyle{same}
-
 \begin{document}
@@
 \vspace{0.5in}
-\noindent {\bf Key Words}:  Distribution family;  mathematical properties; simulations; applications.\\ \\
+\noindent {\bf Key Words}: \\ \\
 %\noindent {\bf JEL Codes}: C16, G1 \\ \\
@@
 
-\vspace{0.6cm}
-
-\begin{figure}[H]
-\begin{center}
-(a)\hspace{3.5cm} (b)\\
-\includegraphics[scale=.3]{density.pdf}
-\includegraphics[scale=.3]{hazard.pdf}\\
-\vspace{-0.5cm}
-\caption{(a) Curves for the MO-$\Gamma$-W density. (b) Curves for the MO-$\Gamma$-W hazard.\label{formas}}
-\end{center}
-\end{figure}
-
-\vspace{0.6cm}
-
-The CDF \eqref{CDF_MO-Gamma-G} can be easily inverted to determine the quantile function (QF) of the MO-$\Gamma$-G distribution,
-say $x=Q_{X}(u)$, in terms of the baseline QF $Q_G(u)$. Let $u$ be a uniform $U(0,1)$ random variate. By using \eqref{CDF_MO-Gamma-G}
-and letting $z=\gamma_{1}\left(a, -\log[1-G(x)]\right)$, it follows $z=z(u)=\theta u/[1-(1-\theta)u]$.
-Then, the QF of $X$ takes the form $x=Q_G\left(1-\rm{e}^{-v}\right)$, where $v=v(z)$ is an upper point
-corresponding to the quantile $z$ of a gamma density (with unit scale and shape $\alpha$).
+%\begin{figure}[h!]
+%\begin{center}
+%(a)\hspace{3.5cm} (b)\\
+%\includegraphics[scale=.3]{density.pdf}
+%\includegraphics[scale=.3]{hazard.pdf}\\
+%\vspace{-0.5cm}
+%\caption{(a) Curves for the MO-$\Gamma$-W density; (b) Curves for the MO-$\Gamma$-W hazard;\label{formas}}
+%\end{center}
+%\end{figure}
 
@@
 
+The CDF \eqref{CDF_MO-Gamma-G} can be easily inverted to calculate the QF of the MO-$\Gamma$-G distribution,
+say $x=Q_{X}(u)=F_X^{-1}(u)$ for $u \in (0,10$, in terms of the baseline QF $Q_G(\cdot)$. The inverse of
+$F_{X}(x)=u$, where $u$ is a uniform number in $(0,1)$ is easily obtained. By combining the inverses
+of Equations (\ref{CDF_MO})and \eqref{CDF_MO-Gamma-G}, $F_{X}(x)=u$ leads to
+$z=z(u)=\theta u/[1-(1-\theta)u]$ and $\gamma_{1}\left(a, -\log[1-G(x)]\right)=z(u)$.
+Then, the QF of $X$ can be expressed as
+$$x=Q_G\left(v(u)\right),$$
+where
+$$v(u)=1-\exp\left[-\gamma_1^{-1}\big(a,z(u)\big)\right],$$
+and $\gamma_1^{-1}(a,w)=Q^{-1}(a,1-w)$ is the inverse function of $\gamma_1(a,w)$. Some formulae for
+$Q^{-1}(a,1-w)$ are given in http:// functions.wolfram.com/ GammaBetaErf/ InverseGammaRegularized/.
+
 \section{Estimation}\label{estimation}
 
-The  MO-$\Gamma$-G family can be  fitted to real data using the {\bf AdequacyModel} package in the {\sf R} software.
+The  MO-$\Gamma$-G family can be  fitted to real data using the {\it AdequacyModel} package in the {\sf R} software.
 This packa\-ge does not require to define the log-likelihood function and it computes the MLEs, their standard errors (SEs)
@@
 
-Due to the impossibility of obtaining the MLEs in closed form, numerical methods to obtain the estimates that maximize $ \ell (\cdot) $ are necessary.
-Several programming languages and statistical software distributes functions and routines that make it easy to obtain numerical estimates by various interactive methods.
-In practice, obtaining the MLEs for the parameters that index a probability distribution are commonly obtained in this way, since the Newton and quasi-Newton methods produce satisfactory results under reasonable conditions of the object function, that is, when they do not impose conditions that disturb the convergence of the algorithms.
-
-To obtain the MLEs, the package {\bf AdequacyModel} of the programming language {\sf R} was used, see R Core Team (2020).
-This library, created and maintained by one of the authors of this paper, is widely cited by several papers in the field of statistics and serves as a basis for other library implementations available on the Comprehensive R Archive Network - CRAN.
-With it, in particular using the function {\tt goodness.fit} it is possible to pass an implementation {\sf R} of (\ref {PDF_MO-Gamma-G}), being in charge of the function {\tt goodness.fit} obtain $\ell (\cdot)$ by returning several measures of fit adequacy as well as MLEs.
-Further details regarding the {\bf AdequacyModel} package can be obtained from Marinho et al.
-(2019).
+The {\it AdequacyModel} package to maximize (\ref{loglik}) uses the PSO (particle swarm optimization)
+approach from the quasi-Newton BFGS, Nelder-Mead and simulated-annealing methods to maximize the log-likelihood function and it does not require
+initial values. More details are available at {\tt https://rdrr.io/cran/AdequacyModel/}.
 
@@
 		\hline
-		$n$ & $B(\hat{\theta})$ & $B(\hat{a})$ & $B(\hat{\alpha})$ & $B(\hat{\beta})$ & $B(\hat{p})$ & Time (mins)\\
+		$n$ & $B(\hat{\theta})$ & $B(\hat{a})$ & $B(\hat{\alpha})$ & $B(\hat{\beta})$ & $B(\hat{p})$ & \textbf{Time (mins)}\\
 		\hline
@@
 
-The {\bf AdequacyModel} is used to fit the distributions cited before to two real data sets. The SANN method, which is a
+The {\it AdequacyModel} package is used to fit the distributions cited before to two real data sets. The SANN method, which is a
 variant of simulated annealing (Belisle, 1992), is considered. The distributions are compared via the Anderson
-Darling (A$^{*}$) and Cram\'er Von Mises (W$^{*}$) statistics reported in the {\tt goodness.fit} function.
+Darling (A$^{*}$) and Cram\'er Von Mises (W$^{*}$) statistics reported in the {\it goodness.fit} function.
 
-For the first data set, a modification of the ``FoodExpenditure'' data from the {\bf betareg} package  is considered, which refers
+For the first data set, a modification of the ``FoodExpenditure'' data from the {\it betareg} package in {\sf R} software is considered, which refers
 to the proportions of income spent on food for a random sample of 38 households in a large US city (according to the package information).
@@
 As a second application, consider a data set collected in a pilot study about hypertension in the Dominican Republic
-in 1997 found in \url{http://biostat.mc.vanderbilt.edu/wiki/
-Main/DataSets}. The observations are the systolic blood pressure of persons who came to medical clinics in
+in 1997 found in http://biostat.mc.vanderbilt.edu/wiki/
+Main/DataSets. The observations are the systolic blood pressure of persons who came to medical clinics in
 several villages for a variety of complaints. The MLEs of the parameters, their SEs and the values of the statistics are
@@
 
-\lstinputlisting[language=R, caption={Monte-Carlo simulations for different sample sizes.}, numbers=left,
-stepnumber=1,
-showspaces=false,
-tabsize=4,
-basicstyle=\scriptsize,
-backgroundcolor=\color{lbcolor},
-showstringspaces=false]{new_code_dagum.R}
+%\lstinputlisting[language=R, caption={Monte-Carlo simulations for different sample sizes.}, numbers=left,
+%stepnumber=1,
+%showspaces=false,
+%tabsize=4,
+%basicstyle=\scriptsize,
+%backgroundcolor=\color{lbcolor},
+%showstringspaces=false]{new_code_dagum.R}
 
@@
 \item
-P.
-R.
-D.
-Marinho,  R.
-B.
-Silva,  M.
-Bourguignon, G.
-M.
-Cordeiro,  S.
-Nadarajah.
-AdequacyModel: An R package for probability distributions and general purpose optimization.
-PloS one, {\bf 14}(8), e0221487 (2019).
-
-\item
-R Core Team. R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL
-\url{https://www.R-project.org/} (2020).
-
-\item
 S. Nadarajah, G.M. Cordeiro, E.M.M. Ortega:

### 2020-09-30 paper_29_09_2020/paper_29_09_2020.tex
versao do dia 29-09-2020

--- 2020-09-28 paper_27_09_2020/paper_27_09_2020.tex
@@
 %\usepackage[skins,listings,breakable]{tcolorbox}
-
+\usepackage{xcolor}
 \usepackage{color}
@@
 This article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes. The family has only two
-extra shape parameters and can be a better alternative than other existing classes of distributions. Simulations are performed to verify the
+extra shape parameters and can be a better model  than other existing classes of distributions. Simulations are performed to verify the
 consistency of the estimators. Its flexibility is shown using two real data sets.
@@
 properties than existing distributions and for improving their goodness-of-fit statistics
-to the data under study.
+to the data under study. Many special distributions in these families are discussed by Tahir
+and Nadarajah (2015).
 
@@
 according to two sequential important gene\-rators. These families are important for modeling data
-in several engineering areas. Many special distributions in these families are discussed by Tahir
-and Nadarajah (2015).
+in several engineering areas.
 
@@
 respectively. By transforming the $Z_i$'s via the baseline QF by $W_i=Q_G(1-\rm{e}^{Z_i})$
-(for $i-1,\ldots,N$), Equation \eqref{densityMO} is defined the PDF of the minimum $W_1,\cdots,W_n$. 
+(for $i-1,\ldots,N$), Equation \eqref{densityMO} is defines the PDF of the minimum $W_1,\cdots,W_n$. 
 Making this double composition of the two generators, the proposed family absorbs the impacts of two different flexibilities 
@@
 $\Phi(x)$ and $\phi(x)$ are the CDF and PDF of the standard normal distribution. The density and hazard functions
-of the Marshall-Olkin-$\Gamma$-Weibull (MO-$\Gamma$-W) are displayed in Figure \ref{formas}, which provide
+of the Marshall-Olkin-$\Gamma$-Weibull (MO-$\Gamma$-W) defined by $h(x) = f(x)/(1-F(x))$ are displayed in Figure \ref{formas}, which provide
 more flexibility for these functions in relation to the baseline ones.
@@
 \begin{center}
-(a)\hspace{3.5cm} (b)\\
-\includegraphics[scale=.3]{density.pdf}
-\includegraphics[scale=.3]{hazard.pdf}\\
-\vspace{-0.5cm}
-\caption{(a) Curves for the MO-$\Gamma$-W density. (b) Curves for the MO-$\Gamma$-W hazard.\label{formas}}
+\includegraphics[scale =  0.39]{pdf-hazard.pdf}
+\caption{(A) MO-$\Gamma$-W density. (B) MO-$\Gamma$-W hazard.\label{formas}}
 \end{center}
@@
 
-The CDF \eqref{CDF_MO-Gamma-G} can be easily inverted to determine the quantile function (QF) of the MO-$\Gamma$-G distribution,
-say $x=Q_{X}(u)$, in terms of the baseline QF $Q_G(u)$. Let $u$ be a uniform $U(0,1)$ random variate. By using \eqref{CDF_MO-Gamma-G}
-and letting $z=\gamma_{1}\left(a, -\log[1-G(x)]\right)$, it follows $z=z(u)=\theta u/[1-(1-\theta)u]$.
-Then, the QF of $X$ takes the form $x=Q_G\left(1-\rm{e}^{-v}\right)$, where $v=v(z)$ is an upper point
-corresponding to the quantile $z$ of a gamma density (with unit scale and shape $\alpha$).
+The CDF \eqref{CDF_MO-Gamma-G} can be easily inverted to calculate the QF of the MO-$\Gamma$-G distribution,
+say $x=Q_{X}(u)=F_X^{-1}(u)$ for $u \in (0,10$, in terms of the baseline QF $Q_G(\cdot)$. The inverse of
+$F_{X}(x)=u$, where $u$ is a uniform number in $(0,1)$ is easily obtained. By combining the inverses
+of Equations (\ref{CDF_MO})and \eqref{CDF_MO-Gamma-G}, $F_{X}(x)=u$ leads to
+$z=z(u)=\theta u/[1-(1-\theta)u]$ and $\gamma_{1}\left(a, -\log[1-G(x)]\right)=z(u)$.
+Then, the QF of $X$ can be expressed as
+$$x=Q_G\left(v(u)\right),$$
+where
+$$v(u)=1-\exp\left[-\gamma_1^{-1}\big(a,z(u)\big)\right],$$
+and $\gamma_1^{-1}(a,w)=Q^{-1}(a,1-w)$ is the inverse function of $\gamma_1(a,w)$. Some formulae for
+$Q^{-1}(a,1-w)$ are given in \url{http:// functions.wolfram.com/ GammaBetaErf/ InverseGammaRegularized/}.
 
@@
 \hline
-{} & {} & {} \\
-\hline
 \end{tabular}
@@
 This library, created and maintained by one of the authors of this paper, is widely cited by several papers in the field of statistics and serves as a basis for other library implementations available on the Comprehensive R Archive Network - CRAN.
-With it, in particular using the function {\tt goodness.fit} it is possible to pass an implementation {\sf R} of (\ref {PDF_MO-Gamma-G}), being in charge of the function {\tt goodness.fit} obtain $\ell (\cdot)$ by returning several measures of fit adequacy as well as MLEs.
-Further details regarding the {\bf AdequacyModel} package can be obtained from Marinho et al.
+With it, in particular using the goodness.fit function, it is possible to provide an implementation {\sf R} of (\ref {PDF_MO-Gamma-G}), being in charge of this function, obtain $\ell(\cdot)$  by returning several measures of fit adequacy as well as the MLEs.
+Further details regarding this package can be obtained from Marinho et al.
 (2019).
@@
 
+{\color{red}
+
+Para gerar obervações da variável aleatória $X$ com distribuição $G$ optou-se em considerar  o algoritmo do método da aceitação e rejeição, muito útil quando a função quantilica envolvem funções complexas que podem trazer algumas imprecisões numéricas.
+Seja $X$ uma variável aleatória com PDF  $f$ e que desejamos gerar observações e $Y$  uma outra variável aleatória com PDF $h$ no mesmo suporte de $f$.
+A variável aleatória $Y$ é escolhida de tal forma que sabemos gerar suas observações.
+Então o algoritmo do método da aceitação e rejeição é definido pelos passos que seguem:
+
+\begin{enumerate}
+	\item Gere uma observação de $y$ proveniente de $Y$;
+	\item Gere uma observação $u$ de uma variável aleatória $U\sim \mathcal{U}(0, 1)$;
+	\item Se $u < \frac{f(y)}{cg(y)}$,  em que $c$ é uma constante real, aceite $x = y$; caso contrário rejeite $y$ como observação de $X$ e volte ao passo 1.
+\end{enumerate}
+A constante $c$ deve ser escolhida de tal forma que $\frac{f(y)}{cg(y)} \leq 1$.
+Considerando o caso discreto, em que também é possível aplicar o método da aceitação e rejeição, se $\{aceita\} = \{x = y\} = \{u < \frac{f(y)}{cg(y)}\}$, então,
+
+$$P(\{aceitar\}| Y = y) = \frac{P(\{aceitar\} \cap {Y=y})}{g(y)} = \frac{P\left( U \leq  \frac{f(y)}{cg(y)}\right)g(y)}{g(y)} = \frac{f(y)}{cg(y)}.$$
+
+Daí, pelo Teorema da Probabilidade Total, temos que:
+
+$$P(\{aceitar\}) = \sum_y P(\{aceitar\}| Y  = y) = \frac{1}{c}.$$
+
+Sendo assim, para minimizar o custo computacional de se gerar obervações de $X$ por meio de observações geradas de $Y$, colhe-se $c$ como o menor valor possível para maximizar a probabilidade de aceitação acima.
+Maiores detalhes do método da aceitação e rejeição poderá ser encontrado em Rizzo (2019).
+}
+
 \begin{table}[H]
 	\centering
-	\caption{Average biases of the MLEs obtained using the BFGS method.}\label{tab:bias}
+	\caption{Mean biases of the MLEs obtained using the BFGS method calculated from the Monte-Carlo simulation.}\label{tab:bias}
 	\begin{tabular}{rrrrrrr}
@@
 
+\item 
+Rizzo, Maria L. Statistical computing with R. CRC Press (2019).
+
 \end{description}

### 2020-09-30 Gerador.tex
update

--- 2020-09-30 paper_29_09_2020/paper_29_09_2020.tex
@@
 
-Para gerar obervações da variável aleatória $X$ com distribuição $G$ optou-se em considerar  o algoritmo do método da aceitação e rejeição, muito útil quando a função quantilica envolvem funções complexas que podem trazer algumas imprecisões numéricas.
-Seja $X$ uma variável aleatória com PDF  $f$ e que desejamos gerar observações e $Y$  uma outra variável aleatória com PDF $h$ no mesmo suporte de $f$.
-A variável aleatória $Y$ é escolhida de tal forma que sabemos gerar suas observações.
-Então o algoritmo do método da aceitação e rejeição é definido pelos passos que seguem:
+To generate observations from the random variable $X$ with density $f$, the well-known Acceptance-Rejection Algorithm for continuous random 
+variables, which is very useful when the quantile function involves complex functions that can lead to some numerical inaccuracies. For doing this, 
+another random variable $Y$ is chosen such that it can generate observations from a PDF $h$ with the same support as $f$.
+Then, the acceptance and rejection algorithm is defined by the following steps:
+\begin{enumerate}
+	\item Generate an outcome $y$ from $Y$;
+	\item Generate an observation $u$ from a random variable $U\sim \mathcal{U}(0,1)$;
+	\item If $u < \frac{f(y)}{c\, g(y)}$, where $c$ is a real constant, accept $x=y$; otherwise reject $y$ as an outcome from $X$ and return to 1.
+\end{enumerate}
 
-\begin{enumerate}
-	\item Gere uma observação de $y$ proveniente de $Y$;
-	\item Gere uma observação $u$ de uma variável aleatória $U\sim \mathcal{U}(0, 1)$;
-	\item Se $u < \frac{f(y)}{cg(y)}$,  em que $c$ é uma constante real, aceite $x = y$; caso contrário rejeite $y$ como observação de $X$ e volte ao passo 1.
-\end{enumerate}
-A constante $c$ deve ser escolhida de tal forma que $\frac{f(y)}{cg(y)} \leq 1$.
-Considerando o caso discreto, em que também é possível aplicar o método da aceitação e rejeição, se $\{aceita\} = \{x = y\} = \{u < \frac{f(y)}{cg(y)}\}$, então,
-
-$$P(\{aceitar\}| Y = y) = \frac{P(\{aceitar\} \cap {Y=y})}{g(y)} = \frac{P\left( U \leq  \frac{f(y)}{cg(y)}\right)g(y)}{g(y)} = \frac{f(y)}{cg(y)}.$$
-
-Daí, pelo Teorema da Probabilidade Total, temos que:
-
-$$P(\{aceitar\}) = \sum_y P(\{aceitar\}| Y  = y) = \frac{1}{c}.$$
-
-Sendo assim, para minimizar o custo computacional de se gerar obervações de $X$ por meio de observações geradas de $Y$, colhe-se $c$ como o menor valor possível para maximizar a probabilidade de aceitação acima.
-Maiores detalhes do método da aceitação e rejeição poderá ser encontrado em Rizzo (2019).
+The constant $c$ must be chosen in such a way that $\frac{f(y)}{c \,g (y)}\leq 1 $. 
+Thus, to minimize the computational cost of generating observations from $X$ through the generated observations from $Y$, $c$ is chosen 
+as the lowest possible value to maximize the likelihood of acceptance. Further details of this method can be found in Rizzo (2019).
 }

### 2020-09-30 code/plots/new_code_dagum.R

@@ -1,0 +1,219 @@
+# Title: Marshall Olkin Gamma-G (MOGG)
+# Author: Pedro Rafael D. Marinho
+
+# Loading libraries. ------------------------------------------------------
+library(parallel)
+library(tibble)
+library(pbmcapply)
+library(magrittr)
+library(purrr)
+library(xtable)
+
+# Baseline functions. -----------------------------------------------------
+pdf_dagum <- function(x, alpha, beta, p) 
+  alpha * p / x * (x / beta) ^ (alpha * p) / ((x / beta) ^ alpha + 1) ^ (p + 1)
+# integrate(f = pdf_dagum, lower = 0, upper = Inf, alpha = 1.2, beta = 1.6, p = 2.2)
+
+cdf_dagum <- function(x, alpha, beta, p) 
+  (1 + (x / beta) ^ (-alpha)) ^ (-p)
+# cdf_dagum(x = Inf, alpha = 1, beta = 4, p = 1)
+
+# This function creates MOGG functions. ----------------------------------
+pdf_mogg <- function(g, G){
+  # Using Closures.
+  function(x, theta, a, ...){
+    if (theta <= 0 || a <= 0) 
+      warning("The \"a\" and \"theta\" parameters must be greater than zero.")
+    num <- theta * (-log(1 - G(x = x, ...)))^(a - 1) * g(x = x, ...)
+    den <- gamma(a) * (theta + (1 - theta) * pgamma(-log(1 - G(x = x, ...)), a, 1L))^2
+    num/den
+  }
+}
+
+rdagum <- function(n = 1L, alpha, beta, p) {
+  beta * (runif(n = n, min = 0, max = 1) ^ (-1 / p) - 1) ^ (-1 / alpha)
+}
+
+pdf_mogdagum <- pdf_mogg(g = pdf_dagum, G = cdf_dagum)
+
+# MOG-Dagum --------------------------------------------------------------------
+rmogdagum <- function(n = 1L, theta, a, alpha, beta, p){
+  
+  cond_c <- function(x, theta, a, alpha, beta, p){
+    num <- pdf_mogdagum(x, theta, a, alpha, beta, p)
+    den <- pdf_dagum(x, alpha = alpha, beta = beta , p = p)
+    -num / den
+  }
+  
+  x_max <- optim(fn = cond_c, method = "BFGS", par = 1, theta = theta, a = a,
+                 alpha = alpha, beta = beta, p = p)$par
+  
[…]

### 2020-09-30 code/plots/plots.R

@@ -1,0 +1,222 @@
+  library(ggplot2)
+  library(cowplot)
+  
+  # Baseline functions. -----------------------------------------------------
+  pdf_weibull <- function(x, alpha, beta)
+   dweibull(x, shape = alpha, scale = beta)
+  
+  cdf_weibull <- function(x, alpha, beta)
+    pweibull(x, shape = alpha, scale = beta)
+  
+  # This function creates MOGW functions ----------------------------------
+  pdf_mogw <- function(g, G) {
+    # Using Closures.
+    function(x, theta, a, ...) {
+      if (theta <= 0 || a <= 0)
+        warning("The \"a\" and \"theta\" parameters must be greater than zero.")
+      num <-
+        theta * (-log(1 - G(x = x, ...))) ^ (a - 1) * g(x = x, ...)
+      den <-
+        gamma(a) * (theta + (1 - theta) * pgamma(-log(1 - G(x = x, ...)), a, 1L)) ^
+        2
+      num / den
+    }
+  }
+  
+  pdf_mogweibull <- pdf_mogw(g = pdf_weibull, G = cdf_weibull)
+  
+  hazard <- function(x, theta, a, alpha, beta) {
+    survival_f <- function(x, theta, a, alpha, beta)
+      1 - integrate(
+        f = pdf_mogweibull,
+        lower = .Machine$double.eps,
+        upper = x,
+        theta,
+        a,
+        alpha,
+        beta
+      )$value
+    
+    vectorize_survival_f <-
+      Vectorize(FUN = survival_f, vectorize.args = "x")
+    
+    pdf_mogweibull(x, theta, a, alpha, beta) / vectorize_survival_f(x, theta, a, alpha, beta)
+  }
+  
+  #  Plots Probability densiy function  -------------------------------------
+  cores <- c("Legenda 1" = "#FF6B58",
+             "Legenda 2" = "#FF4373",
+             "Legenda 3" = "#9239F6",
+             "Legenda 4" = "#E3D26D")
+  
+  base <- ggplot(data.frame(x = c(0, 10)), aes(x)) +
+    ggtitle(
+      "Probability density function",
+      subtitle = "With G following the Weibull distribution "
+    ) +
+    theme(
+      plot.title = element_text(face = "bold"),
+      axis.title = element_text(face = "bold"),
+      axis.text = element_text(face = "bold")
+    )
+  
+  p1 <- 
+    base +
+    stat_function(
+      fun = pdf_mogweibull,
[…]

### 2020-10-09 versao_09_10_2020/09_10_2020.tex
versão com linhas das tabelas corrigidas

--- 2020-09-30 Gerador.tex
@@
 \usepackage{color}
+\usepackage{xurl}
 \definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
@@
 
+\usepackage[hmargin=2.3cm,vmargin=2.3cm,bindingoffset=0.5cm]{geometry}
+
 \hypersetup{
@@
 \begin{abstract}\noindent
-This article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes. The family has only two
-extra shape parameters and can be a better model  than other existing classes of distributions. Simulations are performed to verify the
-consistency of the estimators. Its flexibility is shown using two real data sets.
+This article introduces a new family of distributions by combining the Marshall and Olkin-G and Gamma-G classes.
+The family has only two extra shape parameters and can be a better model than other well-known classes of distributions.
+Simulations are performed to illustrate the consistency of the estimators. Its flexibility is shown using two real data sets.
 \end{abstract}
@@
 \vspace{0.5in}
-\noindent {\bf Key Words}:  Distribution family;  mathematical properties; simulations; applications.\\ \\
+\noindent {\bf Key Words}: Adequacy model package; Marshall and Olkin distribution; R language; Weibull distribution\\ \\
 %\noindent {\bf JEL Codes}: C16, G1 \\ \\
@@
 \noindent $^{b}$ Department of Statistics, Federal University of Paraíba, João Pessoa, Brazil.\\
-E-mail:\emph{gausscordeiro@de.ufpe.br, maria@de.ufpe.br, pedro.rafael.marinho@gmail.com} \\
+E-mail:\emph{gauss@de.ufpe.br, maria@de.ufpe.br, pedro.rafael.marinho@gmail.com} \\
 
@@
 The mechanism by adding shape parameters to a baseline distribution has
-proved to be useful to make the generated distributions more flexible especially for studying tail
-properties than existing distributions and for improving their goodness-of-fit statistics
-to the data under study. Many special distributions in these families are discussed by Tahir
+proved to be useful to generate more flexible distributions, study their
+mathematical properties and improve the goodness-of-fit statistics
+to the data under study. Many special distributions in these recent families are discussed by Tahir
 and Nadarajah (2015).
@@
 Let $G(x)$ be the cumulative distribution function (CDF) of a
-baseline distribution and $g(x)=dG(x)/dx$ be the corresponding  probability density function (PDF) depending on a
-parameter vectot $\eta$. A generalized family are presented
+baseline distribution and $g(x)=dG(x)/dx$ be the corresponding probability density function (PDF)
+depending on a parameter vector $\eta$. A generalized family is introduced here
 with two additional shape parameters by transforming the CDF $G(x)$
-according to two sequential important gene\-rators. These families are important for modeling data
-in several engineering areas.
+according to two sequential important gene\-rators, which is important important
+for modeling data in several applied areas.
 
@@
 
-For $\theta=1$, $f_{\text{MO-G}}(x)$ is equal to $g(x)$.
-Equation \eqref{densityMO} represents the PDF of the minimum of $n$ iid random variables having density $g(x)$, say $T_1,\cdots,T_N$,
-where $N$ has a geometric distribution with probability parameters $\theta$ and $\theta^{-1}$ if $0<\theta<1$ and $\theta>1$,
-respectively.
+For $\theta=1$, $f_{\text{MO-G}}(x)$ is just equal to $g(x)$.
+Equation \eqref{densityMO} represents the PDF of the minimum of $n$ independent and identically distributed (iid) random variables
+having density $g(x)$, say $T_1,\cdots,T_N$, where $N$ has a geometric distribution with probability parameters $\theta$ and $\theta^{-1}$
+if $0<\theta<1$ and $\theta>1$, respectively.
 
 Tahir and Nadarajah (2015, Table 2) presented thirty distributions
-belonging to this family. It is easily generated from the baseline quantile function (QF) by
-$Q_{\text{MO-G}}(u)=Q_{G}\left(\theta u \left[\theta u+1-u\right]\right)$ for $u\in(0,1)$.
+belonging to this family. It can be easily generated via the quantile function (QF) of G as
+$Q_{
+\text{MO-G}}(u)=Q_{G}\left(\theta u \left[\theta u+1-u\right]\right)$ for $u\in(0,1)$.
 
 Marshall and Olkin considered the exponential and Weibull distributions for the baseline G and derived some
-structural properties of the generated distributions. The special case that G is an exponential distribution
-refers to a two-parameter competitive model to the Weibull and gamma distributions.
+structural properties of the generated distributions. The special case that G is an exponential
+distribution refers to a two-parameter competitive model to the Weibull and gamma distributions.
 
@@
 
-Each new $\Gamma$-G distribution follows from a given baseline G.
-For $a=1$, the $\Gamma$-G family reduces to G.
-If $Z$ is a gamma random variable with unit scale
-parameter and shape parameter $a>0$, then $W=Q_G(1-\rm{e}^{Z})$ has density (\ref{PDF_Ga}). So,
-the $\Gamma$-G distribution is easily generated from the gamma distribution and the QF of G.
+Each new $\Gamma$-G distribution follows from a specified baseline G. For $a=1$, the $\Gamma$-G family
+reduces to G. Let $Z$ be a gamma random variable with unit scale and shape parameter $a>0$; then $W=Q_G(1-\rm{e}^{Z})$
+has density (\ref{PDF_Ga}). So, the $\Gamma$-G distribution is easily generated from the gamma distribution and the QF of G.
 
-The remaining of the paper is addressed as follows. Section \ref{sec:MOGaG} introduces the {\it Marshall and Olkin-Gamma-G} (MO-$\Gamma$-G)
-family and presents some special models. The maximum likelihood estimates (MLEs) of the parameters of the new family is addressed
-in Section \ref{estimation}. Some simulations ate performed in Section \ref{sec:simulation} to estimate the biases of the MLEs. Two
-empirical applications illustrate the potentiality of the proposed family in Section \ref{applications}. A variety of theoretical properties are derived
-in Section \ref{properties}. Some conclusions remarks are offered in Section \ref{conclusions}.
+The remainder of this paper is organized as follows. Section \ref{sec:MOGaG} introduces the {\it Marshall and Olkin-Gamma-G} (MO-$\Gamma$-G)
+families and presents some special models. The maximum likelihood estimates (MLEs) is addressed
+in Section \ref{estimation}. Some simulations are reported in Section \ref{sec:simulation} which provide numerical evidence on the biases
+of the estimators in finite samples. Two empirical applications show the potentiality of the new family in
+Section \ref{applications}. Some structural properties are derived in Section \ref{properties}.
+Conclusions remarks are offered in Section \ref{conclusions}.
 
@@
 
-By combining Equations (\ref{CDF_MO}) and (\ref{CDF_Ga}), the CDF of the random variable $X\sim$MO-$\Gamma$-G
-representing the new family is defined by
+By combining Equations (\ref{CDF_MO}) and (\ref{CDF_Ga}), the CDF of the random variable $X\sim$MO-$\Gamma$-G of the new family is defined by
 \begin{equation}\label{CDF_MO-Gamma-G}
@@
 
-By differentiating (\ref{CDF_MO-Gamma-G}), the PDF of $X$ follows as
+By differentiating (\ref{CDF_MO-Gamma-G}), the PDF of $X$ can be expressed as
 \begin{equation}\label{PDF_MO-Gamma-G}
@@
 Table \ref{tabspecial1} provides some special cases of (\ref{PDF_MO-Gamma-G}), where
-$\Phi(x)$ and $\phi(x)$ are the CDF and PDF of the standard normal distribution. The density and hazard functions
-of the Marshall-Olkin-$\Gamma$-Weibull (MO-$\Gamma$-W) defined by $h(x) = f(x)/(1-F(x))$ are displayed in Figure \ref{formas}, which provide
+$\Phi(x)$ and $\phi(x)$ are the CDF and PDF of the standard normal distribution. The density and hazard
+functions of the Marshall-Olkin-$\Gamma$-Weibull (MO-$\Gamma$-W) are displayed in Figure \ref{formas}, which provide
 more flexibility for these functions in relation to the baseline ones.
@@
 The CDF \eqref{CDF_MO-Gamma-G} can be easily inverted to calculate the QF of the MO-$\Gamma$-G distribution,
-say $x=Q_{X}(u)=F_X^{-1}(u)$ for $u \in (0,10$, in terms of the baseline QF $Q_G(\cdot)$. The inverse of
-$F_{X}(x)=u$, where $u$ is a uniform number in $(0,1)$ is easily obtained. By combining the inverses
-of Equations (\ref{CDF_MO})and \eqref{CDF_MO-Gamma-G}, $F_{X}(x)=u$ leads to
-$z=z(u)=\theta u/[1-(1-\theta)u]$ and $\gamma_{1}\left(a, -\log[1-G(x)]\right)=z(u)$.
-Then, the QF of $X$ can be expressed as
+say $x=Q_{X}(u)=F_X^{-1}(u)$ in terms of $Q_G(\cdot)$, where $u$ is a uniform number in $(0,1)$.
+The inverse of $F_{X}(x)=u$ is easily obtained by combining the inverses
+of Equations (\ref{CDF_MO}) and \eqref{CDF_MO-Gamma-G}. Equation $F_{X}(x)=u$ leads to
+$z=z(u)=\theta u/[1-(1-\theta)u]$ and $\gamma_{1}\left(a, -\log[1-G(x)]\right)=z(u)$,
+and then the QF of $X$ has a simple form
 $$x=Q_G\left(v(u)\right),$$
@@
 {} & {} & {} \\
-\textbf{Weibull} &  $G(x)=1-\exp(-(\lambda x)^\gamma),\,\lambda,\gamma>0$ & $f_X(x)=\frac{\theta\,\gamma\lambda^{a\,\gamma}x^{a\,\gamma-1}\exp\{-(\lambda\,\gamma)^\gamma\}}{\Gamma (a)\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x)^\gamma]\}^2}$ \\
+\textbf{Weibull} &  $G(x)=1-\exp(-(x/\beta)^\alpha),\,\alpha,\beta>0$ & $f_X(x)=\frac{\alpha \theta x^{\alpha-1}\,[(x/\beta)^{\alpha}]^{a-1}\,\exp[-(x/\beta)^{\alpha}]}{\beta^{\alpha}\,\Gamma (a)\{\theta+(1-\theta)\gamma_1[a,(x/\beta)^\alpha]\}^2}$ \\
 {} & {} & {} \\
@@
 \end{tabular}
-\caption{Special Distributions in the  MO-$\Gamma$-G family.}
+\caption{Special distributions in the  MO-$\Gamma$-G family.}
 \end{table}
@@
 The  MO-$\Gamma$-G family can be  fitted to real data using the {\bf AdequacyModel} package in the {\sf R} software.
-This packa\-ge does not require to define the log-likelihood function and it computes the MLEs, their standard errors (SEs)
-and the formal statistics defined in Section \ref{applications}. It is necessary to provide the
+This packa\-ge does not require the log-likelihood function and it computes the MLEs, their standard errors (SEs)
+and the formal statistics defined in Section \ref{applications}. It is only necessary to provide the
 PDF and CDF of the distribution to be fitted to a data set.
 
-For example, if $x_i$ is one observation from (\ref{PDF_MO-Gamma-G}) and $\etn$ is a $q$-parameter vector specifying $G(\cdot)$,
+If $x_i$ is one observation from (\ref{PDF_MO-Gamma-G}) and $\etn$ is a $q$-parameter vector specifying $G(\cdot)$,
 the log-likelihood function for $\boldsymbol{\theta}^\top=(a,\theta,\etn^\top)$ from $n$ observations is
@@
 
-Due to the impossibility of obtaining the MLEs in closed form, numerical methods to obtain the estimates that maximize $ \ell (\cdot) $ are necessary.
-Several programming languages and statistical software distributes functions and routines that make it easy to obtain numerical estimates by various interactive methods.
-In practice, obtaining the MLEs for the parameters that index a probability distribution are commonly obtained in this way, since the Newton and quasi-Newton methods produce satisfactory results under reasonable conditions of the object function, that is, when they do not impose conditions that disturb the convergence of the algorithms.
+Due to the impossibility of obtaining the MLEs in closed form, numerical methods to maximize $ \ell (\cdot) $ are necessary.
+Several programming languages and statistical software provides functions and routines that make it easy to obtain numerical estimates by various
+interactive methods. In practice, obtaining the MLEs for the parameters that index a distribution are commonly obtained in this way,
+since the Newton and quasi-Newton methods produce satisfactory results under reasonable conditions of the object function, that is, when they do not impose conditions that disturb the convergence of the algorithms.
 
-To obtain the MLEs, the package {\bf AdequacyModel} of the programming language {\sf R} was used, see R Core Team (2020).
-This library, created and maintained by one of the authors of this paper, is widely cited by several papers in the field of statistics and serves as a basis for other library implementations available on the Comprehensive R Archive Network - CRAN.
-With it, in particular using the goodness.fit function, it is possible to provide an implementation {\sf R} of (\ref {PDF_MO-Gamma-G}), being in charge of this function, obtain $\ell(\cdot)$  by returning several measures of fit adequacy as well as the MLEs.
-Further details regarding this package can be obtained from Marinho et al.
-(2019).
+To obtain the MLEs, the {\bf AdequacyModel} package of the programming language {\sf R} was used, see R Core Team (2020). This library,
+created and updated by one of the authors of this paper, is widely cited by several papers in Statistics and serves as a basis for other library implementations available on the Comprehensive R Archive Network - CRAN.
+By using the goodness.fit function, it provides an implementation of (\ref{PDF_MO-Gamma-G})
+in {\sf R} giving $\ell(\cdot)$ by returning the MLEs and some adequacy measures of fit.
+Further details regarding this package can be obtained from Marinho et al. (2019).
 
@@
 precision of the estimates calculated numerically. For doing that, the biases of the estimators of the parameters of the
-MO-$\Gamma$-Dagum($\theta$, $a$, $\alpha$, $\beta$, $p$) distribution are determined, where $G\sim \mathrm {Dagum} (\alpha, \beta, p)$
+MO-$\Gamma$-Dagum($\theta$, $a$, $\alpha$, $\beta$, $p$) distribution are calculated, where $G\sim \mathrm {Dagum} (\alpha, \beta, p)$
 is the baseline distribution. All parameters are taken equal to one for different sample sizes reported in Table \ref{tab:bias}.
 
-Ten thousand Monte Carlo simulations are performed for each sample size to examine the numerical estimates calculated by the
+Ten thousand Monte Carlo simulations are performed for each sample size to calculate the estimates by the
 BFGS method. The figures in Table \ref{tab:bias} indicate that this method behaves well when the sample size increases.
@@
 requiring, on these hardware, a time of 14.36 hours to perform all simulations. The figures in Table \ref{tab:bias} reveal that the average
-biases of the MLEs could be very reduced only for $n> 2,000$.
+biases of the MLEs could be very reduced only for $n>1,000$.
 
-{\color{red}
-
-To generate observations from the random variable $X$ with density $f$, the well-known Acceptance-Rejection Algorithm for continuous random 
-variables, which is very useful when the quantile function involves complex functions that can lead to some numerical inaccuracies. For doing this, 
-another random variable $Y$ is chosen such that it can generate observations from a PDF $h$ with the same support as $f$.
+To generate observations from the random variable $X$ with density $f$, the well-known Acceptance-Rejection Algorithm for continuous random variables, which is very useful when the quantile function involves complex functions that can lead to some numerical inaccuracies.
+For doing this, another random variable $Y$ is chosen such that it can generate observations from a PDF $h$ with the same support as $f$.
 Then, the acceptance and rejection algorithm is defined by the following steps:
@@
 	\item Generate an outcome $y$ from $Y$;
-	\item Generate an observation $u$ from a random variable $U\sim \mathcal{U}(0,1)$;
+	\item Generate an observation $u$ from a uniform random variable $U$ in $(0,1)$;
 	\item If $u < \frac{f(y)}{c\, g(y)}$, where $c$ is a real constant, accept $x=y$; otherwise reject $y$ as an outcome from $X$ and return to 1.
@@
 
-The constant $c$ must be chosen in such a way that $\frac{f(y)}{c \,g (y)}\leq 1 $. 
-Thus, to minimize the computational cost of generating observations from $X$ through the generated observations from $Y$, $c$ is chosen 
-as the lowest possible value to maximize the likelihood of acceptance. Further details of this method can be found in Rizzo (2019).
-}
+The constant $c$ should be chosen in such a way that $\frac{f(y)}{c \,g (y)}\leq 1 $.
+Thus, to minimize the computational cost of generating observations from $X$ through the generated observations from $Y$,
+$c$ is chosen as the lowest possible value to maximize the likelihood of acceptance. Further details of this method can be found in Rizzo (2019).
 
@@
 Marshall-Olkin Weibull (MO-W) (Ahmed {\it et al.}, 2017), Marshall-Olkin Extended Weibull (MOE-W) (Cordeiro {\it et al.}, 2019),
-exponentiated Weibull (exp-W) (Mudholkar and Srivastava, 1993), gamma Weibull ($\Gamma$-W) Cordeiro {\it et al.}, 2016) and exponentiated
-generalized Weibull (EG-W) (Oguntunde {\it et al.}, 2015) (with $a=1$). Some of these distributions are widely used in practice.
+exponentiated Weibull (exp-W) (Mudholkar and Srivastava, 1993), gamma Weibull ($\Gamma$-W) (Cordeiro {\it et al.}, 2016) and 
+exponentiated generalized Weibull (EG-W) (Oguntunde {\it et al.}, 2015) (with $a=1$). Some of these distributions are widely used in practice.
 
@@
 For the first data set, a modification of the ``FoodExpenditure'' data from the {\bf betareg} package  is considered, which refers
-to the proportions of income spent on food for a random sample of 38 households in a large US city (according to the package information).
-Here, the household expenditures for food are considered and is given by
+to the proportions of income spent on food for a random sample of 38 households in a large US city.
+Here, the household expenditures for food are given by
 \begin{eqnarray*}
@@
 where $FoodExpenditure_{food}$ is the random variable corresponding to the household expenditures for food and $\#(\cdot)$ indicates the number of
-observations on this variable. The MLEs and their standard errors (SEs) (in parentheses) are listed in Table \ref{tab-ex1}.
-The statistics  W$^{*}$ and A$^{*}$ are also given in this table. The results indicate that the proposed model has better performance than the other
-seven fitted models.
+observations on this variable. The MLEs, their standard errors (SEs) (in parentheses) and the adequacy statistics are listed in Table \ref{tab-ex1}.
+The proposed model has a better fit to the data than the others.
 
@@
 
-As a second application, consider a data set collected in a pilot study about hypertension in the Dominican Republic
+As a second application, the systolic blood pressure of persons collected in a pilot study about hypertension in the Dominican Republic
 in 1997 found in \url{http://biostat.mc.vanderbilt.edu/wiki/
-Main/DataSets}. The observations are the systolic blood pressure of persons who came to medical clinics in
-several villages for a variety of complaints. The MLEs of the parameters, their SEs and the values of the statistics are
-listed in Table \ref{tab-ex2} for the previous distributions. By comparing the measures of these formal statistics,
-we conclude that the proposed distribution outperforms the rest of them.
+Main/DataSets} are analyzed. The MLEs, their SEs and the values of the statistics are
+reported in Table \ref{tab-ex2}. The proposed distribution outperforms the rest of them by comparing the measures of these formal 
+statistics.
 
@@
 
-In this section, some main mathematical properties are presented for the MO-$\Gamma$-G family
-based on a general linear representation for its density function, which are important
-to determine its mathematical properties from those of exponentiated-G (exp-G) distributions.
+Some main mathematical properties are addressed for the MO-$\Gamma$-G family
+based on a general linear representation for its density function and those properties 
+of exponentiated-G (exp-G) distributions.
 
@@
 
-By inserting \eqref{EXP33} in Equation \eqref{EXP44} and via a result for a power series raised to a positive integer (Gradshteyn and
+By inserting \eqref{EXP33} in Equation \eqref{EXP44} and via an equation for a power series raised to a positive integer (Gradshteyn and
 Ryzhik, 2000), the expansion for the cdf of the MO-$\Gamma$-G distribution reduces to
@@
 
-So, some structural properties of the proposed family can be determined from the double linear combination (\ref{lcom})
+So, some structural properties of the proposed family can be found from the double linear combination (\ref{lcom})
 and those properties of the exp-G distribution. In most applications, the indices $i$ and $j$ can vary up to five.
@@
 
-Hereafter, let $T_{i,j}\sim$exp-G$[(i+1)a+j]$. The $n$th moment of $X$ can be obtained from (\ref{lcom}) as
+Hereafter, let $T_{i,j}\sim$exp-G$[(i+1)a+j]$. The $n$th moment of $X$ follows from (\ref{lcom}) as
 \begin{eqnarray}\label{moment}
@@
 
-For empirical purposes, the shape of many distributions can be usefully described by
-the incomplete moments. These moments play an important role for measuring
-inequa\-lity. For example, the mean deviations and Lorenz and Bonferroni curves depend upon the first incomplete moment of the distribution.
-The $n$th incomplete moment of $X$ can be expressed as
-{\small
-\begin{eqnarray}\label{incomplete}
-\displaystyle
-\qquad
-m_{n}(y)=\int_{-\infty}^y x^n\,f_{X}(x) dx = \sum_{i,j=0}^{\infty} [(i+1)a+j]\,d_{i,j}\,\int_{0}^{G(y)}\,Q_G(u)^n\, u^{(i+1)a+j-1}\,du.
-\end{eqnarray}
-}
-The definite integral in (\ref{incomplete}) can be evaluated for most baseline G distributions.
+%For empirical purposes, the shape of many distributions can be usefully described by
+%the incomplete moments. These moments play an important role for measuring
+%inequa\-lity. For example, the mean deviations and Lorenz and Bonferroni curves depend upon the first incomplete moment of the distribution.
+%The $n$th incomplete moment of $X$ can be expressed as
+%{\small
+%\begin{eqnarray}\label{incomplete}
+%\displaystyle
+%\qquad
+%m_{n}(y)=\int_{-\infty}^y x^n\,f_{X}(x) dx = \sum_{i,j=0}^{\infty} [(i+1)a+j]\,d_{i,j}\,\int_{0}^{G(y)}\,Q_G(u)^n\, u^{(i+1)a+j-1}\,du.
+%\end{eqnarray}
+%}
+%The definite integral in (\ref{incomplete}) can be evaluated for most baseline G distributions.
 
@@
 A new family of distributions called the Marshall and Olkin-Gamma-G family with two shape parameters is introduced. The estimation of the unknown
-parameters is done via the maximum likelihood method and a simulation study is conducted to verify its adequacy. Additionally, the usefulness
-of the proposed family is shown empirically by means of two applications to real data.
+parameters is done via maximum likelihood and a simulation study is conducted to verify its adequacy. Additionally, the usefulness
+of the proposed family is shown empirically using two real data sets.
 
@@
 \item
-A. Alzaatreh, F. Famoye, C. Lee:
-A new method for generating families of continuous distributions.
+Alzaatreh, A., Famoye, F. and Lee, C. A new method for generating families of continuous distributions.
 Metron {\bf 71}(1) 63-79 (2013).
@@
 \item
-W. Barreto-Souza, A.J. Lemonte, G.M. Cordeiro:
-General results for the Marshall and Olkin's family of distributions.
+Barreto-Souza, W., Lemonte, A.J. and Cordeiro, G.M. General results for the Marshall and Olkin's family of distributions.
 Anais da Academia Brasileira de Ci\^{e}ncias {\bf 85}(1) 3-21 (2013).
@@
 \item
-Z.W. Birnbaum, S.C. Saunders:
-A new family of life distributions.
+Birnbaum, Z.W. and S.C. Saunders. A new family of life distributions.
 Journal of Applied Probability {\bf 6}(2) 319-327 (1969).
@@
 \item
-F. Castellares, A.J. Lemonte:
-A new generalized Weibull distribution gene\-rated by gamma random variables.
+Castellares, F. and Lemonte, A.J. A new generalized Weibull distribution gene\-rated by gamma random variables.
 Journal of the Egyptian Mathematical Society {\bf 23}(2) 382-390 (2015).
@@
 \item
-G.M. Cordeiro, M. de Castro:
-A new family of generalized distributions.
+Cordeiro, G.M. and de Castro, M. A new family of generalized distributions.
 Journal of Statistical Computation and Simulation {\bf 81}(7) 883-898 (2011).
@@
 \item
-N. Eugene, C. Lee, F. Famoye:
-Beta-normal distribution and its applications.
+Eugene, N., Lee, C. and Famoye, F. Beta-normal distribution and its applications.
 Communications in Statistics -- Theory and Methods {\bf 31}(4) 497-512 (2002).
@@
 
-Gradshteyn IS, Ryzhik IM: Table of Integrals, Series and Products. Sixth edition. San Diego: Academic Press (2000).
+Gradshteyn, I.S. and Ryzhik, I.M. Table of Integrals, Series and Products. Sixth edition. San Diego: Academic Press (2000).
 
 \item
-R.C. Gupta, R.D. Gupta, P.L. Gupta:
-Modeling failure time data by Lehmann alternatives.
+Gupta, R.C., Gupta, R.D. and Gupta, P.L. Modeling failure time data by Lehmann alternatives.
 Communications in Statistics -- Theory and Methods {\bf 27}(4) 887-904 (1998).
@@
 \item
-R.D. Gupta, D. Kundu:
-Exponentiated exponential family: an alternative to gamma and Weibull distributions.
+Gupta, R.D. and Kundu, D.Exponentiated exponential family: an alternative to gamma and Weibull distributions.
 Biometrical Journal {\bf 43}(1) 117-130 (2001).
@@
 \item
-A.J. Lemonte, G.M. Cordeiro, G. Moreno-Arenas:
-A new useful three-parameter extension of the exponential distribution.
+Lemonte, A.J., Cordeiro, G.M. and Moreno-Arenas,  G. A new useful three-parameter extension of the exponential distribution.
 Statistics {\bf 50}(2) 312-337 (2016).
@@
 \item
-A.W. Marshall, I. Olkin:
-A new method for adding a parameter to a family of distributions with
+Marinho, P.R.D., Silva, R.B., Bourguignon, M., Cordeiro,  G.
+M.
+and Nadarajah.
+S.
+Adequacy Model: An R package for probability distributions and general purpose optimization.
+PloS one, {\bf 14}(8), e0221487 (2019).
+
+\item
+Marshall, A.W. and Olkin, I. A new method for adding a parameter to a family of distributions with
 application to the exponential and Weibull families.
@@
 \item
-G.S. Mudholkar, D.K. Srivastava:
-The exponentiated Weibull family: a reanalysis of the bus-motor-failure data.
+Mudholkar, G.S. and Srivastava,  D.K. The exponentiated Weibull family: a reanalysis of the bus-motor-failure data.
 Technometrics {\bf 37}(4) 436-445 (1995).
@@
 \item
-P.
-R.
-D.
-Marinho,  R.
-B.
-Silva,  M.
-Bourguignon, G.
-M.
-Cordeiro,  S.
-Nadarajah.
-AdequacyModel: An R package for probability distributions and general purpose optimization.
-PloS one, {\bf 14}(8), e0221487 (2019).
+Nadarajah, S., Cordeiro, G.M. and Ortega, E.M.M. Some general results for the beta-modified Weibull distribution.
+Journal of Statistical Computation and Simulation {\bf 81}(10) 1211-1232 (2011).
+
+\item
+Nadarajah, S., Cordeiro, G.M. and Ortega, E.M.M. General results for the Kumaraswamy G distribution.
+Journal of Statistical Computation and Simulation {\bf 87}(7) 951-979 (2012).
+
+\item
+Nadarajah, S. and Gupta, A.K. The exponentiated gamma distribution with application to drought data.
+Calcutta Statistical Association Bulletin {\bf 59}(1-2) 29-54 (2007).
+
+\item
+Nadarajah, S. and  Haghighi, F. An extension of the exponential distribution.
+Statistics {\bf 45}(6) 543-558 (2011).
+
+\item
+Nadarajah, S. and Kotz,S. The exponentiated-type distributions.
+Acta Applicandae Mathematicae {\bf 92}(2) 97-111 (2006).
+
+\item
+Nichols, M.D. and Padgett, W.J. A Bootstrap control chart for Weibull percentiles.
+Quality and Reliability Engineering International {\bf 22}(2) 141-151 (2006).
 
@@
 \item
-S. Nadarajah, G.M. Cordeiro, E.M.M. Ortega:
-Some general results for the beta-modified Weibull distribution.
-Journal of Statistical Computation and Simulation {\bf 81}(10) 1211-1232 (2011).
-
-\item
-S. Nadarajah, G.M. Cordeiro, E.M.M. Ortega:
-General results for the Kumaraswamy G distribution.
-Journal of Statistical Computation and Simulation {\bf 87}(7) 951-979 (2012).
-
-\item
-S. Nadarajah, A.K. Gupta:
-The exponentiated gamma distribution with application to drought data.
-Calcutta Statistical Association Bulletin {\bf 59}(1-2) 29-54 (2007).
-
-\item
-S. Nadarajah, F. Haghighi:
-An extension of the exponential distribution.
-Statistics {\bf 45}(6) 543-558 (2011).
-
-\item
-S. Nadarajah, S. Kotz:
-The exponentiated-type distributions.
-Acta Applicandae Mathematicae {\bf 92}(2) 97-111 (2006).
-
-\item
-M.D. Nichols, W.J. Padgett:
-A Bootstrap control chart for Weibull percentiles.
-Quality and Reliability Engineering International {\bf 22}(2) 141-151 (2006).
-
-\item
-F. Proschan:
-Theoretical explanation of observed decreasing failure rate.
+Proschan, F. Theoretical explanation of observed decreasing failure rate.
 Technometrics {\bf 5}(3) 375-383 (1963).
@@
 \item
-M.M. Risti\'{c}, N. Balakrishnan:
-The gamma-exponentiated exponential distribution.
+Risti\'{c}, M.M. and Balakrishnan, N. The gamma-exponentiated exponential distribution.
 Journal of Statistical Computation and Simulation {\bf 82}(8) 1191-1206 (2012).
@@
 \item
-E.W. Stacy: A Generalization of the Gamma Distribution. Annals of Mathematical Statistics {\bf 33}(3) 1187-1192 (1962).
+Rizzo, M. L. Statistical computing with R. CRC Press (2019).
 
 \item
-M.H. Tahir, S. Nadarajah:
-Parameter induction in continuous univariate distributions: Well-established G families.
+Stacy, E.W. A Generalization of the Gamma Distribution. Annals of Mathematical Statistics {\bf 33}(3) 1187-1192 (1962).
+
+\item
+Tahir, M.H. and Nadarajah, S. Parameter induction in continuous univariate distributions: Well-established G families.
 Anais da Academia Brasileira de Ci\^{e}ncias {\bf 87}(2) 539-568 (2015).
@@
 \item
-K. Zografos, N. Balakrishnan:
-On families of beta-and generalized gamma-generated distribution and
+Zografos, K. and Balakrishnan, N. On families of beta-and generalized gamma-generated distribution and
 associate inference.  Statistical Methodology {\bf 6}(4) 344-362 (2009).
-
-\item
-Rizzo, Maria L. Statistical computing with R. CRC Press (2019).
 

### 2020-12-15 paper_15_12_2020/letter/letter.Rmd
update

---
author: Prof. Dr. Pedro Rafael D. Marinho
return-address: 
  - Department of Statistics
  - Federal University of Paraíba
  - João Pessoa, Paraíba - PB, Brazil
return-email: pedro.rafael.marinho@gmail.com
papersize: letter
yourmail: pedro.rafael.marinho@gmail.com
return-url: https://prdm0.rbind.io/
urlcolor: blue
linkcolor: red
address:
  - "**Editor-in-Chief: Enrico Colosimo**"
  - "**Brazilian Journal of Probability and Statistics - BJPS**"
  - ""
subject: "A new family of distributions: properties and applications"
opening: | 
  | Dear **BJPS** Editor,
closing: Kind regards,
signature: |
  | Prof. Dr. Pedro Rafael D. Marinho
  | (DSc in Statistics from Federal University of Pernambuco)
output: 
  komaletter::komaletter:
    keep_tex: true
---

we would like to present the paper entitled **A new family of distributions: properties and applications** to the BJPS. This article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes. The family has only two extra shape parameters and can be a better model than other existing classes of distributions. Simulations
are performed to verify the consistency of the estimators. Its flexibility is shown using two real data sets.

This article submitted to this journal is co-authored by researchers Gauss M.  Cordeiro (PhD in Statistics from Imperial College, 1982) of the Statistics Department of Federal University of Pernambuco and Dra. Maria do Carmo S. Lima Federal of the Statistics Department of Federal University of Pernambuco.

This material has not been submitted to any other Journal.

### 2020-12-15 paper_15_12_2020/letter/letter.tex
update

\documentclass[version=last,12pt,{"/home/prdm0/R/x86_64-pc-linux-gnu-library/4.0/komaletter/rmarkdown/templates/pdf/resources/maintainersDelight"},letterpaper,]{scrlttr2}

% For Debuging the Layout  ----------------------------------------------------
% \LoadLetterOption{visualize}
% \showfields{head,address,location,refline,foot}
% \setkomafont{field}{\color{blue}}
% -----------------------------------------------------------------------------

\usepackage{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
% \usepackage[margin=1in]{geometry} interfers with the areaset in my lco_default
%\usepackage[margin=1in]{geometry}
\usepackage[unicode=true]{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{
            pdfauthor={Prof.~Dr.~Pedro Rafael D. Marinho},
            colorlinks=true,
            linkcolor=red,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
% Make links footnotes instead of hotlinks:
\renewcommand{\href}[2]{#2\footnote{\url{#1}}}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\makeatletter
\usepackage{graphicx}
% grffile has become a legacy package: https://ctan.org/pkg/grffile
\IfFileExists{grffile.sty}{%
\usepackage{grffile}
}{}
% set default figure placement to htbp
\def\fps@figure{htbp}
\setkomavar{signature}{Prof.~Dr.~Pedro Rafael D. Marinho\\
(DSc in Statistics from Federal University of Pernambuco)}
\makeatother

\KOMAoptions{fromemail=true}
\setkomavar{fromemail}{pedro.rafael.marinho@gmail.com}
\KOMAoptions{fromurl=true}
\setkomavar{fromurl}{https://prdm0.rbind.io/}

\setkomavar{yourmail}{pedro.rafael.marinho@gmail.com}

\setkomavar{subject}{A new family of distributions: properties and
applications}
\setkomavar{fromname}{Prof.~Dr.~Pedro Rafael D. Marinho}
\setkomavar{fromaddress}{Department of Statistics\\Federal University of
Paraíba\\João Pessoa, Paraíba - PB, Brazil}

\begin{document}

\begin{letter}{\textbf{Editor-in-Chief: Enrico
Colosimo}\\\textbf{Brazilian Journal of Probability and Statistics -
BJPS}\\}
\opening{Dear \textbf{BJPS} Editor,}

we would like to present the paper entitled \textbf{A new family of
distributions: properties and applications} to the BJPS. This article
introduces a new family by combining the Marshall and Olkin-G and
Gamma-G classes. The family has only two extra shape parameters and can
be a better model than other existing classes of distributions.
Simulations are performed to verify the consistency of the estimators.
Its flexibility is shown using two real data sets.

This article submitted to this journal is co-authored by researchers
Gauss M. Cordeiro (PhD in Statistics from Imperial College, 1982) of the
Statistics Department of Federal University of Pernambuco and Dra. Maria
do Carmo S. Lima Federal of the Statistics Department of Federal
University of Pernambuco.

This material has not been submitted to any other Journal.

\closing{Kind regards,}

\end{letter}

\end{document}

### 2022-05-17 paper/letter/letter.Rmd
Added to reply letter.

--- 2020-12-15 paper_15_12_2020/letter/letter.Rmd
@@
 address:
-  - "**Editor-in-Chief: Enrico Colosimo**"
-  - "**Brazilian Journal of Probability and Statistics - BJPS**"
+  - "**Executive Editor**"
+  - "**REVSTAT**"
   - ""
@@
 opening: | 
-  | Dear **BJPS** Editor,
+  | Dear **REVSTAT** Executive Editor,
 closing: Kind regards,
@@
 
-we would like to present the paper entitled **A new family of distributions: properties and applications** to the BJPS.
+we would like to present the paper entitled **A new family of distributions: properties and applications** to the REVSTAT.
 This article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes.

### 2022-05-17 paper/letter/letter.tex
Added to reply letter.

--- 2020-12-15 paper_15_12_2020/letter/letter.tex
@@
 
-\begin{letter}{\textbf{Editor-in-Chief: Enrico
-Colosimo}\\\textbf{Brazilian Journal of Probability and Statistics -
-BJPS}\\}
-\opening{Dear \textbf{BJPS} Editor,}
+\begin{letter}{\textbf{Executive Editor}\\\textbf{REVSTAT}\\}
+\opening{Dear \textbf{REVSTAT} Executive Editor,}
 
 we would like to present the paper entitled \textbf{A new family of
-distributions: properties and applications} to the BJPS. This article
+distributions: properties and applications} to the REVSTAT. This article
 introduces a new family by combining the Marshall and Olkin-G and

### 2022-05-17 paper/reviews/answers/letter_answers.Rmd
Added to reply letter.

---
author: Prof. Dr. Pedro Rafael D. Marinho
return-address: 
  - Department of Statistics
  - Federal University of Paraíba
  - João Pessoa, Paraíba - PB, Brazil
return-email: pedro.rafael.marinho@gmail.com
papersize: letter
yourmail: pedro.rafael.marinho@gmail.com
return-url: https://prdm0.rbind.io/
urlcolor: blue
linkcolor: red
address:
  - "**Replies to reviewers**"
  - "**REVSTAT**"
  - ""
subject: "Marshall and Olkin-G and Gamma-G family of distribution: properties and applications"
opening: | 
  | Dear **REVSTAT** Executive Editor and Reviews,
closing: Kind regards,
signature: |
  | Prof. Dr. Pedro Rafael D. Marinho
  | (DSc in Statistics from Federal University of Pernambuco)
output: 
  komaletter::komaletter:
    keep_tex: true
---

in this letter, I will respond to each of the reviewers valuable contributions. We try to accept all suggestions, aiming at a significant improvement of our article. After each questioning, the respective answers will be given. As suggested by the second reviewer, the title of the paper was modified and better represents the proposal of the work.

**REVIEW I**:

1 – The equality $h(x)=f(x)/(1-F(x))$ is a well known relation between hazard, density and
survival functions. It is not a definition of density or risk functions. Therefore, in page 3,
line 12, the part of the sentence "defined by $h(x)=f(x)/(1-F(x))$" should be omitted.

*Response*:

2 – The expression (3.1) in page 6 corresponds to the log-likelihood of a MO-$\Gamma$-$G$
distribution, considering a Weibull distribution for $G$ (although there is an error in the
last sum of line 1), not a general distribution with a $\eta$ vector of parameters. Therefore,
the text or the expression should be written accordingly.

*Response*:

3 – It is not clear why it is considered the Weibull distribution (for $G$) in Figure 1,
eventually in expression (3.1) and in the applications, whereas for the simulations it is
chosen the Dagum distribution. These choices should be clarified.

*Response*: \textcolor{red}{Indeed, the way in which the application section was written suggests that an attempt was made to fix the $G\sim Weibull$ distribution as one of the necessary assumptions for the analysis. What actually happened is that for the datasets used, the Weibull distribution appeared to be a suitable distribution.}

\textcolor{red}{In order to remove some ambiguity, we opted to extend the simulation studies, where we also include the simulations, considering $G\sim Weibull$.
Indeed, the way in which the application section was written suggests that an attempt was made to fix the $G\sim Weibull$ distribution as one of the necessary assumptions for the analysis. What actually happened is that for the datasets used, the Weibull distribution appeared to be a suitable distribution.}

\textcolor{red}{In order to remove some ambiguity, we opted to extend the simulation studies, where we also include the simulations, considering $G\sim Weibull$.}

4 – As the Dagum distribution is used in the simulations, the generated PDF should also
be in Table 1.

*Response*: \textcolor{red}{Thanks for the observation. The Dagum distribution was included in Table 1.}

5 – As the `goodness.fit` function gives several statistics, the authors should justify why
they only chose the Anderson Darling and Cramer-von Mises statistics.

*Response*: \textcolor{red}{The use of the $A^*$ and $W^*$ statistics, Anderson-Darling and Cramer-von Mises statistics, respectively, corrected by Chen and Balakrishnan, in the paper entitled "A General Purpose Approximate Goodness-of-Fit Test" (see [link](https://www.tandfonline.com/doi/abs/10.1080/00224065.1995.11979578)) are suitable for comparing models that are not necessarily embedded. Therefore, considering the statistics returned by the `goodness.fit` function and considering the distributions compared, we understand that the statistics $A^*$ and $W^*$ are the most suitable for making the comparisons.}

\textcolor{red}{The **AdequacyModel** package was developed by one of the authors of this paper and was published at [https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0221487](https://journals .plos.org/plosone/article?id=10.1371/journal.pone.0221487). A code inspection of the `goodness.fit` function can be done by looking at the [link](https://github.com/prdm0/AdequacyModel/blob/master/R/goodness.fit.R) on GitHub, where it is hosted the development versioning of the package.}

*Minor points:*

1 – page 1, line 8 of Section 1, correct for "vector".

*Response*:

2 – page 2: confirm the expressions of $Q_{MO-G}(u)$ (line 9) and $W$ (line22).

*Response*:

3 – page 2, line -4 of Section 1, correct for "are".

*Response*:

4 – page 3, line 4, where it is written "gamma density unit scale and shape $a>0$," I suggest replacing it by "gamma density with unit scale parameter and shape parameter $a>0$,".

*Response*:

5 – page 3, $3^{rd}$ paragraph, replace "Table 2" by "Table 1".

*Response*:

6 – page 3, line-8, correct for "(0,1)".

*Response*:

7 – Figure 1: I suggest to change the lines to different types (even letting the colours as
they are) so as to enable the interpretation in a black and white print. Also, the letters
assigned to the parameters must agree with those in Table 1 (and, eventually, with those
in expression (3.1)).

*Response*: \textcolor{red}{Thanks a lot for the suggestion. All changes have been made. In fact, in a black and white print, solid lines will not help to differentiate the graphics.}

8 – page 3, lines-8,-7, where it is written "of the baseline $Q_F$ $Q_G(.)$." I suggest replacing
it by "of the $Q_F$ of the baseline distribution $G$, $Q_G(.).$".

*Response*:

9 – page 3, line-6, correct for "(1.1) and".

*Response*:

10 – page 7: the label of the table should be on the top, like the rest of the tables.

*Response*:

11 – page 11, line 4, correct for "distribution".

*Response*:

12 – In expressions (6.4) and (6.6), try to improve the output as the reference numbers
are to close to the formulas.

*Response*:

13 – I suggest to make the labels of Figure 1 and of tables in \LaTeX, not in R.

*Response*: \textcolor{red}{Thanks for the sugestion. The change suggestion has been implemented.}

14 – The references “R Core Team. …” and “Rizzo, …” are in the wrong order.

*Response*:

**REVIEW II**:

1 - The article is written in an overly summarized form and is sometimes unattractive to the
reader of any journal. That alone could lead to your rejection. In addition, I do suggest
reviewing the use of English carefully, and considerable rewording and pruning to make
the paper more concise and precise.

*Response*:

2 - When I see a new paper about a new distribution, I wonder if it is due to any interesting
properties or it arises naturally in some observable process like natural phenomena. I
would like to see these arguments defended more clearly in the article by the authors.
Could you do that?

*Response*:

3 - The bibliography does not have many recent publications such as Martinez-Florez et al.
(2020) and Magalhaes et al. (2020). I also suggest authors to create the state-of-art related
to this topic in the first section that definitively needs to be improved.

*Response*:

4 - I expect to see more detailed discussion in the simulation study and real data analysis.
Could you revise these sections, including the conclusion section that is actually weak?

5 - Suggestions: (i) Rewrite the paper title since the current one is nothing enlightening. How
about naming the proposed distribution?. (ii) Place section 6 (properties) before section 4
(simulation). (iii) Reorganize the presentation of the tables. (iv) Put the simulation code
in Supplementary material.

*Response*:

### 2022-05-17 paper/reviews/answers/letter_answers.tex
Added to reply letter.

\documentclass[version=last,12pt,{"/home/prdm0/R/x86_64-pc-linux-gnu-library/4.2/komaletter/rmarkdown/templates/pdf/resources/maintainersDelight"},letterpaper,]{scrlttr2}

% For Debuging the Layout  ----------------------------------------------------
% \LoadLetterOption{visualize}
% \showfields{head,address,location,refline,foot}
% \setkomafont{field}{\color{blue}}
% -----------------------------------------------------------------------------

\usepackage{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
% \usepackage[margin=1in]{geometry} interfers with the areaset in my lco_default
%\usepackage[margin=1in]{geometry}
\usepackage[unicode=true,pdfversion=1.6]{hyperref} % PrintScaling needs 1.6
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{
            pdfauthor={Prof.~Dr.~Pedro Rafael D. Marinho},
            colorlinks=true,
            linkcolor=red,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true,
            pdfprintscaling=None} % signal the PDF viewer "no auto scale", PDF >= 1.6
\urlstyle{same}  % don't use monospace font for urls
% make links footnotes instead of hotlinks (default)
\renewcommand{\href}[2]{#2\footnote{\url{#1}}}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\makeatletter
\usepackage{graphicx}
% grffile has become a legacy package: https://ctan.org/pkg/grffile
\IfFileExists{grffile.sty}{%
\usepackage{grffile}
}{}
% set default figure placement to htbp
\def\fps@figure{htbp}
\setkomavar{signature}{Prof.~Dr.~Pedro Rafael D. Marinho\\
(DSc in Statistics from Federal University of Pernambuco)}
\makeatother

\KOMAoptions{fromemail=true}
\setkomavar{fromemail}{pedro.rafael.marinho@gmail.com}
\KOMAoptions{fromurl=true}
\setkomavar{fromurl}{https://prdm0.rbind.io/}

\setkomavar{yourmail}{pedro.rafael.marinho@gmail.com}

\setkomavar{subject}{Marshall and Olkin-G and Gamma-G family of
distribution: properties and applications}
\setkomavar{fromname}{Prof.~Dr.~Pedro Rafael D. Marinho}
\setkomavar{fromaddress}{Department of Statistics\\Federal University of
Paraíba\\João Pessoa, Paraíba - PB, Brazil}

\begin{document}

\begin{letter}{\textbf{Replies to reviewers}\\\textbf{REVSTAT}\\}
\opening{Dear \textbf{REVSTAT} Executive Editor and Reviews,}

in this letter, I will respond to each of the reviewers valuable
contributions. We try to accept all suggestions, aiming at a significant
improvement of our article. After each questioning, the respective
answers will be given. As suggested by the second reviewer, the title of
the paper was modified and better represents the proposal of the work.

\textbf{REVIEW I}:

1 -- The equality \(h(x)=f(x)/(1-F(x))\) is a well known relation
between hazard, density and survival functions. It is not a definition
of density or risk functions. Therefore, in page 3, line 12, the part of
the sentence ``defined by \(h(x)=f(x)/(1-F(x))\)'' should be omitted.

\emph{Response}:

2 -- The expression (3.1) in page 6 corresponds to the log-likelihood of
a MO-\(\Gamma\)-\(G\) distribution, considering a Weibull distribution
for \(G\) (although there is an error in the last sum of line 1), not a
general distribution with a \(\eta\) vector of parameters. Therefore,
the text or the expression should be written accordingly.

\emph{Response}:

3 -- It is not clear why it is considered the Weibull distribution (for
\(G\)) in Figure 1, eventually in expression (3.1) and in the
applications, whereas for the simulations it is chosen the Dagum
distribution. These choices should be clarified.

\emph{Response}:
\textcolor{red}{Indeed, the way in which the application section was written suggests that an attempt was made to fix the $G\sim Weibull$ distribution as one of the necessary assumptions for the analysis. What actually happened is that for the datasets used, the Weibull distribution appeared to be a suitable distribution.}

\textcolor{red}{In order to remove some ambiguity, we opted to extend the simulation studies, where we also include the simulations, considering $G\sim Weibull$.
Indeed, the way in which the application section was written suggests that an attempt was made to fix the $G\sim Weibull$ distribution as one of the necessary assumptions for the analysis. What actually happened is that for the datasets used, the Weibull distribution appeared to be a suitable distribution.}

\textcolor{red}{In order to remove some ambiguity, we opted to extend the simulation studies, where we also include the simulations, considering $G\sim Weibull$.}

4 -- As the Dagum distribution is used in the simulations, the generated
PDF should also be in Table 1.

\emph{Response}:
\textcolor{red}{Thanks for the observation. The Dagum distribution was included in Table 1.}

5 -- As the \texttt{goodness.fit} function gives several statistics, the
authors should justify why they only chose the Anderson Darling and
Cramer-von Mises statistics.

\emph{Response}:
\textcolor{red}{The use of the $A^*$ and $W^*$ statistics, Anderson-Darling and Cramer-von Mises statistics, respectively, corrected by Chen and Balakrishnan, in the paper entitled "A General Purpose Approximate Goodness-of-Fit Test" (see [link](https://www.tandfonline.com/doi/abs/10.1080/00224065.1995.11979578)) are suitable for comparing models that are not necessarily embedded. Therefore, considering the statistics returned by the `goodness.fit` function and considering the distributions compared, we understand that the statistics $A^*$ and $W^*$ are the most suitable for making the comparisons.}

\textcolor{red}{The **AdequacyModel** package was developed by one of the authors of this paper and was published at [https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0221487](https://journals .plos.org/plosone/article?id=10.1371/journal.pone.0221487). A code inspection of the `goodness.fit` function can be done by looking at the [link](https://github.com/prdm0/AdequacyModel/blob/master/R/goodness.fit.R) on GitHub, where it is hosted the development versioning of the package.}

\emph{Minor points:}

1 -- page 1, line 8 of Section 1, correct for ``vector''.

\emph{Response}:

2 -- page 2: confirm the expressions of \(Q_{MO-G}(u)\) (line 9) and
\(W\) (line22).

\emph{Response}:

3 -- page 2, line -4 of Section 1, correct for ``are''.

\emph{Response}:

4 -- page 3, line 4, where it is written ``gamma density unit scale and
shape \(a>0\),'' I suggest replacing it by ``gamma density with unit
scale parameter and shape parameter \(a>0\),''.

\emph{Response}:

5 -- page 3, \(3^{rd}\) paragraph, replace ``Table 2'' by ``Table 1''.

\emph{Response}:

6 -- page 3, line-8, correct for ``(0,1)''.

\emph{Response}:

7 -- Figure 1: I suggest to change the lines to different types (even
letting the colours as they are) so as to enable the interpretation in a
black and white print. Also, the letters assigned to the parameters must
agree with those in Table 1 (and, eventually, with those in expression
(3.1)).

\emph{Response}:
\textcolor{red}{Thanks a lot for the suggestion. All changes have been made. In fact, in a black and white print, solid lines will not help to differentiate the graphics.}

8 -- page 3, lines-8,-7, where it is written ``of the baseline \(Q_F\)
\(Q_G(.)\).'' I suggest replacing it by ``of the \(Q_F\) of the baseline
distribution \(G\), \(Q_G(.).\)''.

\emph{Response}:

9 -- page 3, line-6, correct for ``(1.1) and''.

\emph{Response}:

10 -- page 7: the label of the table should be on the top, like the rest
of the tables.

\emph{Response}:

11 -- page 11, line 4, correct for ``distribution''.

\emph{Response}:

12 -- In expressions (6.4) and (6.6), try to improve the output as the
reference numbers are to close to the formulas.

\emph{Response}:

13 -- I suggest to make the labels of Figure 1 and of tables in \LaTeX,
not in R.

\emph{Response}:
\textcolor{red}{Thanks for the sugestion. The change suggestion has been implemented.}

14 -- The references ``R Core Team. \ldots{}'' and ``Rizzo, \ldots{}''
are in the wrong order.

\emph{Response}:

\textbf{REVIEW II}:

1 - The article is written in an overly summarized form and is sometimes
unattractive to the reader of any journal. That alone could lead to your
rejection. In addition, I do suggest reviewing the use of English
carefully, and considerable rewording and pruning to make the paper more
concise and precise.

\emph{Response}:

2 - When I see a new paper about a new distribution, I wonder if it is
due to any interesting properties or it arises naturally in some
observable process like natural phenomena. I would like to see these
arguments defended more clearly in the article by the authors. Could you
do that?

\emph{Response}:

3 - The bibliography does not have many recent publications such as
Martinez-Florez et al. (2020) and Magalhaes et al.~(2020). I also
suggest authors to create the state-of-art related to this topic in the
first section that definitively needs to be improved.

\emph{Response}:

4 - I expect to see more detailed discussion in the simulation study and
real data analysis. Could you revise these sections, including the
conclusion section that is actually weak?

5 - Suggestions: (i) Rewrite the paper title since the current one is
nothing enlightening. How about naming the proposed distribution?. (ii)
Place section 6 (properties) before section 4 (simulation). (iii)
Reorganize the presentation of the tables. (iv) Put the simulation code
in Supplementary material.

\emph{Response}:

\closing{Kind regards,}

\end{letter}

\end{document}

### 2022-05-17 code/simulations/new_code_dagum.R

@@ -8,6 +8,7 @@ library(pbmcapply)
 library(magrittr)
 library(purrr)
 library(xtable)
+library(glue)
 
 # Baseline functions. -----------------------------------------------------
 pdf_dagum <- function(x, alpha, beta, p) 
@@ -73,7 +74,7 @@ rmogdagum <- function(n = 1L, theta, a, alpha, beta, p){
 
 # Testing the rmogw Function ----------------------------------------------
 theta = 5
-a = 1
+a = 1.4
 alpha = 5
 beta = 1
 p = 1

### 2022-05-17 code/simulations/new_code_weibull.R

@@ -2,7 +2,13 @@
 # Author: Pedro Rafael D. Marinho
 
 # Loading libraries. ------------------------------------------------------
+library(parallel)
+library(tibble)
+library(pbmcapply)
+library(magrittr)
 library(purrr)
+library(xtable)
+library(glue)
 
 # Baseline functions. -----------------------------------------------------
 pdf_w <- function(x, alpha, beta) dweibull(x = x, shape = alpha, scale = beta)
@@ -20,12 +26,14 @@ pdf_mogg <- function(g, G){
   }
 }
 
+pdf_mogw <- pdf_mogg(pdf_w, cdf_w)
+
 # MOGW --------------------------------------------------------------------
 rmogw <- function(n = 1L, theta, a, alpha, beta){
   
   cond_c <- function(x, theta, a, alpha, beta){
     num <- pdf_mogw(x, theta, a, alpha, beta)
-    den <- dweibull(x, shape = 1, scale = 1)
+    den <- pdf_w(x, alpha = 1, beta = 1)
     -num/den
   }
   
@@ -36,7 +44,7 @@ rmogw <- function(n = 1L, theta, a, alpha, beta){
   
   criterion <- function(y, u){
     num <- pdf_mogw(y, theta, a, alpha, beta)
-    den <- dweibull(y, shape = alpha, scale = beta)
+    den <- pdf_w(y, alpha, beta)
     u < num / (c * den)
   }
   
@@ -56,18 +64,23 @@ rmogw <- function(n = 1L, theta, a, alpha, beta){
 }
 
 # Testing the rmogw Function ----------------------------------------------
-# theta = 1.2
-# a = 1.5
-# alpha = 1.7
-# beta = 1.4
-# pdf_mogw <- pdf_mogg(g = pdf_w, G = cdf_w)
-# sample_data <- rmogw(n = 250L, theta, a, alpha, beta)
-# x <- seq(0, 6, length.out = 500L)
-# hist(sample_data, probability = TRUE, xlab = "", main = "")
-# lines(x, pdf_mogw(x, theta, a, alpha, beta))
+theta = 1.2
+a = 1.5
+alpha = 1.7
+beta = 1.4
+pdf_mogw <- pdf_mogg(g = pdf_w, G = cdf_w)
+sample_data <- rmogw(n = 250L, theta, a, alpha, beta)
+x <- seq(0, 6, length.out = 500L)
+hist(sample_data, probability = TRUE, xlab = "", main = "")
[…]

### 2022-05-18 paper/paper.tex
Paper in journal layout

--- 2020-09-30 Gerador.tex
@@
-\documentclass[12pt,a4paper]{article} %437
-\usepackage{indentfirst}
+\documentclass[twoside,leqno,11pt]{article}
+\usepackage{revstat-v2}
 \usepackage{amsmath}
@@
 \usepackage{color}
-\makeatletter
-\makeatother
 \usepackage[utf8]{inputenc}
@@
 \usepackage{listings}
-%\usepackage[dvips]{graphicx, color}
-%\usepackage{subfigure}
-%\usepackage[skins,listings,breakable]{tcolorbox}
 \usepackage{xcolor}
 \usepackage{color}
-\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
 
-%TCIDATA{OutputFilter=latex2.dll}
-%TCIDATA{LastRevised=Friday, February 01, 2008 17:54:39}
-%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
-
-\setlength\topmargin{-1.5cm} \setlength\oddsidemargin{0.0cm}
-\setlength\evensidemargin{0.0cm} \setlength{\textwidth}{15cm}
-\setlength{\textheight}{25cm}
-
-\newtheorem{definition}{Definition}
-\newtheorem{theorem}{Theorem}
-\newtheorem{example}{Example}
-\newtheorem{corollary}{Corollary}
-\newtheorem{lemma}{Lemma}
-\newtheorem{proposition}{Proposition}
-\newenvironment{proof}{{\bf Proof:\ \ }}{\qed}
-\newcommand{\qed}{\rule{0.5em}{1.5ex}}
-\newcommand{\bfg}[1]{\mbox{\boldmath $#1$\unboldmath}}
-\newcommand{\dse} {\displaystyle}
-\newcommand{\real}{{I\!\!R}}
-\newcommand{\zern}{{\bf 0}}
-\newcommand{\Cn}{{\bf C}}
-\newcommand{\dn}{{\bf d}}
-\newcommand{\Dn}{{\bf D}}
-\newcommand{\Pn}{{\bf P}}
-\newcommand{\xn}{{\bf x}}
-\newcommand{\Un}{{\bf U}}
-\newcommand{\Kn}{{\bf K}}
-\newcommand{\Xn}{{\bf X}}
-\newcommand{\Vn}{{\bf V}}
-\newcommand{\vn}{{\bf v}}
-\newcommand{\bn}{{\bf b}}
-\newcommand{\an}{{\bf a}}
-\newcommand{\cn}{{\bf c}}
-\newcommand{\en}{{\bf e}}
-\newcommand{\sn}{{\bf s}}
-\newcommand{\Bn}{{\bf B}}
-\newcommand{\An}{{\bf A}}
-\newcommand{\yn}{{\bf y}}
-\newcommand{\Yn}{{\bf Y}}
-\newcommand{\Zn}{{\bf Z}}
-\newcommand{\zn}{{\bf z}}
-\newcommand{\Hn}{{\bf H}}
-\newcommand{\Gn}{{\bf G}}
-\newcommand{\Mn}{{\bf M}}
-\newcommand{\fn}{{\bf f}}
-\newcommand{\hn}{{\bf h}}
-\newcommand{\In}{{\bf I}}
-\newcommand{\Fn}{{\bf F}}
-\newcommand{\En}{{\bf E}}
-\newcommand{\Jn}{{\bf J}}
-\newcommand{\Ln}{{\bf L}}
-\newcommand{\mn}{{\bf m}}
-\newcommand{\rn}{{\bf r}}
-\newcommand{\un}{{\bf u}}
-\newcommand{\Rn}{{\bf R}}
-\newcommand{\Sn}{{\bf S}}
-\newcommand{\Tn}{{\bf T}}
-\newcommand{\GLn}{{\bf G \bf L}}
-\newcommand{\tn}{{\bf t}}
-\newcommand{\alpn}{{\mbox{\boldmath $\alpha$}}}
-\newcommand{\epsiln}{{\mbox{\boldmath $\epsilon$}}}
-\newcommand{\rhn}{{\mbox{\boldmath $\rho$}}}
-\newcommand{\betn}{{\mbox{\boldmath $\beta$}}}
-\newcommand{\deltn}{{\mbox{\boldmath $\delta$}}}
-\newcommand{\sigmn}{{\mbox{\boldmath $\beta$}}}
-\newcommand{\gamn}{{\mbox{\boldmath $\gamma$}}}
-\newcommand{\Gamn}{{\mbox{\boldmath $\Gamma$}}}
-\newcommand{\lamn}{{\mbox{\boldmath $\lambda$}}}
-\newcommand{\Lamn}{{\mbox{\boldmath $\Lambda$}}}
-\newcommand{\mun}{{\mbox{\boldmath $\mu$}}}
 \newcommand{\etn}{{\mbox{\boldmath $\eta$}}} 
-\newcommand{\tetn}{{\mbox{\boldmath $\theta$}}}
-\newcommand{\Tetn}{{\mbox{\boldmath $\Theta$}}}
-\newcommand{\Deltn}{{\mbox{\boldmath $\Delta$}}}
-\newcommand{\Phin}{{\mbox{\boldmath $\Phi$}}}
-\newcommand{\phin}{{\mbox{\boldmath $\phi$}}}
-\newcommand{\Psin}{{\mbox{\boldmath $\Psi$}}}
-\newcommand{\psin}{{\mbox{\boldmath $\psi$}}}
-\newcommand{\Upin}{{\mbox{\boldmath $\Upsilon$}}}
-\newcommand{\upin}{{\mbox{\boldmath $\upsilon$}}}
-\newcommand{\Sign}{{\mbox{\boldmath $\Sigma$}}}
-\newcommand{\Omegn}{{\mbox{\boldmath $\Omega$}}}
-\newcommand{\omegn}{{\mbox{\boldmath $\omega$}}}
-\newcommand{\eln}{{\mbox{\boldmath $\ell$}}}
-\newcommand{\taun}{{\mbox{\boldmath $\tau$}}}
-
 \hyphenation{ge-ne-ra-ted  hy-per-geo-me-tric  cha-rac-te-ri-ze}
 
-\hypersetup{
-	colorlinks=true,
-	linkcolor=blue,
-	filecolor=magenta,
-	urlcolor=cyan,
+\begin{document}
+\thispagestyle{firstpage}
+
+\vspace{-3.2cm}
+
+\noindent
+{\footnotesize {\sffamily REVSTAT~~--~~Statistical~~Journal\\[-1pt]
+		Volume 0, Number 0, Month 0000,
+		000-000}}
+% \thepage-\pageref{LastPage}}}   % requires \usepackage{lastpage}
+
+\vspace{1.5cm}
+\title{Marshall and Olkin-G and Gamma-G family of distribution: properties and applications
+	%\footnote{The opinions expressed in this text are those of the authors and do not necessarily reflect the views of any organization.}
 }
+\renewcommand{\titleheading}
+{Using the ``revstat-v2.sty" Package}  % --- on odd running heads
 
-\urlstyle{same}
+\author{\authoraddress{Maria do Carmo S. Lima \href{https://orcid.org/0000-0004-8882-8330}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}} 
+	{Department of Statistics,
+		Federal University of Pernambuco,\\
+        Pernambuco, Recife, Brazil
+		\ (maria@de.ufpe.br)}
+	\\
+	\authoraddress{Gauss M. Cordeiro \href{https://orcid.org/0000-0002-3052-6551}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}}
+	{Department of Statistics,
+		Federal University of Pernambuco,\\
+		Pernambuco, Recife, Brazil
+		\ (gauss@de.ufpe.br)}
+	\\
+	\authoraddress{Pedro Rafael D. Marinho \href{https://orcid.org/0000-0003-1591-8300}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}
+	\correspondingauthor}
+	{Department of Statistics,
+		Federal University of Paraíba,\\
+		Paraíba, João Pessoa, Brazil
+		\ (pedro.rafael.marinho@gmail.com)}
+}
+\renewcommand{\authorheading}
+{Author Pedro Rafael D. Marinho}  % --- on even running heads
 
-\begin{document}
-
-\begin{center}
-\section*{\centerline {A new family of distributions: properties and applications}}
-\vspace{0.3in}
-{\large Gauss M. Cordeiro$^a$ , Maria do Carmo S. Lima$^a$ and Pedro Rafael D. Marinho$^b$}\\
 %\vspace{0.3in}
@@
 %This Version: 27 January 2011\\
-\end{center}
 
-\begin{abstract}\noindent
+%-------------------------------------------------------------------------------
+% Just asking LaTeX to effectively do the title...
+%-------------------------------------------------------------------------------
+\maketitle
+%-------------------------------------------------------------------------------
+% Just asking LaTeX to numerate lines...
+%-------------------------------------------------------------------------------
+\setpagewiselinenumbers
+\modulolinenumbers[1]
+\linenumbers
+%%%%%%%%%%%%%%%%%%%%%%%%%% alteracao: Datas %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\noindent
+~~~~{\small{\sffamily Received:} December 2020 ~~~~~~{\sffamily Revised:} May 2022 ~~~~~~{\sffamily Accepted:} Month 0000}
+%%%%%%%%%%%%%%%%%%%%%%%%%% alteracao %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%-------------------------------------------------------------------------------
+% Abstract of the article...
+%-------------------------------------------------------------------------------
+\begin{abstract}
 This article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes. The family has only two
@@
 
-\vspace{0.5in}
-\noindent {\bf Key Words}:  Distribution family;  mathematical properties; simulations; applications.\\ \\
-%\noindent {\bf JEL Codes}: C16, G1 \\ \\
-\noindent $^{a}$  Department of Statistics, Federal University of Pernambuco, Recife, Brazil.\\
-\noindent $^{b}$ Department of Statistics, Federal University of Paraíba, João Pessoa, Brazil.\\
-E-mail:\emph{gausscordeiro@de.ufpe.br, maria@de.ufpe.br, pedro.rafael.marinho@gmail.com} \\
+%-------------------------------------------------------------------------------
+% Keywords...
+%-------------------------------------------------------------------------------
+\begin{keywords}
+ Distribution family;  mathematical properties; simulations; applications.
+\end{keywords}
+
+%-------------------------------------------------------------------------------
+% AMS classifications...
+%-------------------------------------------------------------------------------
+\begin{ams}
+	49A05, 78B26.
+\end{ams}
 
@@
 
-{\color{red}
-
-To generate observations from the random variable $X$ with density $f$, the well-known Acceptance-Rejection Algorithm for continuous random 
-variables, which is very useful when the quantile function involves complex functions that can lead to some numerical inaccuracies. For doing this, 
-another random variable $Y$ is chosen such that it can generate observations from a PDF $h$ with the same support as $f$.
+To generate observations from the random variable $X$ with density $f$, the well-known Acceptance-Rejection Algorithm for continuous random variables, which is very useful when the quantile function involves complex functions that can lead to some numerical inaccuracies.
+For doing this, another random variable $Y$ is chosen such that it can generate observations from a PDF $h$ with the same support as $f$.
 Then, the acceptance and rejection algorithm is defined by the following steps:
@@
 as the lowest possible value to maximize the likelihood of acceptance. Further details of this method can be found in Rizzo (2019).
-}
 
@@
 
-\lstinputlisting[language=R, caption={Monte-Carlo simulations for different sample sizes.}, numbers=left,
-stepnumber=1,
-showspaces=false,
-tabsize=4,
-basicstyle=\scriptsize,
-backgroundcolor=\color{lbcolor},
-showstringspaces=false]{new_code_dagum.R}
-
 \section*{References}

### 2022-05-18 paper/reviews/answers/letter_answers.Rmd
Paper in journal layout

@@
 *Response*:
+
+- (i) \textcolor{red}{Really, the title of the paper was really bad.
+We switched to **Marshall and Olkin-G and Gamma-G family of distribution: properties and applications**.
+We believe that the title now clarifies the paper's proposal better.}
+- (ii) \textcolor{red}{Change made. Thanks for the sugestion.}
+- (iii) \textcolor{red}{Thanks for the observation. The presentation of tables has been reorganized.}
+- (iv) \textcolor{red}{Thanks for the sugestion.We chose to put the code for the simulations in a repository on GitHub.
+Thus, we considerably reduced the number of pages in the article and made it easier for readers of the material to reuse the code.
+With the code on GitHub it is also possible to verify the implementation and validate the simulations obtained.
+To access the codes, see the} [link](https://github.com/prdm0/MOGG/tree/master/code/simulations).

### 2022-05-18 paper/reviews/answers/letter_answers.tex
Paper in journal layout

@@
-\documentclass[version=last,12pt,{"/home/prdm0/R/x86_64-pc-linux-gnu-library/4.2/komaletter/rmarkdown/templates/pdf/resources/maintainersDelight"},letterpaper,]{scrlttr2}
+\documentclass[version=last,12pt,{"maintainersDelight"},letterpaper,]{scrlttr2}
 
@@
 \def\fps@figure{htbp}
-\setkomavar{signature}{Prof.~Dr.~Pedro Rafael D. Marinho\\
-(DSc in Statistics from Federal University of Pernambuco)}
+\setkomavar{signature}{Prof.~Dr.~Pedro Rafael D. Marinho and co-authors}
 \makeatother
@@
 distribution: properties and applications}
-\setkomavar{fromname}{Prof.~Dr.~Pedro Rafael D. Marinho}
+\setkomavar{fromname}{Response letter from the authors}
 \setkomavar{fromaddress}{Department of Statistics\\Federal University of
@@
 \emph{Response}:
-\textcolor{red}{The use of the $A^*$ and $W^*$ statistics, Anderson-Darling and Cramer-von Mises statistics, respectively, corrected by Chen and Balakrishnan, in the paper entitled "A General Purpose Approximate Goodness-of-Fit Test" (see [link](https://www.tandfonline.com/doi/abs/10.1080/00224065.1995.11979578)) are suitable for comparing models that are not necessarily embedded.
-Therefore, considering the statistics returned by the `goodness.fit` function and considering the distributions compared, we understand that the statistics $A^*$ and $W^*$ are the most suitable for making the comparisons.}
+\textcolor{red}{The use of the $A^*$ and $W^*$ statistics, Anderson-Darling and Cramer-von Mises statistics, respectively, corrected by Chen and Balakrishnan, in the paper entitled "A General Purpose Approximate Goodness-of-Fit Test" (see   \url{https://www.tandfonline.com/doi/abs/10.1080/00224065.1995.11979578}) are suitable for comparing models that are not necessarily embedded.
+Therefore, considering the statistics returned by the \texttt{goodness.fit} function and considering the distributions compared, we understand that the statistics $A^*$ and $W^*$ are the most suitable for making the comparisons.}
 
-\textcolor{red}{The **AdequacyModel** package was developed by one of the authors of this paper and was published at [https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0221487](https://journals .plos.org/plosone/article?id=10.1371/journal.pone.0221487).
-A code inspection of the `goodness.fit` function can be done by looking at the [link](https://github.com/prdm0/AdequacyModel/blob/master/R/goodness.fit.R) on GitHub, where it is hosted the development versioning of the package.}
+\textcolor{red}{The  \textbf{AdequacyModel} package was developed by one of the authors of this paper and was published at   \url{https://journals .plos.org/plosone/article?id=10.1371/journal.pone.0221487}.
+A code inspection of the \texttt{goodness.fit} function can be done by looking at the   \href{https://github.com/prdm0/AdequacyModel/blob/master/R/goodness.fit.R}{link} on GitHub, where it is hosted the development versioning of the package.}
 
@@
 
+\begin{itemize}
+\item
+  \begin{enumerate}
+  \def\labelenumi{(\roman{enumi})}
+  \tightlist
+  \item
+    \textcolor{red}{Really, the title of the paper was really bad.
+We switched to \textbf{Marshall and Olkin-G and Gamma-G family of distribution: properties and applications}.
+We believe that the title now clarifies the paper's proposal better.}
+  \end{enumerate}
+\item
+  \begin{enumerate}
+  \def\labelenumi{(\roman{enumi})}
+  \setcounter{enumi}{1}
+  \tightlist
+  \item
+    \textcolor{red}{Change made. Thanks for the sugestion.}
+  \end{enumerate}
+\item
+  \begin{enumerate}
+  \def\labelenumi{(\roman{enumi})}
+  \setcounter{enumi}{2}
+  \tightlist
+  \item
+    \textcolor{red}{Thanks for the observation. The presentation of tables has been reorganized.}
+  \end{enumerate}
+\item
+  \begin{enumerate}
+  \def\labelenumi{(\roman{enumi})}
+  \setcounter{enumi}{3}
+  \tightlist
+  \item
+    \textcolor{red}{Thanks for the sugestion.We chose to put the code for the simulations in a repository on GitHub.
+Thus, we considerably reduced the number of pages in the article and made it easier for readers of the material to reuse the code.
+With the code on GitHub it is also possible to verify the implementation and validate the simulations obtained.
+To access the codes, see the
+    \url{https://github.com/prdm0/MOGG/tree/master/code/simulations}}.
+  \end{enumerate}
+\end{itemize}
+
 \closing{Kind regards,}

### 2022-05-18 paper/revstat_template_may2021/rs-examp-2021.tex
Paper in journal layout

%-------------------------------------------------------------------------------
% THIS FILE IS AN EXAMPLE ON HOW TO USE THE "revstat-v2.sty" PACKAGE...
% last modified: 2019/12/02
%-------------------------------------------------------------------------------
% REVSTAT - STATISTICAL JOURNAL
% Instituto Nacional de Estatística - Portugal
% https://www.ine.pt/revstat/inicio.html
% revstat@ine.pt
%-------------------------------------------------------------------------------
% The following 10 packages are pre-loaded:
%
%     graphicx   latexsym   enumerate   amsmath   amsfonts   amssymb
%     amsthm     amsopn     amstext     amscd     lineno     hyperref
%-------------------------------------------------------------------------------
\documentclass[twoside,leqno,11pt]{article}
\usepackage{revstat-v2}
%\usepackage{lastpage}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%% alteracao %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\thispagestyle{firstpage}

\vspace{-3.2cm}

\noindent
{\footnotesize {\sffamily REVSTAT~~--~~Statistical~~Journal\\[-1pt]
Volume 0, Number 0, Month 0000,
 000-000}}
% \thepage-\pageref{LastPage}}}   % requires \usepackage{lastpage}

\vspace{1.5cm}
%%%%%%%%%%%%%%%%%%%%%%%%%% alteracao %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-------------------------------------------------------------------------------
% Title of the article...
%-------------------------------------------------------------------------------
\title{TITLE - NO MORE THAN 120 CHARACTERS (WITH SPACES) - THIS FILE IS AN EXAMPLE ON HOW TO USE THE ``REVSTAT-V2.STY'' PACKAGE
%\footnote{The opinions expressed in this text are those of the authors and do not necessarily reflect the views of any organization.}
}
\renewcommand{\titleheading}
             {Using the ``revstat-v2.sty" Package}  % --- on odd running heads
%-------------------------------------------------------------------------------
% Author(s)' names and addresses...
%-------------------------------------------------------------------------------
\author{\authoraddress{Author Abcdefg
\href{https://orcid.org/0000-0004-8882-8330}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}
                        \correspondingauthor} % Corresponding author
                       {Some Department,
                       Some University,\\
                       A Planet Earth Country
                       \ (author.abcdefg@org.country)}
\\
        \authoraddress{Author Hijklmn \href{https://orcid.org/0000-0004-8882-8330}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}}
                      {Some Organization Department,
                       Some Institute,\\
                       Another Planet Earth Country
                       \ (author.hijklmn@org.country)}
}
\renewcommand{\authorheading}
             {Author Abcdefg \ and \ Author Hijklmn}  % --- on even running heads

%-------------------------------------------------------------------------------
% Just asking LaTeX to effectively do the title...
%-------------------------------------------------------------------------------
\maketitle
%-------------------------------------------------------------------------------
% Just asking LaTeX to numerate lines...
%-------------------------------------------------------------------------------
\setpagewiselinenumbers
\modulolinenumbers[1]
\linenumbers
%%%%%%%%%%%%%%%%%%%%%%%%%% alteracao: Datas %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
~~~~{\small{\sffamily Received:} Month 0000 ~~~~~~{\sffamily Revised:} Month 0000 ~~~~~~{\sffamily Accepted:} Month 0000}
%%%%%%%%%%%%%%%%%%%%%%%%%% alteracao %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
% Abstract of the article...
%-------------------------------------------------------------------------------
\begin{abstract}
A summary of less than one hundred words, followed by a maximum of six key words and the AMS 2000 subject classification. The paper should not have more than 25 pages. If necessary authors may consider a file for Supplementary Material, from their own responsibility. This paper approaches issues related with frame problems and nonresponse in surveys. These
\emph{nonsampling errors}  % --- to emphasize text use \emph{}
affect the accuracy of the estimates whereas the estimators become biased and less precise. We analyse some estimation methods that deal with those problems and give an especial focus to the poststratification procedures. We then address the Bootstrap methodology for variance estimation.
\end{abstract}

%-------------------------------------------------------------------------------
% Keywords...
%-------------------------------------------------------------------------------
\begin{keywords}
Poststratification; frame problems; nonresponse; reweighting; adjustment methods; Bootstrap.
\end{keywords}

%-------------------------------------------------------------------------------
% AMS classifications...
%-------------------------------------------------------------------------------
\begin{ams}
49A05, 78B26.
\end{ams}

%-------------------------------------------------------------------------------
% Main text of the paper:  sections, subsections and subsubsections,
%                          with theorems, lemmas, ..., figures, tables, ..., etc
%-------------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%% alteracao %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\mainpaper  % --- just a blank page and a \newpage command
\newpage     % --- just a newpage - not a blank page
%%%%%%%%%%%%%%%%%%%%%%%%%% alteracao %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-------------------------------------------------------------------------------
% First section
%-------------------------------------------------------------------------------
\section{INTRODUCTION}  % --- sections in UPPERCASE
\label{Sec1}              % --- this section label

The importance of the treatment of factual items in the XYZ has long been recognized in the literature\footnote{See, for instance, Rothwell (\cite{R1}).}.
If not excluded for the purposes of index number compilation, the most common approaches to the treatment of such goods are the so-called fix...

\section{DESCRIPTION OF THE PROBLEM}
\label{Sec2}

\subsection{Theoretical background}

As mentioned in section~\ref{Sec1}, in principle, the difficulties raised by the existence of factual items can be tackle by either:
\begin{enumerate}
\item[a)] ignoring the issue and excluding all the possible `problematic' items from XYZ compilation;
\item[b)] allocating fixed weights, assuming that factual items are to be treated in the same way as all other items (this is the fixed weights approach);
\item[c)] allocating variable/changing weights, according to the consumption pattern found in the base year (this is the variable weights approach).
\end{enumerate}

Table~\ref{Tab1} summarises the main advantages and disadvantages of the three considered approaches.

\vspace*{5mm}
\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|}
\hline
\textbf{Approach} & \textbf{Advantages} & \textbf{Disadvantages}\\
\hline
Ignore... & Simplicity & Overlooking...\\
Fixed-weight & Theoretical consistency & Choice of imputation... \\
Variable-weight & Minimisation... & Theoretical inconsistency\\
\hline
\end{tabular}
\caption{Advantages and disadvantages of different approaches to the treatment of factual items in a XYZ.
\label{Tab1}}
\end{table}
\vspace*{5mm}

Ignoring the `problematic' or more `volatile' items can be seen as a non-solution in the context of an index that wants to reflect changes in consumption prices. If these items have some importance in the XYZ basket, then there is, in principle, no reason for ignoring them.

Figure~\ref{Fig1} compares the carry forward and percentage change indices.\break
Although different in level, they nearly have the same turning points and behaviour in terms of movement.

\vspace*{5mm}
\begin{figure}[h]
\centering
%\includegraphics{rs-fig01.eps}
\includegraphics[width=0.7\textwidth]{rs-fig01.png}
\caption{Carry forward and percentage change indices.\hfil\break
Both indices tend to approximate in the months with less prices.
 \label{Fig1}}
\end{figure}
\vspace*{5mm}

\begin{theorem}
\label{Thm1}
Consider aggregation with all the other XYZ components.
\begin{equation}
\label{Eq1}
I_{i;o,m}^{t,m}=\frac{p_{i;t,m}}{p_{i;o,m}}~.
\end{equation}
\end{theorem}

\begin{proof}
This could be the proof of the previous Theorem...
\end{proof}

\subsubsection{This is a subsubsection}

The percentage change index presents a higher volatility than the forward imputation method (\ref{Eq1}), (\ref{Eq2}) and (\ref{Eq3}) (see Theorem~\ref{Thm1} and Lemma~\ref{Lem1}).

\begin{lemma}
\label{Lem1}
Consider aggregation with all the other XYZ components. That is only possible at the class level:
\begin{eqnarray}
\label{Eq2}
 && I_{i;o,m}^{t,m}=\frac{p_{i;t,m}}{p_{i;o,m}}~,~~~~m,n\in\N~;\\[2mm]
\label{Eq3}
 && {}_{s}I_{o,m}^{t,m}=\sum_{i}I_{i;o,m}^{t,m}\,
 \frac{p_{i;t,m}\cdot q_{i;o,m}}{{\displaystyle \sum_{i} p_{i;t,m}\cdot q_{i;o,m}}}~.
\end{eqnarray}
\end{lemma}

No matter which approach is followed, one has to bear in mind that no ``perfect" solution exist...
\\\\
Similar environment for corollary, proposition, ...
%\begin{corollary} \label{Cor1}
% First Corollary...
% \end{corollary}

%\begin{proposition} \label{Pro1}
% First Proposition...
% \end{proposition}

\begin{remark}
\label{Rem1}
First Remark...
\end{remark}

% \begin{note} \label{Not1}
% First Note...
% \end{note}
\noindent
Similar  environment for note, definition, example, ...

% \begin{definition} \label{Def1}
% First Definition...
% \end{definition}

% \begin{example} \label{Exa1}
% First Example...
% \end{example}

\begin{proof}[Proof of Lemma~\ref{Lem1}]
This is the proof of the previous Lemma...
\end{proof}

%-------------------------------------------------------------------------------
% Acknowledgments... Changed in revstat-v2
%-------------------------------------------------------------------------------
\begin{acknowledgments}
This work has been supported by the grant number xyz from Research Institution XX.
We also acknowledge the valuable suggestions from Prof.\ EFG and the referees.
\end{acknowledgments}
%-------------------------------------------------------------------------------
% References...
%-------------------------------------------------------------------------------
\begin{thebibliography}{8}

% --- example of Journal article:
\bibitem{Ab1}
\textsc{Author, B.}
 (1980).
 Article title in lowercase,
\textit{Journal Name In Uppercase},
\textbf{23},
 4,
 230--350.

\bibitem{R1}
\textsc{Rothwell, D.P.}
 (1958).
 Use of varying seasonal weights in price index construction,
\textit{Journal of the American Statistical Association},
\textbf{53}, 1, 66--77.

% --- example of Book:
\bibitem{Ab2}
\textsc{Author, B.} (1990).
\textit{Book Name In Uppercase}, Academic Press, New York.

\bibitem{Ro1}
\textsc{Robert, C.P.} (1999).
\textit{Monte Carlo Statistical Methods}, Springer Verlag.

% --- example of contribution on Book:
\bibitem{Ab3}
\textsc{Author, B.}  (2000).
\textit{Contribution title in lowercase}.
 In "Book Name In Uppercase"
 (J.\ Black and A.\ White, Eds.),
 Academic Press, New York, 123--130.

\bibitem{Ru1}
\textsc{Runbin, D.G.}
 (1988).
\textit{Using the SIR algorithm to simulate posterior distributions}.
 In ``Bayesian Statistics"
 (J.M.\ Bernardo, ... and A.F.M.\ Smith, Eds.),
 Oxford University Press, 395--402.

% --- example of 2 authors (book):
\bibitem{AA1}
\textsc{Author, B.\ \textup{and} Author, C.}  % --- notice the upshape "and"
 (1980).
\textit{Book Name In Uppercase},
 Academic Press, New York.

% --- example of 3 or more authors (book):
\bibitem{AAA1}
\textsc{Author, B.; Author, C.\ \textup{and} Author, D.}  % --- ";" and "and"
 (1980).
\textit{Book Name In Uppercase},
 Academic Press, New York.

\end{thebibliography}

\end{document}

### 2022-05-18 paper/new_code_dagum.R

@@ -1,326 +1,0 @@
-# Title: Marshall Olkin Gamma-G (MOGG)
-# Author: Pedro Rafael D. Marinho
-
-# Loading libraries. ------------------------------------------------------
-library(parallel)
-library(tibble)
-library(pbmcapply)
-library(magrittr)
-library(purrr)
-library(xtable)
-
-# Baseline functions. -----------------------------------------------------
-pdf_dagum <- function(x, alpha, beta, p)
-  alpha * p / x * (x / beta) ^ (alpha * p) / ((x / beta) ^ alpha + 1) ^ (p + 1)
-# integrate(f = pdf_dagum, lower = 0, upper = Inf, alpha = 1.2,
-#           beta = 1.6, p = 2.2)
-
-cdf_dagum <- function(x, alpha, beta, p)
-  (1 + (x / beta) ^ (-alpha)) ^ (-p)
-# cdf_dagum(x = Inf, alpha = 1, beta = 4, p = 1)
-
-# This function creates MOGG functions. ----------------------------------
-pdf_mogg <- function(g, G) {
-  # Using Closures.
-  function(x, theta, a, ...) {
-    if (theta <= 0 || a <= 0)
-      warning("The \"a\" and \"theta\" parameters must be greater than zero.")
-    num <-
-      theta * (-log(1 - G(x = x, ...))) ^ (a - 1) * g(x = x, ...)
-    den <-
-      gamma(a) *
-      (theta + (1 - theta) *
-         pgamma(-log(1 - G(x = x, ...)), a, 1L)) ^ 2
-    num / den
-  }
-}
-
-rdagum <- function(n = 1L, alpha, beta, p) {
-  beta * (runif(n = n, min = 0, max = 1) ^ (-1 / p) - 1) ^ (-1 / alpha)
-}
-
-pdf_mogdagum <- pdf_mogg(g = pdf_dagum, G = cdf_dagum)
-
-# MOG-Dagum --------------------------------------------------------------------
-rmogdagum <- function(n = 1L, theta, a, alpha, beta, p) {
-  cond_c <- function(x, theta, a, alpha, beta, p) {
-    num <- pdf_mogdagum(x, theta, a, alpha, beta, p)
-    den <- pdf_dagum(x,
-                     alpha = alpha,
-                     beta = beta ,
-                     p = p)
-    - num / den
-  }
-  
-  x_max <-
-    optim(
-      fn = cond_c,
-      method = "BFGS",
[…]

### 2022-05-18 paper/paper.tex
Update paper

@@
 \usepackage{color}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 \renewcommand{\titleheading}
-{Using the ``revstat-v2.sty" Package}  % --- on odd running heads
+{MOGG family of distribution: properties and applications}  % --- on odd running heads
 
@@
 \renewcommand{\authorheading}
-{Author Pedro Rafael D. Marinho}  % --- on even running heads
+{Maria do Carmo S. Lima, Gauss M. Cordeiro and Pedro Rafael D. Marinho, }  % --- on even running heads
 
@@
 \begin{ams}
-	49A05, 78B26.
+	60E05, 62E10, 62E15.
 \end{ams}
 
-\section{Introduction}
+\section{INTRODUCTION}
 
@@
 
-\section{The New Family}\label{sec:MOGaG}
+\section{THE NEW FAMILY}\label{sec:MOGaG}
 
@@
 
-\begin{figure}[H]
-\begin{center}
-\includegraphics[scale =  0.39]{pdf-hazard.pdf}
-\caption{(A) MO-$\Gamma$-W density. (B) MO-$\Gamma$-W hazard.\label{formas}}
-\end{center}
+%\begin{figure}[H]
+%\begin{center}
+%\includegraphics[scale =  0.39]{pdf-hazard.pdf}
+%\caption{(A) MO-$\Gamma$-W density. (B) MO-$\Gamma$-W hazard.\label{formas}}
+%\end{center}
+%\end{figure}
+
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{pdf_function.pdf}
+		\caption{MO-$\Gamma$-W density function.}
+		\label{fig:pdf}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{hazard_function.pdf}
+		\caption{MO-$\Gamma$-W hazard function.}
+		\label{fig:hazard}
+	\end{subfigure}
+\caption{MO-$\Gamma$-W density function and  MO-$\Gamma$-W hazard function with G following the Weibull distribution.}
+\label{formas}
 \end{figure}
@@
 
-\section{Estimation}\label{estimation}
+\section{ESTIMATION}\label{estimation}
 
@@
 
-\section{Simulations}\label{sec:simulation}
+\section{SIMULATIONS}\label{sec:simulation}
 
@@
 
-\section{Applications}\label{applications}
+\section{APPLICATIONS}\label{applications}
 
@@
 
-\section{Mathematical properties}\label{properties}
+\section{MATHEMATICAL PROPERTIES}\label{properties}
 
@@
 
-\section{Conclusions}\label{conclusions}
+\section{CONCLUSIONS}\label{conclusions}
 
@@
 
-\appendix
-
-\section{Appendix: Simulation code}\label{ap:simulation}
-
-The script below is used to perform the simulations whose results are given in Table \ref{tab:bias} of Section \ref{sec:simulation}.
-It is developed a script using the programming language {\sf R} to be used in other simulations or even to check the results presented in this paper.
-
-\section*{References}
-
-\begin{description}
+\begin{thebibliography}{8}
 
@@
 
-\end{description}
+\end{thebibliography}
 

### 2022-05-18 code/plots/plots.R

@@ -49,11 +49,16 @@
              "Legenda 3" = "#9239F6",
              "Legenda 4" = "#E3D26D")
   
+  type_lines <- c("solid",
+                  "dotted",
+                  "dotdash",
+                  "twodash")
+  
   base <- ggplot(data.frame(x = c(0, 10)), aes(x)) +
-    ggtitle(
-      "Probability density function",
-      subtitle = "With G following the Weibull distribution "
-    ) +
+    # ggtitle(
+    #   "Probability density function",
+    #   subtitle = "With G following the Weibull distribution "
+    # ) +
     theme(
       plot.title = element_text(face = "bold"),
       axis.title = element_text(face = "bold"),
@@ -71,7 +76,8 @@
         beta = 3
       ),
       aes(color = "Legenda 1"),
-      size = 1.5
+      size = 1.5,
+      linetype = "solid"
     ) +
     
     stat_function(
@@ -83,7 +89,8 @@
         beta = 0.3
       ),
       aes(color = "Legenda 2"),
-      size = 1.5
+      size = 1.5,
+      linetype = "dotted"
     ) +
     
     stat_function(
@@ -95,7 +102,8 @@
         beta = 2.1
       ),
       aes(color = "Legenda 3"),
-      size = 1.5
+      size = 1.5,
+      linetype = "dotdash"
     ) +
     
     stat_function(
@@ -107,41 +115,49 @@
         beta = 2.7
       ),
       aes(color = "Legenda 4"),
-      size = 1.5
-    ) +
+      size = 1.5,
+      linetype = "twodash"
+    )  +
     
     labs(x = "x",
          y = expression("f(x)"),
          color = expression(paste("MO-", Gamma, "-Weibull")),
          element_text(face = "bold"))  +
-    
+  
     scale_color_manual(values = cores, labels =
                          expression(
                            paste(theta, " = 2.2, ", "a = 3.2, ", alpha, " = 2.0, ", beta, " = 3.0"),
                            paste(theta, " = 3.0, ", "a = 1.5, ", alpha, " = 0.7, ", beta, " = 0.3"),
                            paste(theta, " = 0.2, ", "a = 4.0, ", alpha, " = 1.4, ", beta, " = 2.1"),
                            paste(theta, " = 5.1, ", "a = 4.1, ", alpha, " = 2.5, ", beta, " = 2.7")
-                         )) +
+                         ), 
+                       guide = guide_legend(override.aes = list(
[…]

### 2022-05-20 code/new_code_dagum.R
Add run_all_simulations.R

@@ -8,6 +8,9 @@ library(pbmcapply)
 library(magrittr)
 library(purrr)
 library(xtable)
+library(glue)
+library(fs)
+library(kableExtra)
 
 # Baseline functions. -----------------------------------------------------
 pdf_dagum <- function(x, alpha, beta, p) 
@@ -73,7 +76,7 @@ rmogdagum <- function(n = 1L, theta, a, alpha, beta, p){
 
 # Testing the rmogw Function ----------------------------------------------
 theta = 5
-a = 1
+a = 1.4
 alpha = 5
 beta = 1
 p = 1
@@ -152,11 +155,11 @@ mc <- function(n = 250L, M = 1e3L, par_true, method = "BFGS") {
 }
 
 bias_function <- function(x, par_true){
-  x - par_true
+  round(x - par_true, digits = 3L)
 }
 
 mse_function <- function(x, par_true) {
-  (x - par_true) ^ 2
+  round((x - par_true) ^ 2, digits = 3L)
 }
 
 simulate <- function(n) {
@@ -166,43 +169,109 @@ simulate <- function(n) {
   set.seed(1L, kind = "L'Ecuyer-CMRG")
   t0 <- Sys.time()
   result_mc <- mc(n = n, M = 1e4L, par_true = true_parameters, method = "BFGS")
-  total_time <- Sys.time() - t0
+  total_time <- difftime(Sys.time(), t0, units = 'mins')[[1L]] 
     
   mc.reset.stream()
   
   # Average Bias of Estimators ----------------------------------------------
   eval(parse(text = glue("bias_{n} <- apply(X = result_mc, MARGIN = 1L, FUN = bias_function, par_true = true_parameters) %>% 
         apply(MARGIN = 1L, FUN = mean)"))) 
-  eval(parse(text = glue("save(file = \"bias_{n}.RData\", bias_{n})")))
+  eval(parse(text = glue("save(file = \"rdata/dagum/bias_{n}.RData\", bias_{n})")))
   
   # Mean Square Error -------------------------------------------------------
   eval(parse(text = glue("mse_{n} <- apply(X = result_mc, MARGIN = 1L, FUN = mse_function, par_true = true_parameters) %>% 
         apply(MARGIN = 1L, FUN = mean)"))) 
-  eval(parse(text = glue("save(file = \"mse_{n}.RData\", mse_{n})")))
[…]

### 2022-05-20 code/new_code_weibull.R

@@ -9,6 +9,7 @@ library(magrittr)
 library(purrr)
 library(xtable)
 library(glue)
+library(fs)
 
 # Baseline functions. -----------------------------------------------------
 pdf_w <- function(x, alpha, beta) dweibull(x = x, shape = alpha, scale = beta)
@@ -155,60 +156,119 @@ simulate <- function(n) {
   set.seed(1L, kind = "L'Ecuyer-CMRG")
   t0 <- Sys.time()
   result_mc <- mc(n = n, M = 1e4L, par_true = true_parameters, method = "BFGS")
-  total_time <- Sys.time() - t0
+  total_time <- difftime(Sys.time(), t0, units = 'mins')[[1L]] 
   
   mc.reset.stream()
   
   # Average Bias of Estimators ----------------------------------------------
   eval(parse(text = glue("bias_{n} <- apply(X = result_mc, MARGIN = 1L, FUN = bias_function, par_true = true_parameters) %>% 
         apply(MARGIN = 1L, FUN = mean)"))) 
-  eval(parse(text = glue("save(file = \"bias_{n}.RData\", bias_{n})")))
+  eval(parse(text = glue("save(file = \"rdata/weibull/bias_{n}.RData\", bias_{n})")))
   
   # Mean Square Error -------------------------------------------------------
   eval(parse(text = glue("mse_{n} <- apply(X = result_mc, MARGIN = 1L, FUN = mse_function, par_true = true_parameters) %>% 
         apply(MARGIN = 1L, FUN = mean)"))) 
-  eval(parse(text = glue("save(file = \"mse_{n}.RData\", mse_{n})")))
+  eval(parse(text = glue("save(file = \"rdata/weibull/mse_{n}.RData\", mse_{n})")))
   
   # Total Time --------------------------------------------------------------
   eval(parse(text = glue("time_{n} <- total_time")))
-  eval(parse(text = glue("save(file = \"time_{n}.RData\", time_{n})")))
+  eval(parse(text = glue("save(file = \"rdata/weibull/time_{n}.RData\", time_{n})")))
   
   # Result MC
   eval(parse(text = glue("result_{n} <- result_mc")))
-  eval(parse(text = glue("save(file = \"result_{n}.RData\", result_{n})")))
[…]

### 2022-05-20 code/run_all_simulations.R

@@ -1,0 +1,2 @@
+source("new_code_weibull.R")
+source("new_code_dagum.R")

### 2022-05-20 code/simulations/Simu_MO-G-Wei.R

@@ -1,155 +1,0 @@
-############################################################
-###############   MO-Ga-Weibull DISTRIBUTION     ###########
-############################################################
-#PURPOSE: Marshall Olkin Gamma-Weibull (MO-Ga-Weibull) model 
-#AUTHOR: Tatiane F. Ribeiro
-#DATE: December 26th, 2019.
-############################################################
-#Clear the memory
-rm(list = ls())
-#Seed
-set.seed(19)
-
-#Inicializations
-R = 10 #number of replications
-vn<- c(100,150, 200,250) #sample sizes
-
-#Parameters 
-a = 1
-theta = 4
-lambda = 2
-gama = 2
-
-#Weibull
-dwei <- function(x){
-  lambda*gama*(lambda*x)^(gama-1)*exp(-(lambda*x)^gama)
-}
-pwei <- function(x){
-  1-exp(-((lambda*x)^gama))
-}
-#Test density
-integrate(dwei,0,Inf)
-
-qwei <- function(u,par1,par2){
-  1/lambda*(-log(1-u))^(1/gama)
-}
-#Tests quantile function
-aux=pwei(c(3,.4,5,.7,6))
-qwei(aux)
-
-#cdf MO-Ga-Weibull
-cdf_MOGa_Wei <- function(x){
-  pgamma(-log(1-pwei(x)),a)/((1-theta)*
-                               pgamma(-log(1-pwei(x)),a)+theta)
-}
-
-#pdf MO-Ga-Weibull
-pdf_MOGa_Wei <- function(x){
-  g = lambda*gama*(lambda*x)^(gama-1)*exp(-(lambda*x)^gama)
-  G =   1-exp(-((lambda*x)^gama))
-  
-  num = theta*g*(-log(1-G))^(a-1)
-  den = ((1-theta)*pgamma(-log(1-G),a,1)+theta)^2
-  
-  num/(gamma(a)*den)
-}
-#integrate(pdf_MOGa_Wei,0,Inf)
-
-#Quantile function MO-Ga-Weibull
-qf_MOGa_Wei <- function(u){
-  quant = 1-exp(-qgamma(u*theta/(-u*(1-theta)+1),a))
-  res = qwei(quant,lambda,gama)    
-  return(res)
-}
-
-#Inversion method
[…]

### 2022-05-20 code/simulations/new_code_dagum.R

@@ -1,220 +1,0 @@
-# Title: Marshall Olkin Gamma-G (MOGG)
-# Author: Pedro Rafael D. Marinho
-
-# Loading libraries. ------------------------------------------------------
-library(parallel)
-library(tibble)
-library(pbmcapply)
-library(magrittr)
-library(purrr)
-library(xtable)
-library(glue)
-
-# Baseline functions. -----------------------------------------------------
-pdf_dagum <- function(x, alpha, beta, p) 
-  alpha * p / x * (x / beta) ^ (alpha * p) / ((x / beta) ^ alpha + 1) ^ (p + 1)
-# integrate(f = pdf_dagum, lower = 0, upper = Inf, alpha = 1.2, beta = 1.6, p = 2.2)
-
-cdf_dagum <- function(x, alpha, beta, p) 
-  (1 + (x / beta) ^ (-alpha)) ^ (-p)
-# cdf_dagum(x = Inf, alpha = 1, beta = 4, p = 1)
-
-# This function creates MOGG functions. ----------------------------------
-pdf_mogg <- function(g, G){
-  # Using Closures.
-  function(x, theta, a, ...){
-    if (theta <= 0 || a <= 0) 
-      warning("The \"a\" and \"theta\" parameters must be greater than zero.")
-    num <- theta * (-log(1 - G(x = x, ...)))^(a - 1) * g(x = x, ...)
-    den <- gamma(a) * (theta + (1 - theta) * pgamma(-log(1 - G(x = x, ...)), a, 1L))^2
-    num/den
-  }
-}
-
-rdagum <- function(n = 1L, alpha, beta, p) {
-  beta * (runif(n = n, min = 0, max = 1) ^ (-1 / p) - 1) ^ (-1 / alpha)
-}
-
-pdf_mogdagum <- pdf_mogg(g = pdf_dagum, G = cdf_dagum)
-
-# MOG-Dagum --------------------------------------------------------------------
-rmogdagum <- function(n = 1L, theta, a, alpha, beta, p){
-  
-  cond_c <- function(x, theta, a, alpha, beta, p){
-    num <- pdf_mogdagum(x, theta, a, alpha, beta, p)
-    den <- pdf_dagum(x, alpha = alpha, beta = beta , p = p)
-    -num / den
-  }
-  
-  x_max <- optim(fn = cond_c, method = "BFGS", par = 1, theta = theta, a = a,
-                 alpha = alpha, beta = beta, p = p)$par
-  
[…]

### 2022-05-25 paper/letter_answers.tex
Add TTT plots.

--- 2022-05-18 paper/reviews/answers/letter_answers.tex
@@
 1 -- The equality \(h(x)=f(x)/(1-F(x))\) is a well known relation
-between hazard, density and survival functions. It is not a definition
-of density or risk functions. Therefore, in page 3, line 12, the part of
-the sentence ``defined by \(h(x)=f(x)/(1-F(x))\)'' should be omitted.
+between hazard, density and survival functions.
+It is not a definition of density or risk functions.
+Therefore, in page 3, line 12, the part of the sentence ``defined by \(h(x)=f(x)/(1-F(x))\)'' should be omitted.
+
+\textcolor{red}{Thank you. Done}.
 
@@
 
-2 -- The expression (3.1) in page 6 corresponds to the log-likelihood of
-a MO-\(\Gamma\)-\(G\) distribution, considering a Weibull distribution
-for \(G\) (although there is an error in the last sum of line 1), not a
-general distribution with a \(\eta\) vector of parameters. Therefore,
-the text or the expression should be written accordingly.
+2 -- The expression (3.1) in page 6 corresponds to the log-likelihood of the MO-\(\Gamma\)-\(G\) distribution, 
+thus considering a Weibull distribution
+for \(G\) (although there is an error in the last sum 
+of line 1), not a general distribution with a \(\eta\) 
+vector of parameters. Therefore, the text or the expression 
+should be written accordingly.
 
@@
 
-3 -- It is not clear why it is considered the Weibull distribution (for
-\(G\)) in Figure 1, eventually in expression (3.1) and in the
-applications, whereas for the simulations it is chosen the Dagum
-distribution. These choices should be clarified.
+3 -- It is not clear why it is considered the Weibull distribution (for \(G\)) in Figure 1, eventually in expression (3.1) and in 
+the applications, whereas for the simulations it is chosen the 
+Dagum distribution. These choices should be clarified.
 
 \emph{Response}:
-\textcolor{red}{Indeed, the way in which the application section was written suggests that an attempt was made to fix the $G\sim Weibull$ distribution as one of the necessary assumptions for the analysis.
-What actually happened is that for the datasets used, the Weibull distribution appeared to be a suitable distribution.}
+\textcolor{red}{Indeed, the way in which the application section was introduced suggests that an attempt was made to fit the $G\sim Weibull$ model as a suitable distribution to the current datasets.
+In order to remove some ambiguity, we opted to extend the simulation studies, where we now include the $G\sim Weibull$ in the simulations.}
 
-\textcolor{red}{In order to remove some ambiguity, we opted to extend the simulation studies, where we also include the simulations, considering $G\sim Weibull$.
-Indeed, the way in which the application section was written suggests that an attempt was made to fix the $G\sim Weibull$ distribution as one of the necessary assumptions for the analysis.
-What actually happened is that for the datasets used, the Weibull distribution appeared to be a suitable distribution.}
-
-\textcolor{red}{In order to remove some ambiguity, we opted to extend the simulation studies, where we also include the simulations, considering $G\sim Weibull$.}
-
-4 -- As the Dagum distribution is used in the simulations, the generated
-PDF should also be in Table 1.
+4 -- As the Dagum distribution is used in the simulations, the generated PDF should also be in Table 1.
 
 \emph{Response}:
-\textcolor{red}{Thanks for the observation. The Dagum distribution was included in Table 1.}
+\textcolor{red}{Thank you for pointing that out. The Dagum distribution was now included in Table 1.}
 
-5 -- As the \texttt{goodness.fit} function gives several statistics, the
-authors should justify why they only chose the Anderson Darling and
-Cramer-von Mises statistics.
+5 -- As the \texttt{goodness.fit} function gives several statistics, the authors should justify why they only chose the Anderson Darling and Cram\'er-von Mises statistics.
 
 \emph{Response}:
-\textcolor{red}{The use of the $A^*$ and $W^*$ statistics, Anderson-Darling and Cramer-von Mises statistics, respectively, corrected by Chen and Balakrishnan, in the paper entitled "A General Purpose Approximate Goodness-of-Fit Test" (see   \url{https://www.tandfonline.com/doi/abs/10.1080/00224065.1995.11979578}) are suitable for comparing models that are not necessarily embedded.
-Therefore, considering the statistics returned by the \texttt{goodness.fit} function and considering the distributions compared, we understand that the statistics $A^*$ and $W^*$ are the most suitable for making the comparisons.}
+\textcolor{red}{The use of the Anderson-Darling  $A^*$ and Cram\'er-von Mises $W^*$  statistics, corrected by Chen and Balakrishnan, in the paper entitled ``A General Purpose Approximate Goodness-of-Fit Test'' (see   \url{https://www.tandfonline.com/doi/abs/10.1080/00224065.1995.11979578}) is indicated for comparing mo\-dels that are not necessarily embedded.
+Hence, considering the statistics returned by the \texttt{goodness.fit} function and the distributions compared, we understand that these statistics are the most suitable ones for
+the comparisons.}
 
-\textcolor{red}{The  \textbf{AdequacyModel} package was developed by one of the authors of this paper and was published at   \url{https://journals .plos.org/plosone/article?id=10.1371/journal.pone.0221487}.
-A code inspection of the \texttt{goodness.fit} function can be done by looking at the   \href{https://github.com/prdm0/AdequacyModel/blob/master/R/goodness.fit.R}{link} on GitHub, where it is hosted the development versioning of the package.}
+\textcolor{red}{The \textbf{AdequacyModel} package was developed 
+by one of the authors of this paper and it was published at   \url{https://journals .plos.org/plosone/article?id=10.1371/journal.pone.0221487}. 
+A code inspection of the \texttt{goodness.fit} function can be done by looking at the link   \href{https://github.com/prdm0/AdequacyModel/blob/master/R/goodness.fit.R}{link} on GitHub, where it is hosted the development versioning of the package.}
 
@@
 
-\emph{Response}:
+\emph{Response}: \textcolor{red}{Done.}
 
@@
 
-\emph{Response}:
+\emph{Response}: \textcolor{red}{Done.}
 
-4 -- page 3, line 4, where it is written ``gamma density unit scale and
-shape \(a>0\),'' I suggest replacing it by ``gamma density with unit
-scale parameter and shape parameter \(a>0\),''.
+4 -- page 3, line 4, where it is written ``gamma density unit scale and shape \(a>0\),'' I suggest replacing it by ``gamma density with unit scale parameter and shape parameter \(a>0\),''.
 
-\emph{Response}:
+\emph{Response}: \textcolor{red}{Done.}
 
@@
 
-\emph{Response}:
+\emph{Response}: \textcolor{red}{Done.}
 
-7 -- Figure 1: I suggest to change the lines to different types (even
-letting the colours as they are) so as to enable the interpretation in a
-black and white print. Also, the letters assigned to the parameters must
-agree with those in Table 1 (and, eventually, with those in expression
-(3.1)).
+7 -- Figure 1: I suggest to change the lines to different types (even letting the colours as they are) so as to enable the interpretation in a black and white print.
+Also, the letters assigned to the parameters must agree with those in Table 1 (and, eventually, with those in expression (3.1)).
 
@@
 
-8 -- page 3, lines-8,-7, where it is written ``of the baseline \(Q_F\)
-\(Q_G(.)\).'' I suggest replacing it by ``of the \(Q_F\) of the baseline
-distribution \(G\), \(Q_G(.).\)''.
+8 -- page 3, lines-8,-7, where it is written ``of the baseline \(Q_F\) \(Q_G(.)\).'' I suggest replacing it by ``of the \(Q_F\) of the baseline distribution \(G\), \(Q_G(.).\)''.
 
-\emph{Response}:
+\emph{Response}: \textcolor{red}{Done.}
 
@@
 
-10 -- page 7: the label of the table should be on the top, like the rest
-of the tables.
+10 -- page 7: the label of the table should be on the top, like the rest of the tables.
 
-\emph{Response}:
+\emph{Response}: \textcolor{red}{Done.}
 
@@
 
-\emph{Response}:
+\emph{Response}: \textcolor{red}{Done.}
 
-12 -- In expressions (6.4) and (6.6), try to improve the output as the
-reference numbers are to close to the formulas.
+12 -- In expressions (6.4) and (6.6), try to improve the output as the reference numbers are to close to the formulas.
+
+\emph{Response}: \textcolor{red}{Done.}
+
+13 -- I suggest to make the labels of Figure 1 and of tables in \LaTeX, not in R.
 
 \emph{Response}:
+\textcolor{red}{Thanks for the suggestion. The change suggestion has been implemented.}
 
-13 -- I suggest to make the labels of Figure 1 and of tables in \LaTeX,
-not in R.
-
-\emph{Response}:
-\textcolor{red}{Thanks for the sugestion. The change suggestion has been implemented.}
-
-14 -- The references ``R Core Team. \ldots{}'' and ``Rizzo, \ldots{}''
-are in the wrong order.
+14 -- The references ``R Core Team. \ldots{}'' and ``Rizzo, \ldots{}'' are in the wrong order.
 
@@
 
-1 - The article is written in an overly summarized form and is sometimes
-unattractive to the reader of any journal. That alone could lead to your
-rejection. In addition, I do suggest reviewing the use of English
-carefully, and considerable rewording and pruning to make the paper more
-concise and precise.
+1 - The article is written in an overly summarized form and is sometimes unattractive to the reader of any journal.
+That alone could lead to your rejection.
+In addition, I do suggest reviewing the use of English carefully, and considerable rewording and pruning to make the paper more concise and precise.
 
@@
 
-2 - When I see a new paper about a new distribution, I wonder if it is
-due to any interesting properties or it arises naturally in some
+\textcolor{red}{We have improved the English language of the article in all sections.}
+
+2 - When I see a new paper about a new distribution, I wonder if it is due to any interesting properties or it arises naturally in some
 observable process like natural phenomena. I would like to see these
-arguments defended more clearly in the article by the authors. Could you
-do that?
+arguments defended more clearly in the article by the authors. Could you do that?
 
@@
 
+\textcolor{red}{The Marshall and Olkin-G and Gamma-G generators, each with one more parameter, are often used to build new distributions.
+We empirically show through two real datasets that by combining these two generators, we obtain a new family of distributions that is better than two families widely used in the literature: beta and Kumarawamy (each one of the three with two parameters).
+In fact, the ``beta-G family of distributions" has over 3100 citations on google, whereas the ``Kumaraswamy-G family of distributions" has over 4500 citations  up to this date (May, 2022).
+Further, the properties of the proposed family are obtained similarly from the other two families using exponentiated distributions.}
+
 3 - The bibliography does not have many recent publications such as
 Martinez-Florez et al. (2020) and Magalhaes et al.~(2020). I also
-suggest authors to create the state-of-art related to this topic in the
-first section that definitively needs to be improved.
+suggest authors to create the state-of-art related to this topic in the first section that definitively needs to be improved.
 
@@
 
-4 - I expect to see more detailed discussion in the simulation study and
-real data analysis. Could you revise these sections, including the
-conclusion section that is actually weak?
+4 - I expect to see more detailed discussion in the simulation study and real data analysis. Could you revise these sections, including the conclusion section that is actually weak?
 
-5 - Suggestions: (i) Rewrite the paper title since the current one is
-nothing enlightening. How about naming the proposed distribution?. (ii)
-Place section 6 (properties) before section 4 (simulation). (iii)
-Reorganize the presentation of the tables. (iv) Put the simulation code
-in Supplementary material.
+5 - Suggestions: (i) Rewrite the paper title since the current one is nothing enlightening.
+How about naming the proposed distribution?.
+(ii) Place section 6 (properties) before section 4 (simulation).
+(iii) Reorganize the presentation of the tables.
+(iv) Put the simulation code in Supplementary material.
 
@@
   \item
-    \textcolor{red}{Really, the title of the paper was really bad.
-We switched to \textbf{Marshall and Olkin-G and Gamma-G family of distribution: properties and applications}.
-We believe that the title now clarifies the paper's proposal better.}
+    \textcolor{red}{ Really, the title of the paper was no good.
+We changed to \textbf{Marshall and Olkin-Gamma-G family of distributions: properties and applications}.
+We believe that the title now clarifies the paper's proposal better.
+It is worth mentioning that the new name is consistent with the sequential application of the MO family to the baseline Gamma-G.}
   \end{enumerate}
@@
   \item
-    \textcolor{red}{Change made. Thanks for the sugestion.}
+    \textcolor{red}{Done. Thanks for the suggestion.}
   \end{enumerate}
@@
   \item
-    \textcolor{red}{Thanks for the observation. The presentation of tables has been reorganized.}
+    \textcolor{red}{Thanks for this point. The presentation of the tables was reorganized.}
   \end{enumerate}
@@
   \item
-    \textcolor{red}{Thanks for the sugestion.We chose to put the code for the simulations in a repository on GitHub.
+    \textcolor{red}{Thanks for the suggestion.
+We chose to put the code for the simulations in a repository on GitHub.
 Thus, we considerably reduced the number of pages in the article and made it easier for readers of the material to reuse the code.
 With the code on GitHub it is also possible to verify the implementation and validate the simulations obtained.
-To access the codes, see the
+To access the codes, see the link
     \url{https://github.com/prdm0/MOGG/tree/master/code/simulations}}.
@@
 
-\closing{Kind regards,}
+\closing{Yours Sincerely,}
 

### 2022-05-25 paper/paper.tex
Add TTT plots.

@@
 
-\author{\authoraddress{Maria do Carmo S. Lima \href{https://orcid.org/0000-0004-8882-8330}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}} 
+\author{\authoraddress{Maria do Carmo S. Lima \href{https://orcid.org/0000-0002-5480-3103}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}} 
 	{Department of Statistics,
@@
 baseline distribution and $g(x)=dG(x)/dx$ be the corresponding  probability density function (PDF) depending on a
-parameter vectot $\eta$. A generalized family are presented
+parameter vector $\eta$. A generalized family are presented
 with two additional shape parameters by transforming the CDF $G(x)$
@@
 belonging to this family. It is easily generated from the baseline quantile function (QF) by
-$Q_{\text{MO-G}}(u)=Q_{G}\left(\theta u \left[\theta u+1-u\right]\right)$ for $u\in(0,1)$.
+$Q_{\text{MO-G}}(u)=Q_{G}\left(\theta u / \left[\theta u+1-u\right]\right)$ for $u\in(0,1)$.
 
@@
 If $Z$ is a gamma random variable with unit scale
-parameter and shape parameter $a>0$, then $W=Q_G(1-\rm{e}^{Z})$ has density (\ref{PDF_Ga}). So,
+parameter and shape parameter $a>0$, then $W=Q_G(1-\rm{e}^{-Z})$ has density (\ref{PDF_Ga}). So,
 the $\Gamma$-G distribution is easily generated from the gamma distribution and the QF of G.
 
-The remaining of the paper is addressed as follows. Section \ref{sec:MOGaG} introduces the {\it Marshall and Olkin-Gamma-G} (MO-$\Gamma$-G)
+The remaining of the paper is addressed as follows. Section \ref{sec:MOGaG} introduces the {\it Marshall and Olkin-Gamma-G} (MOGa-G)
 family and presents some special models. The maximum likelihood estimates (MLEs) of the parameters of the new family is addressed
@@
 
-By combining Equations (\ref{CDF_MO}) and (\ref{CDF_Ga}), the CDF of the random variable $X\sim$MO-$\Gamma$-G
+By combining Equations (\ref{CDF_MO}) and (\ref{CDF_Ga}), the CDF of the random variable $X\sim$MOGa-G
 representing the new family is defined by
@@
 The density (\ref{PDF_MO-Gamma-G}) can be interpreted from a sequence of $N$ iid random variables, say $Z_1,\cdots,Z_N$,
-each one having a gamma density unit scale and shape $a>0$, assuming that $N$ (is not fixed) has a geometric 
+each one having a gamma density with unit scale parameter and shape parameter $a>0$, assuming that $N$ (is not fixed) has a geometric 
 distribution with probabilities $\theta$ and $\theta^{-1}$ for $0<\theta<1$ and $\theta>1$,
-respectively. By transforming the $Z_i$'s via the baseline QF by $W_i=Q_G(1-\rm{e}^{Z_i})$
+respectively. By transforming the $Z_i$'s via the baseline QF by $W_i=Q_G(1-\rm{e}^{-Z_i})$
 (for $i-1,\ldots,N$), Equation \eqref{densityMO} is defines the PDF of the minimum $W_1,\cdots,W_n$. 
@@
 
-Table \ref{tabspecial1} provides some special cases of (\ref{PDF_MO-Gamma-G}), where
+Table 1 provides some special cases of (\ref{PDF_MO-Gamma-G}), where
 $\Phi(x)$ and $\phi(x)$ are the CDF and PDF of the standard normal distribution. The density and hazard functions
-of the Marshall-Olkin-$\Gamma$-Weibull (MO-$\Gamma$-W) defined by $h(x) = f(x)/(1-F(x))$ are displayed in Figure \ref{formas}, which provide
+of the Marshall-Olkin-$\Gamma$-Weibull (MOGa-W) defined by $h(x) = f(x)/(1-F(x))$ are displayed in Figure \ref{formas}, which provide
 more flexibility for these functions in relation to the baseline ones.
@@
 %\includegraphics[scale =  0.39]{pdf-hazard.pdf}
-%\caption{(A) MO-$\Gamma$-W density. (B) MO-$\Gamma$-W hazard.\label{formas}}
+%\caption{(A) MOGa-W density. (B) MOGa-W hazard.\label{formas}}
 %\end{center}
@@
 		\includegraphics[width=\textwidth]{pdf_function.pdf}
-		\caption{MO-$\Gamma$-W density function.}
+		\caption{MOGa-W density function.}
 		\label{fig:pdf}
@@
 		\includegraphics[width=\textwidth]{hazard_function.pdf}
-		\caption{MO-$\Gamma$-W hazard function.}
+		\caption{MOGa-W hazard function.}
 		\label{fig:hazard}
 	\end{subfigure}
-\caption{MO-$\Gamma$-W density function and  MO-$\Gamma$-W hazard function with G following the Weibull distribution.}
+\caption{MOGa-W density function and  MOGa-W hazard function with G following the Weibull distribution.}
 \label{formas}
@@
 
-The CDF \eqref{CDF_MO-Gamma-G} can be easily inverted to calculate the QF of the MO-$\Gamma$-G distribution,
-say $x=Q_{X}(u)=F_X^{-1}(u)$ for $u \in (0,10$, in terms of the baseline QF $Q_G(\cdot)$. The inverse of
+The CDF \eqref{CDF_MO-Gamma-G} can be easily inverted to calculate the QF of the MOGa-G distribution,
+say $x=Q_{X}(u)=F_X^{-1}(u)$ for $u \in (0,1)$, in terms of the Q$_F$ of the baseline distribution G, $Q_G(\cdot)$. The inverse of
 $F_{X}(x)=u$, where $u$ is a uniform number in $(0,1)$ is easily obtained. By combining the inverses
@@
 	\begin{table}[htbp]\label{tabspecial1}
+		\caption{Special Distributions in the  MOGa-G family.}
 		\centering
-\begin{tabular}{c|c|c}
+\scalebox{0.7}{	
+		\begin{tabular}{l|l|l}
 			\hline
@@
 			\hline
-\end{tabular}
-\caption{Special Distributions in the  MO-$\Gamma$-G family.}
+			\textbf{Dagum} & $G(x) = \Big[1 + \Big(\frac{x}{\beta}\Big) ^ {-\alpha}\Big] ^ {-p},\,\, \alpha, \beta, p > 0$ & $f_X(x) = \frac{\theta  \left\{ -\log[1-G(x)] \right\}^{a-1}\, g(x)}{\Gamma(a)\{\theta + (1 - \theta)\gamma_1[a, -\log   (1-((x/\beta)^{-\alpha}+1)^{-p})]\}}$ \\
+			\hline
+		\end{tabular} }
 	\end{table}
@@
 
-The  MO-$\Gamma$-G family can be  fitted to real data using the {\bf AdequacyModel} package in the {\sf R} software.
+The  MOGa-G family can be  fitted to real data using the {\bf AdequacyModel} package, {\color{red}Marinho et al. (2019)}, in the {\sf R} software.
 This packa\-ge does not require to define the log-likelihood function and it computes the MLEs, their standard errors (SEs)
@@
 
-Due to the probable absence of MLEs in closed-form for distributions belonging to the MO-$\Gamma $-G family, it is necessary to examine the
-precision of the estimates calculated numerically. For doing that, the biases of the estimators of the parameters of the
-MO-$\Gamma$-Dagum($\theta$, $a$, $\alpha$, $\beta$, $p$) distribution are determined, where $G\sim \mathrm {Dagum} (\alpha, \beta, p)$
-is the baseline distribution. All parameters are taken equal to one for different sample sizes reported in Table \ref{tab:bias}.
-
-Ten thousand Monte Carlo simulations are performed for each sample size to examine the numerical estimates calculated by the
-BFGS method. The figures in Table \ref{tab:bias} indicate that this method behaves well when the sample size increases.
-This is theoretically expected. However, in practice, difficulties can be faced in other families of distributions
-due to the flatness of the log-likelihood function.
-
-All simulations can be reproduced using the script in Appendix \ref{ap:simulation}. The simulations are parallelized and able to use all threads
-available by a multicore processor, thus making them more computationally efficient and consequently requiring less time to complete.
-The simulations are performed on a computer with an Intel Core i5-8265U processor with 8 threads working at a maximum frequency of 3.90 GHz,
-requiring, on these hardware, a time of 14.36 hours to perform all simulations. The figures in Table \ref{tab:bias} reveal that the average
-biases of the MLEs could be very reduced only for $n> 2,000$.
+{\color{red}Due to the probable absence of MLEs in closed-form for distributions belonging to the MOGa-G family, it is necessary to examine the precision of the estimates calculated numerically.
+
+For doing that, the biases of the estimators of the parameters of the
+MOGa-Dagum($\theta$, $a$, $\alpha$, $\beta$, $p$) and  MOGa-Weibull($\theta$, $a$, $\lambda$, $\gamma$) distribution are determined, where $G\sim \mathrm {Dagum} (\alpha, \beta, p)$ and  $\mathrm {Weibull} (\gamma, \lambda)$ are the baselines distributions, respectively.
+All parameters are taken equal to one for different sample sizes reported in the Tables \ref{tab:bias1} and \ref{tab:bias2}.
+
+The Tables \ref{tab:bias1} and \ref{tab:bias2} indicate that this method behaves well when the sample size increases.
+This is theoretically expected.
+However, in practice, difficulties can be faced in other families of distributions due to the flatness of the log-likelihood function.
+
+All simulations can be reproduced using the script in \url{https://github.com/prdm0/MOGG}.
+The simulations are parallelized and able to use all threads available by a multicore processor, thus making them more computationally efficient and consequently requiring less time to complete.
+
+The simulations are performed on a computer with an Intel(R) Core(TM) i5-9500 CPU processor with 6 threads working at a maximum frequency of 3.00GHz, requiring, on these hardware, a time of 15.4828 hours to perform all simulations, 7.7414 hours for the MOGa-Dagum($\theta$, $a$, $\alpha$, $\beta$, $p$) distribution and 4.9688 hours for the MOGa-Weibull($\theta$, $a$, $\lambda$, $\gamma$) distribution.
+The  Tables \ref{tab:bias1} and  \ref{tab:bias2} reveal that the average biases of the MLEs could be very reduced only for $n> 2,000$.}
 
@@
 	\centering
-	\caption{Mean biases of the MLEs obtained using the BFGS method calculated from the Monte-Carlo simulation.}\label{tab:bias}
+	\caption{\textcolor{red}{Mean biases of the MLEs of the MOGa-Dagum($\theta$, $a$, $\alpha$, $\beta$, $p$) distribution obtained by the BFGS method calculated from the Monte-Carlo simulation.}}\label{tab:bias1}
 	\begin{tabular}{rrrrrrr}
@@
 		\hline
-		10 & 0.2376 & 2.1635 & 2.7557 & 1.6282 & 1.3057 & 1.1430\\
-		20 & 0.4154 & 2.4639 & 1.5728 & 1.8082 & 0.7383 & 1.6248\\
-		60 & 0.7214 & 2.2432 & 0.5667 & 1.8815 & 0.2872 & 3.3954\\
-		100 & 0.6146 & 1.9579 & 0.3253 & 1.6148 & 0.2651 & 4.9628\\
-		200 & 0.3838 & 1.3894 & 0.1827 & 1.1773 & 0.3701 & 8.1457\\
-		400 & 0.2166 & 0.9635 & 0.1076 & 0.6181 & 0.3957 & 13.7370\\
-		600 & 0.1269 & 0.7242 & 0.0772 & 0.3968 & 0.3637 & 17.9310\\
-		1,000 & 0.0553 & 0.4885 & 0.0521 & 0.2328 & 0.2636 & 22.8784 \\
-		2,000  &  0.0456 & 0.3087 &  0.0334 &  0.0990 & 0.1722 &  38.4593\\
-		5,000 & -0.0058 & 0.1307 & 0.0146 & 0.0117 & 0.0171 & 52.8098\\
-		10,000 & -0.0146 & 0.0842 & 0.0095 & 0.0095 & 0.0031 & 95.8380\\
-		20,000 & -0.0090 & 0.0330 & 0.0038 & 0.0005 & -0.0099 & 126.4260\\
-		30,000 & -0.0028 & 0.0183 & 0.0012 & -0.0036 & -0.0029 & 182.0760\\
-		50,000 & -0.0057 & 0.0124 & 0.0015 & 0.0016 & -0.0021 & 291.9300\\
+10 & 0.2213 & 2.1944 & 2.6971 & 1.5803 & 1.3190 & 0.6960 \\ 
+20 & 0.4240 & 2.4793 & 1.5591 & 1.8083 & 0.7414 & 0.9819 \\ 
+60 & 0.7458 & 2.2661 & 0.5598 & 1.8495 & 0.2812 & 1.9417 \\ 
+100 & 0.6194 & 1.9438 & 0.3312 & 1.6142 & 0.2935 & 2.7208 \\ 
+200 & 0.3950 & 1.4262 & 0.1856 & 1.1556 & 0.3611 & 4.4534 \\ 
+400 & 0.2077 & 0.9599 & 0.1082 & 0.6157 & 0.4076 & 7.4698 \\ 
+600 & 0.1200 & 0.7213 & 0.0767 & 0.4024 & 0.3572 & 9.4975 \\ 
+1000 & 0.0629 & 0.4791 & 0.0503 & 0.2123 & 0.2584 & 12.4221 \\ 
+2000 & 0.0362 & 0.2958 & 0.0298 & 0.1145 & 0.1878 & 20.7251 \\ 
+5000 & -0.0040 & 0.1325 & 0.0159 & 0.0144 & 0.0167 & 28.3380 \\ 
+10000 & -0.0133 & 0.0815 & 0.0096 & 0.0081 & 0.0039 & 50.9298 \\ 
+20000 & -0.0111 & 0.0349 & 0.0037 & 0.0006 & -0.0109 & 68.6320 \\ 
+30000 & -0.0036 & 0.0191 & 0.0006 & -0.0041 & -0.0034 & 97.3046 \\ 
+50000 & -0.0057 & 0.0129 & 0.0016 & 0.0015 & -0.0026 & 158.3737 \\ 
+		\hline
+	\end{tabular}
+\end{table}
+
+\begin{table}[H]
+	\centering
+	\caption{\textcolor{red}{Mean biases of the MLEs of the MOGa-Weibull($\theta$, $a$, $\lambda$, $\gamma$) distribution obtained by the BFGS method calculated from the Monte-Carlo simulation.}}\label{tab:bias2}
+	\begin{tabular}{rrrrrr}
+		\hline
+		$n$ & $B(\hat{\theta})$ & $B(\hat{a})$ & $B(\hat{\lambda})$ & $B(\hat{\gamma})$ & Time (mins)\\
+		\hline
+		10 & 0.0818 & 0.1362 & 4.9274 & 1.2407 & 0.6716 \\ 
+		20 & 0.3404 & -0.0177 & 3.4160 & 1.4117 & 0.8077 \\ 
+		60 & 0.7037 & -0.0677 & 1.8806 & 1.3385 & 1.1773 \\ 
+		100 & 0.6698 & -0.0535 & 1.3684 & 1.1796 & 1.2643 \\ 
+		200 & 0.5371 & -0.0299 & 0.8265 & 0.9110 & 1.7886 \\ 
+		400 & 0.3371 & -0.0047 & 0.4205 & 0.5967 & 2.8386 \\ 
+		600 & 0.2457 & 0.0076 & 0.2685 & 0.4306 & 3.6867 \\ 
+		1000 & 0.1476 & 0.0093 & 0.1553 & 0.2818 & 5.0944 \\ 
+		2000 & 0.0731 & 0.0035 & 0.0758 & 0.1530 & 8.8577 \\ 
+		5000 & 0.0264 & 0.0007 & 0.0283 & 0.0618 & 15.8586 \\ 
+		10000 & 0.0128 & -0.0007 & 0.0142 & 0.0318 & 29.8629 \\ 
+		20000 & 0.0053 & -0.0012 & 0.0071 & 0.0160 & 48.7417 \\ 
+		30000 & 0.0023 & -0.0014 & 0.0053 & 0.0119 & 64.7387 \\ 
+		50000 & 0.0023 & -0.0004 & 0.0028 & 0.0063 & 112.7422 \\ 
 		\hline
@@
 
-The log-likelihood for the Marshall-Olkin-Gamma-Weibull (MO-$\Gamma$-W) from one observation is
+The log-likelihood for the Marshall-Olkin-Gamma-Weibull (MOGa-W) from one observation is
 \begin{align}
@@
 where $FoodExpenditure_{food}$ is the random variable corresponding to the household expenditures for food and $\#(\cdot)$ indicates the number of
-observations on this variable. The MLEs and their standard errors (SEs) (in parentheses) are listed in Table \ref{tab-ex1}.
+observations on this variable. \textcolor{red}{Some descriptive statistics are displayed from Table \ref{tabds}. }
+
+\begin{table}[!htb] 
+\scriptsize
+\center
+\caption{Descriptive statistics for the first data}
+\label{tabds}
+\begin{tabular}{ ccccccccc}
+\hline\noalign{\smallskip}
+   Min. & 1st Qu.&  Median&    Mean& 3rd  Qu.&    Max. & sd &skewness & kurtosis\\
+   \hline
+ 0.1956  &0.2913 & 0.3903 & 0.4198 & 0.5027 & 0.7626 & 0.148009 & 0.5250021 & -0.4440273\\
+\hline
+\end{tabular}
+\end{table}
+
+\textcolor{red}{The minimum value in the table above refers to a family that has 3 people and with a family income of 39,.151US, which does not represent the lowest family income in the data set in question, as expected, occupying only the fifth position among those with the lowest income.
+The maximum value represents a family with a family income of 69,.929US and with 6 people, the second largest number among the number of people per family in the group in question.
+Furthermore, we can observe that the considered dataset presents positive asymmetry and negative kurtosis.
+Additionally, the standard deviation (sd) is relatively low.
+Figure \ref{ttt} of the data set referring to the first application indicates the decreasing form for the failure rate function.
+Therefore, these plots indicate the appropriateness of the MOGa-W distribution to fit these data, since the new model can present this form of the hrf, as showed in Figure \ref{fig:hazard}.
+}
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[scale =  1]{ttt1.eps}
+\caption{TTT plot for the fisrt data.\label{ttt}}
+\end{center}
+\end{figure}
+
+The MLEs and their standard errors (SEs) (in parentheses) are listed in Table \ref{tab-ex1}.
 The statistics  W$^{*}$ and A$^{*}$ are also given in this table. The results indicate that the proposed model has better performance than the other
@@
  & & & & &  \\
-MO-$\Gamma$-W$(a,\theta,\lambda,\gamma)$    &  0.926134 & 1.379664 & 33.323073 & 25.398809 & 0.0339 &  0.2376 \\                            &    (0.02626926) & (0.22381086) & (0.28530971) & (0.08259864)  & & \\
+MOGa-W$(a,\theta,\lambda,\gamma)$    &  0.926134 & 1.379664 & 33.323073 & 25.398809 & 0.0339 &  0.2376 \\                            &    (0.02626926) & (0.22381086) & (0.28530971) & (0.08259864)  & & \\
 
@@
 As a second application, consider a data set collected in a pilot study about hypertension in the Dominican Republic
-in 1997 found in \url{http://biostat.mc.vanderbilt.edu/wiki/
-Main/DataSets}. The observations are the systolic blood pressure of persons who came to medical clinics in
-several villages for a variety of complaints. The MLEs of the parameters, their SEs and the values of the statistics are
+in 1997. The observations are the systolic blood pressure of persons who came to medical clinics in
+several villages for a variety of complaints. 
+\textcolor{red}{ The data set in question has the following observations} 
+         150,
+         120,
+         120,
+         180,
+         138,
+         115,
+         130,
+         150,
+         200,
+         120,
+         190,
+         90,
+         130,
+         120,
+         200,
+         140,
+         110,
+         134,
+         160,
+         140,
+         105,
+         126,
+         129,
+         120,
+         100,
+         130,
+         118,
+         144,
+         180,
+         138,
+         110,
+         140,
+         120,
+         118,
+         110,
+         110,
+         130,
+         140,
+         130,
+         165,
+         180,
+         130,
+         140,
+         112,
+         130,
+         158,
+         112,
+         150,
+         140,
+         142,
+         110,
+         140,
+         130,
+         132,
+         140,
+         140,
+         122,
+         128,
+         90,
+         118,
+         120,
+         110,
+         122,
+         200,
+         110,
+         140,
+         150,
+         120,
+         150,
+         120,
+         164,
+         122,
+         112,
+         130,
+         140,
+         102,
+         122,
+         130,
+         102,
+         130,
+         122,
+         200,
+         140,
+         180,
+         124,
+         110,
+         124,
+         90,
+         120,
+         159,
+         142,
+         140,
+         118,
+         122,
+         108,
+         170,
+         120,
+         140,
+         100,
+         118,
+         110,
+         114,
+         150,
+         160,
+         140,
+         190,
+         118,
+         120,
+         150,
+         120,
+         200,
+         150,
+         168,
+         110,
+         142,
+         150,
+         160,
+         142,
+         160,
+         150,
+         110,
+         128,
+         122,
+         150,
+         140,
+         122,
+         120,
+         130,
+         100,
+         130,
+         150,
+         130,
+         100,
+         120,
+         105,
+         100,
+         150,
+         196,
+         130,
+         110,
+         140,
+         122,
+         110,
+         164,
+         120,
+         120,
+         150,
+         160,
+         150,
+         135,
+         124,
+         110,
+         100,
+         95,
+         130,
+         120,
+         108,
+         118,
+         170,
+         105,
+         120,
+         95,
+         95,
+         120,
+         140,
+         142,
+         160,
+         110,
+         190,
+         180,
+         130,
+         130,
+         120,
+         204,
+         150,
+         150,
+         120,
+         122,
+         120,
+         130,
+         140,
+         148,
+         118,
+         126,
+         136,
+         140,
+         130,
+         102,
+         110,
+         110,
+         130,
+         126,
+         142,
+         140,
+         128,
+         130,
+         124,
+         162,
+         130,
+         130,
+         110,
+         80,
+         166,
+         140,
+         160,
+         160,
+         140,
+         98,
+         138,
+         120,
+         112,
+         112,
+         134,
+         140,
+         115,
+         140,
+         98,
+         115,
+         120,
+         80,
+         160,
+         126,
+         110,
+         130,
+         104,
+         236,
+         118,
+         120,
+         140,
+         120,
+         98,
+         164,
+         150,
+         110,
+         120,
+         130,
+         170,
+         180,
+         110,
+         120,
+         130,
+         118,
+         130,
+         190,
+         158,
+         90,
+         99,
+         210,
+         180,
+         140,
+         184,
+         105,
+         120,
+         150,
+         140,
+         130,
+         160,
+         118,
+         210,
+         100,
+         170,
+         150,
+         130,
+         170,
+         150,
+         120,
+         134,
+         90,
+         125,
+         170,
+         140,
+         150,
+         110,
+         105,
+         140,
+         120,
+         100,
+         124,
+         112,
+         160,
+         140,
+         118,
+         190,
+         110,
+         118,
+         160,
+         150,
+         124,
+         128,
+         150,
+         120,
+         125,
+         118,
+         132,
+         110,
+         143,
+         170,
+         98,
+         124,
+         180,
+         178,
+         110,
+         98,
+         159,
+         110,
+         140,
+         130,
+         122,
+         110,
+         98,
+         180,
+         90,
+         118,
+         165,
+         138,
+         138,
+         170,
+         106,
+         170,
+         140,
+         90,
+         118,
+         110,
+         102,
+         102,
+         180,
+         100,
+         110,
+         162,
+         140,
+         110,
+         98,
+         140,
+         140,
+         110,
+         170,
+         112,
+         90,
+         102,
+         106,
+         124,
+         110,
+         180,
+         138,
+         90,
+         150,
+         126,
+         110,
+         130,
+         150,
+         145,
+         140,
+         156,
+         110,
+         150,
+         160,
+         120,
+         140,
+         120,
+         110,
+         120,
+         140,
+         160,
+         160,
+         110,
+         150,
+         118,
+         110,
+         120,
+         120,
+         146,
+         124,
+         170,
+         124,
+         170,
+         159,
+         120,
+         120,
+         118,
+         152,
+         190.
+
+\textcolor{red}{
+ Table \ref{tabds2} represents the descriptive statistics for the second data.
+Considering that the systolic blood pressure represents the highest number presented in the pressure measuring equipment, the maximum found in table (236) must represent an individual with serious heart problems.
+This is due to the fact that the value considered normal for systolic pressure is 120.
+}
+
+ \textcolor{red}{Regarding the minimum value (80), what we can conclude is that this observation must be from an individual who suffers from low blood pressure, probably.
+Also note that the data set has positive skewness.
+This indicates that few people have high pressure values  and, in this case, the mode is 120, which represents a good value for systolic pressure.
+}
+
+ \textcolor{red}{Figure \ref{ttt2} represents TTT plot for the second data. As seen in the first data set, the hrf function is decreasing, conforming to the forms found for the model function.  }
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[scale =  1]{ttt2.eps}
+\caption{TTT plot for the second data.\label{ttt2}}
+\end{center}
+\end{figure}
+
+\begin{table}[!htb] 
+\scriptsize
+\center
+\caption{Descriptive statistics for the second data}
+\label{tabds2}
+\begin{tabular}{ ccccccccc}
+\hline\noalign{\smallskip}
+   Min. & 1st Qu.&  Median&    Mean& 3rd  Qu.&    Max. & sd &skewness & kurtosis\\
+   \hline
+ 80   &  118    & 130&     133 &    150 &    236  &25.71575 &0.7893591 & 0.5908937\\
+\hline
+\end{tabular}
+\end{table}
+
+The MLEs of the parameters, their SEs and the values of the statistics are
 listed in Table \ref{tab-ex2} for the previous distributions. By comparing the measures of these formal statistics,
@@
  & & & & &  \\
-MO-$\Gamma$-W$(a,\theta,\lambda,\gamma)$    &  9.629304 & 3.640779 & 6.260826 & 12.823429 &0.5093&  2.8076 \\
+MOGa-W$(a,\theta,\lambda,\gamma)$    &  9.629304 & 3.640779 & 6.260826 & 12.823429 &0.5093&  2.8076 \\
                                        &    (0.006217876) & (0.182495785) & (0.024446563) & (0.007965221)  && \\
@@
 
-In this section, some main mathematical properties are presented for the MO-$\Gamma$-G family
+In this section, some main mathematical properties are presented for the MOGa-G family
 based on a general linear representation for its density function, which are important
-to determine its mathematical properties from those of exponentiated-G (exp-G) distributions.
+to determine its mathematical properties from those of exponentiated-G (exp-G) distribution.
 
@@
 By inserting \eqref{EXP33} in Equation \eqref{EXP44} and via a result for a power series raised to a positive integer (Gradshteyn and
-Ryzhik, 2000), the expansion for the cdf of the MO-$\Gamma$-G distribution reduces to
+Ryzhik, 2000), the expansion for the cdf of the MOGa-G distribution reduces to
 \begin{align*}
@@
 
-By differentiating the last equation, the expansion for the MO-$\Gamma$-G density follows as
+By differentiating the last equation, the expansion for the MOGa-G density follows as
 \begin{equation}\label{lcom}
@@
 Hereafter, let $T_{i,j}\sim$exp-G$[(i+1)a+j]$. The $n$th moment of $X$ can be obtained from (\ref{lcom}) as
+{\footnotesize
 \begin{eqnarray}\label{moment}
@@
 \end{eqnarray}
+}
 where
@@
 A general expansion for the moment generating function (MGF) $M(t)=E(\rm{e}^{t\,X})$ of $X$ can be expressed from (\ref{lcom})
+{\footnotesize
 \begin{eqnarray}\label{mgf}
@@
 \end{eqnarray}
+}
 where $M_{i,j}(t)$ is the MGF of $Y_{i,j}$ and
@@
 
-The MGFs of many MO-$\Gamma$-G distributions can be determined from Equation (\ref{mgf}).
-For example, the generating function of the MO-$\Gamma$-exponential with parameter $\lambda$
+The MGFs of many MOGa-G distributions can be determined from Equation (\ref{mgf}).
+For example, the generating function of the MOGa-exponential with parameter $\lambda$
 (if $t<\lambda^{-1}$) is
@@
 The $n$th incomplete moment of $X$ can be expressed as
-{\small
+{\footnotesize
 \begin{eqnarray}\label{incomplete}

### 2022-05-25 paper/reviews/answers/Reply_Letter_May_24.tex
Add TTT plots.

--- 2022-05-25 paper/letter_answers.tex
@@
-\documentclass[version=last,12pt,{"maintainersDelight"},letterpaper,]{scrlttr2}
+\documentclass[version=last,12pt,{"maintainersDelight"}]{scrlttr2}
 
@@
 
-\begin{letter}{\textbf{Replies to reviewers}\\\textbf{REVSTAT}\\}
-\opening{Dear \textbf{REVSTAT} Executive Editor and Reviews,}
+\begin{letter}{\textbf{Replies to reviewers' comments}\\\textbf{REVSTAT}\\}
+\opening{Dear Executive Editor and Reviews,}
 
-in this letter, I will respond to each of the reviewers valuable
+In this letter, we will answer to each of the reviewers valuable
 contributions. We try to accept all suggestions, aiming at a significant
@@
 1 -- The equality \(h(x)=f(x)/(1-F(x))\) is a well known relation
-between hazard, density and survival functions.
-It is not a definition of density or risk functions.
-Therefore, in page 3, line 12, the part of the sentence ``defined by \(h(x)=f(x)/(1-F(x))\)'' should be omitted.
+between hazard, density and survival functions. It is not a definition of density or risk functions. 
+Therefore, in page 3, line 12, the part of the sentence ``defined by \(h(x)=f(x)/(1-F(x))\)'' should be 
+omitted.
 
@@
 2 -- The expression (3.1) in page 6 corresponds to the log-likelihood of the MO-\(\Gamma\)-\(G\) distribution, 
-thus considering a Weibull distribution
-for \(G\) (although there is an error in the last sum 
+thus considering a Weibull distribution for \(G\) (although there is an error in the last sum 
 of line 1), not a general distribution with a \(\eta\) 
@@
 
-\emph{Response}:
+\emph{Response}: \textcolor{red}{Thank you. Done}.
 
@@
 \emph{Response}:
-\textcolor{red}{Indeed, the way in which the application section was introduced suggests that an attempt was made to fit the $G\sim Weibull$ model as a suitable distribution to the current datasets.
-In order to remove some ambiguity, we opted to extend the simulation studies, where we now include the $G\sim Weibull$ in the simulations.}
+{\color{red} Indeed, the way in which the application section was introduced suggests that a forced attempt was made to fit the $G\sim Weibull$ model as an adequate distribution to the datasets, thus clashing with the distribution considered in the simulations.
+To eliminate some ambiguity, we chose to extend the simulations studies, where we now also include the MOGa-Weibull distribution.
+
+Furthermore, the simulations of the MOGa-Dagum distribution were redone, considering that the current hardware is not 
+the same as that one we used at the time of submission.
+
+The Monte-Carlo simulations were performed in parallel, using the package \textbf{parallel} of the \texttt{R} language, in which the pseudo-random number generator considered for a processing with thread division was the L'Ecuyer-CMRG (see \url{https://pubsonline.informs.org/doi/abs/10.1287/opre.47.1.159} and \url{https://pubsonline.informs.org/doi/abs/10.1287/opre.50.6.1073.358}.
+As this generator depends on a fixed seed and also on the number of threads, which in turn depends on the hardware used, this was the other reason that led us to redo all the simulations.}
 
@@
 \emph{Response}:
-\textcolor{red}{Thank you for pointing that out. The Dagum distribution was now included in Table 1.}
+\textcolor{red}{Thank you for pointing that out. The Dagum distribution is now included in Table 1.}
 
@@
 \emph{Response}:
-\textcolor{red}{The use of the Anderson-Darling  $A^*$ and Cram\'er-von Mises $W^*$  statistics, corrected by Chen and Balakrishnan, in the paper entitled ``A General Purpose Approximate Goodness-of-Fit Test'' (see   \url{https://www.tandfonline.com/doi/abs/10.1080/00224065.1995.11979578}) is indicated for comparing mo\-dels that are not necessarily embedded.
+\textcolor{red}{The use of the Anderson-Darling  A$^*$ and Cram\'er-von Mises W$^*$  statistics, corrected by Chen and Balakrishnan, in the paper entitled ``A General Purpose Approximate Goodness-of-Fit Test'' (see   \url{https://www.tandfonline.com/doi/abs/10.1080/00224065.1995.11979578}) is indicated for comparing mo\-dels that are not necessarily embedded.
 Hence, considering the statistics returned by the \texttt{goodness.fit} function and the distributions compared, we understand that these statistics are the most suitable ones for
@@
 
-7 -- Figure 1: I suggest to change the lines to different types (even letting the colours as they are) so as to enable the interpretation in a black and white print.
-Also, the letters assigned to the parameters must agree with those in Table 1 (and, eventually, with those in expression (3.1)).
+7 -- Figure 1: I suggest to change the lines to different types (even letting the colours as they are) so as to enable the interpretation 
+in a black and white print. Also, the letters assigned to the parameters must agree with those in Table 1 (and, eventually, with those in expression (3.1)).
 
@@
 
-13 -- I suggest to make the labels of Figure 1 and of tables in \LaTeX, not in R.
+13 -- I suggest to make the labels of Figure 1 and of tables in \LaTeX, not in \texttt{R}.
 
 \emph{Response}:
-\textcolor{red}{Thanks for the suggestion. The change suggestion has been implemented.}
+\textcolor{red}{Thanks for the suggestion. This suggestion was implemented.}
 
@@
 3 - The bibliography does not have many recent publications such as
-Martinez-Florez et al. (2020) and Magalhaes et al.~(2020). I also
+Martinez-Florez et al. (2020) and Magalhães et al.~(2020). I also
 suggest authors to create the state-of-art related to this topic in the first section that definitively needs to be improved.
 
-\emph{Response}:
+\emph{Response}: \textcolor{red}{Done.}
 
 4 - I expect to see more detailed discussion in the simulation study and real data analysis. Could you revise these sections, including the conclusion section that is actually weak?
+
+\emph{Response}: \textcolor{red}{Missing.}
 
@@
   \item
-    \textcolor{red}{ Really, the title of the paper was no good.
-We changed to \textbf{Marshall and Olkin-Gamma-G family of distributions: properties and applications}.
+    \textcolor{red}{Really, the title of the paper was no good.
+We changed to \textbf{The Marshall and Olkin-Gamma-G family of distributions: properties and applications}.
 We believe that the title now clarifies the paper's proposal better.
-It is worth mentioning that the new name is consistent with the sequential application of the MO family to the baseline Gamma-G.}
+It is worth mentioning that the new title is very consistent with the sequential application of the MO family to the baseline Gamma-G.}
   \end{enumerate}

### 2022-05-25 code/plots/plots.R

@@ -1,247 +1,684 @@
-  library(ggplot2)
-  library(cowplot)
-  
-  # Baseline functions. -----------------------------------------------------
-  pdf_weibull <- function(x, alpha, beta)
-   dweibull(x, shape = alpha, scale = beta)
-  
-  cdf_weibull <- function(x, alpha, beta)
-    pweibull(x, shape = alpha, scale = beta)
-  
-  # This function creates MOGW functions ----------------------------------
-  pdf_mogw <- function(g, G) {
-    # Using Closures.
-    function(x, theta, a, ...) {
-      if (theta <= 0 || a <= 0)
-        warning("The \"a\" and \"theta\" parameters must be greater than zero.")
-      num <-
-        theta * (-log(1 - G(x = x, ...))) ^ (a - 1) * g(x = x, ...)
-      den <-
-        gamma(a) * (theta + (1 - theta) * pgamma(-log(1 - G(x = x, ...)), a, 1L)) ^
-        2
-      num / den
-    }
-  }
-  
-  pdf_mogweibull <- pdf_mogw(g = pdf_weibull, G = cdf_weibull)
-  
-  hazard <- function(x, theta, a, alpha, beta) {
-    survival_f <- function(x, theta, a, alpha, beta)
-      1 - integrate(
-        f = pdf_mogweibull,
-        lower = .Machine$double.eps,
-        upper = x,
-        theta,
-        a,
-        alpha,
-        beta
-      )$value
-    
-    vectorize_survival_f <-
-      Vectorize(FUN = survival_f, vectorize.args = "x")
-    
-    pdf_mogweibull(x, theta, a, alpha, beta) / vectorize_survival_f(x, theta, a, alpha, beta)
-  }
-  
-  #  Plots Probability densiy function  -------------------------------------
-  cores <- c("Legenda 1" = "#FF6B58",
-             "Legenda 2" = "#FF4373",
-             "Legenda 3" = "#9239F6",
-             "Legenda 4" = "#E3D26D")
-  
-  type_lines <- c("solid",
-                  "dotted",
-                  "dotdash",
-                  "twodash")
-  
-  base <- ggplot(data.frame(x = c(0, 10)), aes(x)) +
-    # ggtitle(
-    #   "Probability density function",
-    #   subtitle = "With G following the Weibull distribution "
-    # ) +
-    theme(
-      plot.title = element_text(face = "bold"),
-      axis.title = element_text(face = "bold"),
[…]

### 2022-05-25 code/yacas.R

@@ -1,0 +1,18 @@
+library(Ryacas)
+
+G <- "(1 + (x/beta) ^ (-alpha)) ^ (-p)"
+g <- y_fn(G, "D(x)") |> yac_str()
+
+fun <- function(x, alpha, beta, p){
+  eval(yac_expr(g))
+}
+
+Fun <- function(x, alpha, beta, p){
+  eval(yac_expr(G))
+}
+
+paste0("theta * (-Ln(1 - (", G, ")))^(alpha - 1) * ", g) |> 
+  y_fn(fn = "Simplify") |> 
+  yac_str() |> 
+  y_fn(fn = "TexForm") |> 
+  yac_str()

### 2022-05-30 paper/carta_resposta/letter_answers.tex
Add tex

--- 2022-05-25 paper/reviews/answers/Reply_Letter_May_24.tex
@@
 {\color{red} Indeed, the way in which the application section was introduced suggests that a forced attempt was made to fit the $G\sim Weibull$ model as an adequate distribution to the datasets, thus clashing with the distribution considered in the simulations.
-To eliminate some ambiguity, we chose to extend the simulations studies, where we now also include the MOGa-Weibull distribution.
+We chose to extend the simulation studies to eliminate some
+ambiguity, where we now also include the MOGa-Weibull distribution.
 
-Furthermore, the simulations of the MOGa-Dagum distribution were redone, considering that the current hardware is not 
+Furthermore, the simulations of the MOGa-Dagum distribution were redone by considering that the current hardware is not 
 the same as that one we used at the time of submission.
 
-The Monte-Carlo simulations were performed in parallel, using the package \textbf{parallel} of the \texttt{R} language, in which the pseudo-random number generator considered for a processing with thread division was the L'Ecuyer-CMRG (see \url{https://pubsonline.informs.org/doi/abs/10.1287/opre.47.1.159} and \url{https://pubsonline.informs.org/doi/abs/10.1287/opre.50.6.1073.358}.
+The Monte-Carlo simulations were performed in parallel using 
+the  \textbf{parallel-}package of the \texttt{R} language, in which the pseudo-random number generator considered for a processing with thread division was the L'Ecuyer-CMRG (see \url{https://pubsonline.informs.org/doi/abs/10.1287/opre.47.1.159} and \url{https://pubsonline.informs.org/doi/abs/10.1287/opre.50.6.1073.358}.
 As this generator depends on a fixed seed and also on the number of threads, which in turn depends on the hardware used, this was the other reason that led us to redo all the simulations.}
@@
 by one of the authors of this paper and it was published at \url{https://journals .plos.org/plosone/article?id=10.1371/journal.pone.0221487}. 
-A code inspection of the \texttt{goodness.fit} function can be done by looking at the link   \href{https://github.com/prdm0/AdequacyModel/blob/master/R/goodness.fit.R}{link} on GitHub, where it is hosted the development versioning of the package.}
+A code inspection of the \texttt{goodness.fit} function can be done by looking at the    \href{https://github.com/prdm0/AdequacyModel/blob/master/R/goodness.fit.R}{link} on GitHub, where it is hosted the development versioning of the package.}
 
@@
 
-7 -- Figure 1: I suggest to change the lines to different types (even letting the colours as they are) so as to enable the interpretation 
-in a black and white print. Also, the letters assigned to the parameters must agree with those in Table 1 (and, eventually, with those in expression (3.1)).
+7 -- Figure 1: I suggest to change the lines to different types (even letting the colours as they are) so as to enable the interpretation in a black and white print.
+Also, the letters assigned to the parameters must agree with those in Table 1 (and, eventually, with those in expression (3.1)).
 
@@
 \emph{Response}:
-\textcolor{red}{Thanks for the suggestion. This suggestion was implemented.}
+\textcolor{red}{Thanks for the suggestion. It was implemented.}
 
@@
 
-\emph{Response}: \textcolor{red}{Missing.}
+\emph{Response}: \textcolor{red}{We noticed the need to modify the simulations. So, we extended the simulations to the MOGa-Weibull family to be adopted in the data applications. We also add 
+the \texttt{R} code on GitHub (see \url{https://github.com/prdm0/MOGG}) for easy checking 
+and reuse by readers of the paper.}
 
@@
     \textcolor{red}{Really, the title of the paper was no good.
-We changed to \textbf{The Marshall and Olkin-Gamma-G family of distributions: properties and applications}.
+Then, we changed to \textbf{``The Marshall and Olkin-Gamma-G family of distributions: properties and applications''}.
 We believe that the title now clarifies the paper's proposal better.
-It is worth mentioning that the new title is very consistent with the sequential application of the MO family to the baseline Gamma-G.}
+It is worth mentioning that the new title is very consistent with the sequential application of the MO family to the baseline Gamma-G class.}
   \end{enumerate}
@@
 To access the codes, see the link
-    \url{https://github.com/prdm0/MOGG/tree/master/code/simulations}}.
+    \url{https://github.com/prdm0/MOGG/tree/master/code/simulations}}.\\\\
   \end{enumerate}

### 2022-05-30 paper/paper.tex
Add tex

@@
 \vspace{1.5cm}
-\title{Marshall and Olkin-G and Gamma-G family of distribution: properties and applications
+\title{\color{red}{The Marshall and Olkin-G and Gamma-G family of distributions: properties and applications
 	%\footnote{The opinions expressed in this text are those of the authors and do not necessarily reflect the views of any organization.}
-}
+}}
 \renewcommand{\titleheading}
-{MOGG family of distribution: properties and applications}  % --- on odd running heads
+{The MOGG family of distributions}  % --- on odd running heads
 
@@
 \begin{abstract}
-This article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes. The family has only two
-extra shape parameters and can be a better model  than other existing classes of distributions. Simulations are performed to verify the
-consistency of the estimators. Its flexibility is shown using two real data sets.
+The article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes. It has only two
+extra shape parameters and can be a better model than other existing classes of distributions.
+Simulations are performed to verify the consistency of the estimators.
+Its flexibility is shown by means of two real data sets.
 \end{abstract}
@@
 \begin{keywords}
- Distribution family;  mathematical properties; simulations; applications.
+Applications; distribution family; mathematical properties; simulations. 
 \end{keywords}
@@
 
-The mechanism by adding shape parameters to a baseline distribution has
-proved to be useful to make the generated distributions more flexible especially for studying tail
-properties than existing distributions and for improving their goodness-of-fit statistics
-to the data under study. Many special distributions in these families are discussed by Tahir
-and Nadarajah (2015).
+\textcolor{red}{The advances in the field of Data Science requires the search for new fa\-milies of distributions that adequately model real data has been increasing steadily in the last years.
+The construction of different generation methods and even generators of families has made it difficult to compare new proposals.
+In the midst of a huge set of existing families in the literature of new distributions, to find a proposal that is in fact an excellent competitor when compared to other existing ones, in terms of adjustment to real data sets and also that does not present estimation problems, is a major challenge.}
+
+\textcolor{red}{The classes of distributions in the early 1980s were based on the simple idea of adding parameters to a baseline distribution.} The mechanism by adding shape parameters to a baseline distribution has proved to be useful to make the
+generated distributions more flexible especially for studying 
+tail properties than existing ones and for improving their goodness-of-fit statistics to real data. Many special 
+distributions in these families are discussed by Tahir and Nadarajah (2015).
+
+\textcolor{red}{The addition of parameters in the construction of new distributions/families was improved by the inclusion of mathematical functions known in the literature, such as beta and gamma functions, for example, which produce new generators
+with more flexible properties than their baselines. 
+Two well-known examples are the beta-G (Eugene et al., 2002) 
+and gamma-G (Zografos and Balakrishnan, 2009) generators.}
+
+\textcolor{red}{However, the inclusion of such functions for generating new families brought, in some cases, problems for parameter estimation.
+So, despite the fit being more suitable for some types of data and, therefore, having a superior performance when compared to other generators, the estimation process can
+often be a problem.}
+
+\textcolor{red}{In this context, this work presents a new family obtained by composing a very competitive class in the literature with another class that has the gamma function in its structure.}
 
@@
 baseline distribution and $g(x)=dG(x)/dx$ be the corresponding  probability density function (PDF) depending on a
-parameter vector $\eta$. A generalized family are presented
-with two additional shape parameters by transforming the CDF $G(x)$
-according to two sequential important gene\-rators. These families are important for modeling data
-in several engineering areas.
-
-The CDF of the Marshall and Olkin's (1997) ($\text{MO-G}$) family (for $\theta>0$) is
+parameter vector $\eta$. A generalized family is presented
+with two extra shape parameters by transforming the CDF $G(x)$
+according to two sequential important classes. 
+These classes, \textcolor{red}{called Marshall and Olkin-G
+and Gamma-G}, are important for modeling data in several areas,  \textcolor{red}{and they are reviewed below}.
+
+The CDF of the Marshall and Olkin's (1997) ($\text{MO-G}$) 
+class (for $\theta>0$) is
 \begin{equation}\label{CDF_MO}
@@
 
-Tahir and Nadarajah (2015, Table 2) presented thirty distributions
-belonging to this family. It is easily generated from the baseline quantile function (QF) by
+Tahir and Nadarajah (2015, Table 2) presented thirty 
+distributions belonging to this family. It is easily generated 
+from the baseline quantile function (QF) by
 $Q_{\text{MO-G}}(u)=Q_{G}\left(\theta u / \left[\theta u+1-u\right]\right)$ for $u\in(0,1)$.
@@
 Marshall and Olkin considered the exponential and Weibull distributions for the baseline G and derived some
-structural properties of the generated distributions. The special case that G is an exponential distribution
-refers to a two-parameter competitive model to the Weibull and gamma distributions.
-
-The CDF of the gamma-G ($\Gamma$-G) family (Zografos and Balakrishnan, 2009) is
+structural properties of the generated distributions. 
+If G is an exponential distribution, the special case 
+refers to a two-parameter competitive model to the 
+Weibull and gamma distributions.
+
+The CDF of the gamma-G ($\Gamma$-G) class (Zografos and Balakrishnan, 2009) is
 \begin{eqnarray}\label{CDF_Ga}
@@
 \end{eqnarray}
-where $a>0$ is an extra shape parameter,  $\gamma_1(a,z)= \gamma(a,z)/\Gamma(a)$ is the incomplete gamma function ratio
+where $a>0$ is an extra shape parameter, $\gamma_1(a,z)= \gamma(a,z)/\Gamma(a)$ is the incomplete gamma function ratio, 
 and $\gamma(a,z)=\int_0^{z} t^{a-1}\,\rm{e}^{-t}dt$.
 
-Then, the PDF of the $\Gamma$-G family can be expressed as
+Then, the PDF of the $\Gamma$-G class can be expressed as
 \begin{eqnarray}\label{PDF_Ga}
@@
 
-Each new $\Gamma$-G distribution follows from a given baseline G.
-For $a=1$, the $\Gamma$-G family reduces to G.
+Each new $\Gamma$-G distribution follows from a given 
+baseline G. For $a=1$, the $\Gamma$-G class reduces to G.
 If $Z$ is a gamma random variable with unit scale
-parameter and shape parameter $a>0$, then $W=Q_G(1-\rm{e}^{-Z})$ has density (\ref{PDF_Ga}). So,
-the $\Gamma$-G distribution is easily generated from the gamma distribution and the QF of G.
-
-The remaining of the paper is addressed as follows. Section \ref{sec:MOGaG} introduces the {\it Marshall and Olkin-Gamma-G} (MOGa-G)
-family and presents some special models. The maximum likelihood estimates (MLEs) of the parameters of the new family is addressed
-in Section \ref{estimation}. Some simulations ate performed in Section \ref{sec:simulation} to estimate the biases of the MLEs. Two
-empirical applications illustrate the potentiality of the proposed family in Section \ref{applications}. A variety of theoretical properties are derived
-in Section \ref{properties}. Some conclusions remarks are offered in Section \ref{conclusions}.
+and shape $a>0$, then $W=Q_G(1-\rm{e}^{-Z})$ has density (\ref{PDF_Ga}). So, the $\Gamma$-G distribution is easily 
+generated from the gamma distribution and the QF of G.
+
+The remaining of the paper is addressed as follows.
+Section \ref{sec:MOGaG} introduces the {\it Marshall and Olkin-Gamma-G} (MOGa-G) family, and provides some special models.
+The maximum likelihood estimates (MLEs) of its parameters is addressed in Section \ref{estimation}.
+Some simulations are performed in Section \ref{sec:simulation} to estimate the biases of the MLEs.
+Two empirical applications illustrate the potentiality of the proposed family in Section \ref{applications}.
+A variety of theoretical properties are obtained in Section \ref{properties}.
+Some conclusions remarks are offered in Section \ref{conclusions}.
 
@@
 
-By combining Equations (\ref{CDF_MO}) and (\ref{CDF_Ga}), the CDF of the random variable $X\sim$MOGa-G
-representing the new family is defined by
+By combining Equations (\ref{CDF_MO}) and (\ref{CDF_Ga}), the CDF of the random variable $X\sim$MOGa-G representing the new family 
+has the form 
 \begin{equation}\label{CDF_MO-Gamma-G}
@@
 The density (\ref{PDF_MO-Gamma-G}) can be interpreted from a sequence of $N$ iid random variables, say $Z_1,\cdots,Z_N$,
-each one having a gamma density with unit scale parameter and shape parameter $a>0$, assuming that $N$ (is not fixed) has a geometric 
+each one having a gamma density with unit scale and shape $a>0$, assuming that $N$ (is not fixed) has a geometric 
 distribution with probabilities $\theta$ and $\theta^{-1}$ for $0<\theta<1$ and $\theta>1$,
-respectively. By transforming the $Z_i$'s via the baseline QF by $W_i=Q_G(1-\rm{e}^{-Z_i})$
-(for $i-1,\ldots,N$), Equation \eqref{densityMO} is defines the PDF of the minimum $W_1,\cdots,W_n$. 
-Making this double composition of the two generators, the proposed family absorbs the impacts of two different flexibilities 
-on applications.
-
-Table 1 provides some special cases of (\ref{PDF_MO-Gamma-G}), where
-$\Phi(x)$ and $\phi(x)$ are the CDF and PDF of the standard normal distribution. The density and hazard functions
-of the Marshall-Olkin-$\Gamma$-Weibull (MOGa-W) defined by $h(x) = f(x)/(1-F(x))$ are displayed in Figure \ref{formas}, which provide
-more flexibility for these functions in relation to the baseline ones.
+respectively. By transforming the $Z_i$'s via the baseline QF by $W_i=Q_G(1-\rm{e}^{-Z_i})$ (for $i=1,\ldots,N$), Equation \eqref{densityMO} defines the PDF of the minimum $W_1,\cdots,W_n$. 
+The proposed family from the double composition of the two 
+classes absorbs the impacts of their different flexibilities on real applications.
+
+Table 1 provides some special cases of (\ref{PDF_MO-Gamma-G}), where $\Phi(x)$ and $\phi(x)$ are the CDF and PDF of the standard normal distribution.
+The density and hazard ($h(x) = f(x)/[1-F(x)]$) functions of the MOGa-Weibull (MOGa-W) model
+are displayed in Figure \ref{formas}, which provide more flexibility to both functions for both classes applied separately to the Weibull model.
 
@@
 
-\begin{figure}
+\begin{figure}[H]
 	\centering
@@
 		\includegraphics[width=\textwidth]{pdf_function.pdf}
-		\caption{MOGa-W density function.}
+		\caption{Density function.}
 		\label{fig:pdf}
@@
 		\includegraphics[width=\textwidth]{hazard_function.pdf}
-		\caption{MOGa-W hazard function.}
+		\caption{Hazard function.}
 		\label{fig:hazard}
 	\end{subfigure}
-\caption{MOGa-W density function and  MOGa-W hazard function with G following the Weibull distribution.}
+\caption{The density and hazard functions of the MOGa-W model.}
 \label{formas}
@@
 
-The CDF \eqref{CDF_MO-Gamma-G} can be easily inverted to calculate the QF of the MOGa-G distribution,
-say $x=Q_{X}(u)=F_X^{-1}(u)$ for $u \in (0,1)$, in terms of the Q$_F$ of the baseline distribution G, $Q_G(\cdot)$. The inverse of
-$F_{X}(x)=u$, where $u$ is a uniform number in $(0,1)$ is easily obtained. By combining the inverses
-of Equations (\ref{CDF_MO})and \eqref{CDF_MO-Gamma-G}, $F_{X}(x)=u$ leads to
-$z=z(u)=\theta u/[1-(1-\theta)u]$ and $\gamma_{1}\left(a, -\log[1-G(x)]\right)=z(u)$.
-Then, the QF of $X$ can be expressed as
+The CDF \eqref{CDF_MO-Gamma-G} can be easily inverted to 
+calculate the QF of the MOGa-G distribution, say $x=Q_{X}(u)=F_X^{-1}(u)$ (for $u \in (0,1)$), in terms of 
+the baseline QF $Q_G(\cdot)$. The inverse of
+$F_{X}(x)=u$, where $u$ is a uniform number in $(0,1)$, 
+follows by combining the inverses of Equations (\ref{CDF_MO}) and \eqref{CDF_MO-Gamma-G}. So, $F_{X}(x)=u$ gives 
+$z=z(u)=\theta u/[1-(1-\theta)u]$ and $\gamma_{1}\left(a, -\log[1-G(x)]\right)=z(u)$. Hence, the QF of $X$ can be 
+expressed as
 $$x=Q_G\left(v(u)\right),$$
@@
 and $\gamma_1^{-1}(a,w)=Q^{-1}(a,1-w)$ is the inverse function of $\gamma_1(a,w)$. Some formulae for
-$Q^{-1}(a,1-w)$ are given in \url{http:// functions.wolfram.com/ GammaBetaErf/ InverseGammaRegularized/}.
-
-\begin{landscape}
-	\begin{table}[htbp]\label{tabspecial1}
+$Q^{-1}(a,1-w)$ are given in \url{http://functions.wolfram.com/GammaBetaErf/InverseGammaRegularized/}.
+
+%\begin{landscape}
+\begin{table}[H]\label{tabspecial1}
 \caption{Special Distributions in the  MOGa-G family.}
 \centering
-\scalebox{0.7}{	
+\scalebox{0.73}{
 \begin{tabular}{l|l|l}
@@
 \hline
-			\textbf{Dagum} & $G(x) = \Big[1 + \Big(\frac{x}{\beta}\Big) ^ {-\alpha}\Big] ^ {-p},\,\, \alpha, \beta, p > 0$ & $f_X(x) = \frac{\theta  \left\{ -\log[1-G(x)] \right\}^{a-1}\, g(x)}{\Gamma(a)\{\theta + (1 - \theta)\gamma_1[a, -\log   (1-((x/\beta)^{-\alpha}+1)^{-p})]\}}$ \\
-			\hline
-		\end{tabular} }
+\textbf{Dagum} & $G(x) = [1 + (x/\beta) ^ {-\alpha}] ^ {-p},\,\, \alpha, \beta, p > 0$ & $f_X(x) = \frac{\theta  \left\{ -\log[1-[1 + (x/\beta) ^ {-\alpha}] ^ {-p}] \right\}^{a-1}\, g(x)}{\Gamma(a)\{\theta + (1 - \theta)\gamma_1[a, -\log   (1-((x/\beta)^{-\alpha}+1)^{-p})]\}}$ \\
+\hline
+\end{tabular}}
 \end{table}
-\end{landscape}
+%\end{landscape}
 
@@
 
-The  MOGa-G family can be  fitted to real data using the {\bf AdequacyModel} package, {\color{red}Marinho et al. (2019)}, in the {\sf R} software.
-This packa\-ge does not require to define the log-likelihood function and it computes the MLEs, their standard errors (SEs)
-and the formal statistics defined in Section \ref{applications}. It is necessary to provide the
+The MOGa-G family can be fitted to real data using the {\bf AdequacyModel} package ({\color{red}Marinho et al., 2019}) 
+in the {\sf R} software. This packa\-ge does not require to 
+define the log-likelihood function, and it computes the MLEs, 
+their standard errors (SEs), and the formal statistics defined 
+in Section \ref{applications}. It is only necessary to provide the
 PDF and CDF of the distribution to be fitted to a data set.
 
-For example, if $x_i$ is one observation from (\ref{PDF_MO-Gamma-G}) and $\etn$ is a $q$-parameter vector specifying $G(\cdot)$,
-the log-likelihood function for $\boldsymbol{\theta}^\top=(a,\theta,\etn^\top)$ from $n$ observations is
+For example, if $x_i$ is one observation from (\ref{PDF_MO-Gamma-G}) and $\etn$ is a $q$-parameter vector specifying $G(\cdot)$ \textcolor{red}{as the Weibull CDF}, the log-likelihood function for $\boldsymbol{\theta}^\top=(a,\theta,\etn^\top)$ from $n$ observations can be expressed as
 \begin{align}\label{loglik}
@@
 
-Due to the impossibility of obtaining the MLEs in closed form, numerical methods to obtain the estimates that maximize $ \ell (\cdot) $ are necessary.
-Several programming languages and statistical software distributes functions and routines that make it easy to obtain numerical estimates by various interactive methods.
-In practice, obtaining the MLEs for the parameters that index a probability distribution are commonly obtained in this way, since the Newton and quasi-Newton methods produce satisfactory results under reasonable conditions of the object function, that is, when they do not impose conditions that disturb the convergence of the algorithms.
-
-To obtain the MLEs, the package {\bf AdequacyModel} of the programming language {\sf R} was used, see R Core Team (2020).
-This library, created and maintained by one of the authors of this paper, is widely cited by several papers in the field of statistics and serves as a basis for other library implementations available on the Comprehensive R Archive Network - CRAN.
-With it, in particular using the goodness.fit function, it is possible to provide an implementation {\sf R} of (\ref {PDF_MO-Gamma-G}), being in charge of this function, obtain $\ell(\cdot)$  by returning several measures of fit adequacy as well as the MLEs.
-Further details regarding this package can be obtained from Marinho et al.
-(2019).
+Due to the impossibility of obtaining the MLEs in closed form, numerical methods to calculate the estimates that maximize $\ell(\cdot)$ are necessary.
+Several programming languages and statistical software provides functions and routines that make it easy to obtain numerical estimates by various interactive methods.
+In practice, these estimates are commonly found in this way, since the Newton and quasi-Newton methods produce satisfactory results under reasonable conditions of the object function, i.e., when they do not impose restrictions that disturb the convergence of
+the algorithms.
+
+The {\bf AdequacyModel} package of the programming language {\sf R} is used to obtain the MLEs, see R Core Team (2020). This library, created and maintained by one of the authors of this paper,
+is widely cited by several works in statistics, and serves as 
+a basis for other library implementations available on the Comprehensive R Archive Network (CRAN). By using the goodness.fit function, it is possible to provide an implementation  
+of (\ref {PDF_MO-Gamma-G}), and obtain $\ell(\cdot)$ by returning the MLEs, and some measures of adequacy of fit. Further details regarding this package can be obtained from Marinho et al. (2019).
 
@@
 
-For doing that, the biases of the estimators of the parameters of the
-MOGa-Dagum($\theta$, $a$, $\alpha$, $\beta$, $p$) and  MOGa-Weibull($\theta$, $a$, $\lambda$, $\gamma$) distribution are determined, where $G\sim \mathrm {Dagum} (\alpha, \beta, p)$ and  $\mathrm {Weibull} (\gamma, \lambda)$ are the baselines distributions, respectively.
-All parameters are taken equal to one for different sample sizes reported in the Tables \ref{tab:bias1} and \ref{tab:bias2}.
-
-The Tables \ref{tab:bias1} and \ref{tab:bias2} indicate that this method behaves well when the sample size increases.
-This is theoretically expected.
-However, in practice, difficulties can be faced in other families of distributions due to the flatness of the log-likelihood function.
-
-All simulations can be reproduced using the script in \url{https://github.com/prdm0/MOGG}.
-The simulations are parallelized and able to use all threads available by a multicore processor, thus making them more computationally efficient and consequently requiring less time to complete.
-
-The simulations are performed on a computer with an Intel(R) Core(TM) i5-9500 CPU processor with 6 threads working at a maximum frequency of 3.00GHz, requiring, on these hardware, a time of 15.4828 hours to perform all simulations, 7.7414 hours for the MOGa-Dagum($\theta$, $a$, $\alpha$, $\beta$, $p$) distribution and 4.9688 hours for the MOGa-Weibull($\theta$, $a$, $\lambda$, $\gamma$) distribution.
-The  Tables \ref{tab:bias1} and  \ref{tab:bias2} reveal that the average biases of the MLEs could be very reduced only for $n> 2,000$.}
-
-To generate observations from the random variable $X$ with density $f$, the well-known Acceptance-Rejection Algorithm for continuous random variables, which is very useful when the quantile function involves complex functions that can lead to some numerical inaccuracies.
+In order to do that, the biases of the estimators of the 
+parameters of the MOGa-Dagum($\theta,a,\alpha,\beta,p$) and  MOGa-Weibull($\theta,a,\lambda,\gamma$) distributions 
+are determined, where $G\sim \mathrm {Dagum} (\alpha,\beta,p)$ and $\mathrm {Weibull} (\gamma,\lambda)$ are the baseline models, respectively. All parameters are taken equal to 
+one for different sample sizes reported in Tables \ref{tab:bias1} and \ref{tab:bias2}.
+
+The numbers in Tables \ref{tab:bias1} and \ref{tab:bias2} 
+indicate that the estimation method behaves well when the 
+sample size increases. This is theoretically expected. However, 
+in practice, difficulties can be faced to other families due 
+to the flatness of the log-likelihood function.
+
+All Monte Carlo simulations can be reproduced using the script 
+in \url{https://github.com/prdm0/MOGG}. The simulations are parallelized and able to use all threads available by a multicore processor, thus making them more computa\-tio\-nally efficient, 
+and consequently requiring less time to complete.
+
+The simulations are performed on a computer with an Intel(R) Core(TM) i5-9500 CPU processor with 6 threads working at a maximum frequency of 3.00GHz, requiring, on this hardware, a time of 15.4828 hours to perform all simulations, 7.7414 hours for the MOGa-Dagum($\theta, a, \alpha, \beta, p$) distribution,
+and 4.9688 hours for the MOGa-Weibull($\theta, a, \lambda, \gamma$) distribution. Tables \ref{tab:bias1} and  \ref{tab:bias2} 
+reveal that the average biases of the MLEs could be very small for $n>2,000$.}
+
+To generate observations from the random variable $X$ with density $f$, the well-known Acceptance-Rejection Algorithm for 
+continuous random variables is very useful when the QF involves complex functions that can lead to some numerical inaccuracies.
 For doing this, another random variable $Y$ is chosen such that it can generate observations from a PDF $h$ with the same support as $f$.
@@
 The constant $c$ must be chosen in such a way that $\frac{f(y)}{c \,g (y)}\leq 1 $.
-Thus, to minimize the computational cost of generating observations from $X$ through the generated observations from $Y$, $c$ is chosen 
-as the lowest possible value to maximize the likelihood of acceptance. Further details of this method can be found in Rizzo (2019).
+Thus, to minimize the computational cost of generating observations from $X$ through the generated observations from $Y$, $c$ is chosen as the lowest possible value to maximize the likelihood of acceptance.
+Further details of this method can be found in Rizzo (2019).
 
@@
 \centering
-	\caption{\textcolor{red}{Mean biases of the MLEs of the MOGa-Dagum($\theta$, $a$, $\alpha$, $\beta$, $p$) distribution obtained by the BFGS method calculated from the Monte-Carlo simulation.}}\label{tab:bias1}
+\caption{\textcolor{red}{Average biases of the MLEs of the MOGa-Dagum($\theta, a, \alpha, \beta, p$) distri\-bu\-tion 
+calculated by the BFGS method from simulations.}}\label{tab:bias1}
 	\begin{tabular}{rrrrrrr}
@@
 	\centering
-	\caption{\textcolor{red}{Mean biases of the MLEs of the MOGa-Weibull($\theta$, $a$, $\lambda$, $\gamma$) distribution obtained by the BFGS method calculated from the Monte-Carlo simulation.}}\label{tab:bias2}
+\caption{\textcolor{red}{Average biases of the MLEs of the MOGa-Weibull($\theta, a, \lambda, \gamma$) distribution calculated 
+by the BFGS method from simulations.}}\label{tab:bias2}
 	\begin{tabular}{rrrrrr}
@@
 
-Consider the Weibull baseline. Two applications are provided to compare the new generated model with seven extended Weibull
-distributions, namely the beta-Weibull ($\beta$-W) (Famoye {\it et al.}, 2005), Kumaraswamy Weibull (Kw-W) (Cordeiro and Nadarajah, 2010),
-Marshall-Olkin Weibull (MO-W) (Ahmed {\it et al.}, 2017), Marshall-Olkin Extended Weibull (MOE-W) (Cordeiro {\it et al.}, 2019),
-exponentiated Weibull (exp-W) (Mudholkar and Srivastava, 1993), gamma Weibull ($\Gamma$-W) Cordeiro {\it et al.}, 2016) and exponentiated
-generalized Weibull (EG-W) (Oguntunde {\it et al.}, 2015) (with $a=1$). Some of these distributions are widely used in practice.
-
-The log-likelihood for the Marshall-Olkin-Gamma-Weibull (MOGa-W) from one observation is
+Two applications compare the MOGa-Weibull (MOGa-W for short) 
+model with seven extended Weibull distributions: the 
+beta-Weibull ($\beta$-W) (Famoye et al., 2005), 
+Kumaraswamy Weibull (Kw-W) (Cordeiro et al., 2010), 
+Marshall-Olkin Weibull (MO-W) (Ahmed et al., 2017), 
+Marshall-Olkin Extended Weibull (MOE-W) (Cordeiro et al., 2019), exponentiated Weibull (exp-W) (Mudholkar and Srivastava, 1993), gamma Weibull ($\Gamma$-W) (Cordeiro et al., 2016), 
+and exponentiated generalized Weibull 
+(EG-W) (Oguntunde et al., 2015) (with $a=1$). Some of 
+these distributions are widely used in practice.
+
+The log-likelihood for $\boldsymbol{\theta}$ from the MOGa-W distribution from one observa\-tion can be expressed as 
 \begin{align}
@@
 U_{a}(\boldsymbol{\theta})=\gamma  \log (\lambda )+\gamma  \log (x)-\psi ^{(0)}(a)-\frac{2\left\{(1-\theta ) A-(1-\theta ) \psi ^{(0)}(a) \gamma_1 \left[a,(x \lambda
-   )^{\gamma }\right]\right\}}{\theta\,\Gamma(a)+(1-\theta)\gamma_1\left[a,(x \lambda
-   )^{\gamma }\right]},
+   )^{\gamma }\right]\right\}}{\theta\,\Gamma(a)+(1-\theta)\gamma_1\left[a,(\lambda x)^{\gamma }\right]},
 \end{equation*}
@@
 \begin{equation*}
-U_{\theta}(\boldsymbol{\theta})=\frac{1}{\theta}-\frac{2\left\{\Gamma(a)-\gamma_1\left[a,(\lambda\,x)^\gamma\right]\right\}}{\theta\,\Gamma(a)+(1-\theta)\gamma_1\left[a,(\lambda\,x)^\gamma\right]},
+U_{\theta}(\boldsymbol{\theta})=\frac{1}{\theta}-\frac{2\left\{\Gamma(a)-\gamma_1\left[a,(\lambda\,x)^\gamma\right]\right\}}{\theta\,\Gamma(a)+(1-\theta)\gamma_1\left[a,(\lambda x)^\gamma\right]},
 \end{equation*}
@@
 U_{\lambda}(\boldsymbol{\theta})=\frac{\gamma }{\lambda }\left[a-(\lambda\,x)^\gamma\right]+\frac{2 \gamma \,\lambda^{-1}(\lambda\,x)^{a\,\gamma} (1-\theta )\exp\{-(\lambda\,x)^\gamma\} }{\theta \,\Gamma(a)+(1-\theta )
-   \gamma_1 \left[a,(x \lambda )^{\gamma }\right]}
+   \gamma_1 \left[a,(\lambda x)^{\gamma }\right]}
 \end{equation*}
@@
 \begin{equation*}		
-U_{\gamma}\boldsymbol{\theta}=\frac{1}{\gamma }+a \log (\lambda )+a \log (x)-(\lambda  x)^{\gamma } \log
+U_{\gamma}(\boldsymbol{\theta})=\frac{1}{\gamma }+a \log (\lambda )+a \log (x)-(\lambda  x)^{\gamma } \log
    (\lambda  x)+\frac{2 (1-\theta )(\lambda
-   x)^{\gamma\,a } \log (\lambda  x)\exp\{-(\lambda  x)^{\gamma }\}  }{\theta \,\Gamma(a)+(1-\theta )
-   \gamma_1 \left[a,(x \lambda )^{\gamma }\right]},
+   x)^{\gamma\,a } \log (\lambda  x)\exp\{-(\lambda x)^{\gamma }\}  }{\theta \,\Gamma(a)+(1-\theta)\,
+   \gamma_1\left[a,(\lambda x)^{\gamma }\right]},
 \end{equation*}
-where
+where $\psi^{(n)}(x)$ is the $n$th derivative of the digamma function,
 \begin{align*}
-A=G_{2,3}^{3,0}\left[(x \lambda )^{\gamma }\Big{|}
+A=\log\left[(\lambda  x)^{\gamma }\right] \,\gamma_1 \left[a,(\lambda x)^{\gamma}\right]
++G_{2,3}^{3,0}\left((\lambda x)^{\gamma }\Big{|}
 \begin{array}{c}
@@
 \end{array}
-\right]+\log \left[(\lambda  x)^{\gamma }\right] \gamma_1 \left[a,(x \lambda )^{\gamma
-   }\right],
+\right),
 \end{align*}
-$\psi^{(n)}(x)$ is the $n$-th derivative of the digamma function,
-\begin{eqnarray*}
-A=\psi^{(0)}(a) - \log\left[(\lambda x)^{\gamma}\right]-G^{3,0}_{2,3}\,\left((\lambda x)^{\gamma} \Big{|}	\stackrel{1,1}{0,0,a}\right),
-\end{eqnarray*}
 and $G^{m,n}_{p,q}\,\left(z \Big{|}	\stackrel{a_{1},\ldots,a_{p}}{b_{1},\ldots,b_{q}}\right)$ is the Meijer G function.
 
-The {\bf AdequacyModel} is used to fit the distributions cited before to two real data sets. The SANN method, which is a
-variant of simulated annealing (Belisle, 1992), is considered. The distributions are compared via the Anderson
-Darling (A$^{*}$) and Cram\'er Von Mises (W$^{*}$) statistics reported in the {\tt goodness.fit} function.
-
-For the first data set, a modification of the ``FoodExpenditure'' data from the {\bf betareg} package  is considered, which refers
-to the proportions of income spent on food for a random sample of 38 households in a large US city (according to the package information).
-Here, the household expenditures for food are considered and is given by
+The {\bf AdequacyModel} package is used to fit the 
+previous distributions to two real data sets. The SANN method, which is a variant of simulated annealing algorithm (Belisle, 1992), is used here. The distributions are compared 
+via the Anderson Darling (A$^{*}$) and Cram\'er Von Mises (W$^{*}$) statistics reported in the {\tt goodness.fit} function.
+
+For the first case, the {\bf betareg} package is applied to a modification of the ``FoodExpenditure'' data, which refer to 
+the proportions of income spent on food for 38 households 
+in a large US city (according to the package information). The household expenditures for food are given by
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-where $FoodExpenditure_{food}$ is the random variable corresponding to the household expenditures for food and $\#(\cdot)$ indicates the number of
-observations on this variable. \textcolor{red}{Some descriptive statistics are displayed from Table \ref{tabds}. }
-
-\begin{table}[!htb] 
+where $FoodExpenditure_{food}$ is the random variable 
+corresponding to the household expenditures for food, and $\#(\cdot)$ indicates the number of observations on this variable. \textcolor{red}{The observations for the first data set are given bellow:\\
+  0.4210000, 0.4382105, 0.5721316, 0.1955526, 0.2758158, 0.3565263,
+  0.6120000, 0.4730526, 0.3726579, 0.2322368, 0.3732632, 0.5158947,
+  0.3612632, 0.5563421, 0.4591053, 0.2533947, 0.3685526, 0.2410526,
+  0.4955526, 0.2010789, 0.3653158, 0.2544737, 0.5685263, 0.2859474,
+  0.7626316, 0.2863684, 0.4884474, 0.3060263, 0.4754474, 0.3826053,
+  0.5050526, 0.6820526, 0.7587632, 0.4176053, 0.3923684, 0.2513158,
+  0.6070000, 0.3881842.}
+
+\textcolor{red}{Some descriptive statistics are reported in Table \ref{tabds}. The minimum value refers to a family of 3 people and income of 39,151, which does not represent the lowest family 
+income for the current data, as expected, occupying only the 
+fifth position among those with the lowest income.
+The maximum value corresponds to a family of 6 people with an income of 69,929, the second-largest number among the number of people per family in the group in question.
+Furthermore, we can note that the current data  present positive asymmetry and negative kurtosis.}
+
+\textcolor{red}{In addition, the standard deviation is relatively low.
+Figure \ref{ttt} displays the total time on test (TTT) plot for the first data set, which shows that the failure function is decreasing.
+So, the MOGa-W distribution is appropriate to fit
+these data, since its  hazard function presents this shape (see,  Figure \ref{fig:hazard}).}
+
+\begin{table}[H] 
+%\scriptsize
+\center
+\caption{Descriptive statistics for the food data.}
+\label{tabds}
+\begin{tabular}{lc}
+\hline\noalign{\smallskip}
+   Minimum &  0.1956\\
+   1st Qu.& 0.2913 \\
+   Median&  0.3903 \\
+   Mean& 0.4198\\
+   3rd  Qu.&    0.5027\\
+   Maximum & 0.7626\\
+   Standard Deviation & 0.1480\\
+   Skewness & 0.5250\\
+   Kurtosis &-0.4440\\
+   \hline
+
+\end{tabular}
+\end{table}
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[height=8cm, width=8cm]{TTT_app_1.pdf}
+\caption{TTT plot for the food data.\label{ttt}}
+\end{center}
+\end{figure}
+
+The MLEs, their standard errors (SEs) (in parentheses), and the statistics W$^{*}$ and A$^{*}$ for the fitted models to the current data are listed in Table \ref{tab-ex1}.
+The results indicate that the proposed model has better performance than the other seven fitted models.
+
+\begin{table}[H]
 \scriptsize
 \center
-\caption{Descriptive statistics for the first data}
-\label{tabds}
-\begin{tabular}{ ccccccccc}
-\hline\noalign{\smallskip}
-   Min. & 1st Qu.&  Median&    Mean& 3rd  Qu.&    Max. & sd &skewness & kurtosis\\
-   \hline
- 0.1956  &0.2913 & 0.3903 & 0.4198 & 0.5027 & 0.7626 & 0.148009 & 0.5250021 & -0.4440273\\
-\hline
-\end{tabular}
-\end{table}
-
-\textcolor{red}{The minimum value in the table above refers to a family that has 3 people and with a family income of 39,.151US, which does not represent the lowest family income in the data set in question, as expected, occupying only the fifth position among those with the lowest income.
-The maximum value represents a family with a family income of 69,.929US and with 6 people, the second largest number among the number of people per family in the group in question.
-Furthermore, we can observe that the considered dataset presents positive asymmetry and negative kurtosis.
-Additionally, the standard deviation (sd) is relatively low.
-Figure \ref{ttt} of the data set referring to the first application indicates the decreasing form for the failure rate function.
-Therefore, these plots indicate the appropriateness of the MOGa-W distribution to fit these data, since the new model can present this form of the hrf, as showed in Figure \ref{fig:hazard}.
-}
-
-\begin{figure}[H]
-\begin{center}
-\includegraphics[scale =  1]{ttt1.eps}
-\caption{TTT plot for the fisrt data.\label{ttt}}
-\end{center}
-\end{figure}
-
-The MLEs and their standard errors (SEs) (in parentheses) are listed in Table \ref{tab-ex1}.
-The statistics  W$^{*}$ and A$^{*}$ are also given in this table. The results indicate that the proposed model has better performance than the other
-seven fitted models.
-
-\begin{table}[!htb]
-\scriptsize
-\center
-\caption{  \small Application 1}
+\caption{\small Estimation results for food data.}
 \label{tab-ex1}
+\scalebox{1.1}{
 \begin{tabular}{lcccccc}
 \hline\noalign{\smallskip}
-Model & $a$ & $\theta$ & $\lambda$ & $\gamma$ &  $W^*$ & $A^*$   \\
+Model & $\hat{a}$ & $\hat{\theta}$ & $\hat{\lambda}$ & $\hat{\gamma}$ &  $W^*$ & $A^*$   \\
 \hline \\
  & & & & &  \\
-MOGa-W$(a,\theta,\lambda,\gamma)$    &  0.926134 & 1.379664 & 33.323073 & 25.398809 & 0.0339 &  0.2376 \\                            &    (0.02626926) & (0.22381086) & (0.28530971) & (0.08259864)  & & \\
-
- & & & & &  \\
-$\beta-$W$(a,\theta,\lambda,\gamma)$ &   9.92882 &  0.1700880 & 9.759469 & 1.530541  & 0.043567 & 0.2594618\\
-                                    &    (0.02908181) & (0.02049663) & ($<$0.0001) & ($<$0.0001)  && \\
-                                                                                & & & & &  \\
-KW-W$(a,\theta,\lambda,\gamma)$ &    0.04987575 & 99.99989793 &  1.07602954 & 23.40287099 & 1.330915 & 6.742609\\
-                                       &    (0.008090352) & (16.225905058) &  (0.003156126) &  (0.014646102) && \\																						 & & & & &  \\
-                                       MOE-W$(a,\theta,\lambda,\gamma)$  &  0.1366666 & 2.020436 & 62.72201 & 4.2956659  &0.03541554 & 0.2579222 \\
- & (0.1599182) & ($<$0.0001) &($<$0.0001) & (0.7365535)    &  & \\
-                                                                              & & & & &  \\
-EGW$(a,b,\lambda,\gamma)$    &  5.6189861421 &  6.1833138579 &  1.2870816760  & 1.3798562942  &  0.03715255 & 0.2518879 \\
-& (0.0028147823) & (0.0009807091) & (0.1159810838) & (0.1480747352)    &  & \\
-                                                           & & & & &  \\                                                           MO-W$(a,\lambda,\gamma)$  & 0.15920715  & - &  1.58609458  & 4.26713785  &  0.03456333   & 0.257339\\
-&    (0.07170351) & (-) & (0.13353716) & (0.16650667)  &  & \\
-
- & & & & &  \\
-exp-W$(a,\lambda,\gamma)$   &    6.1102948   & - &   4.4680469 &  1.3858740 &   0.03726684   & 0.2523749 \\
-&   (0.4222173) & (-) & (0.3175876) & (0.1677722)   &  & \\
-
- & & & & &  \\
-$\gamma$-W$(a,\lambda,\gamma)$    & 5.751546  & - &  10.0000 & 1.208773&  0.0879 & 0.6599  \\
-&  (0.0015006)&  (-)&  (0.0001163185) &(0.00822782)    &  & \\
-
- & & & & &  \\
-
-%GammaBS$(a,b,\alpha)$     &  1.2354 & 40.4438 &  0.1379 &       & 0.4931 &   2.7656 &  0.3725 & $1.765x10^{-12}$\\
-                          %&  ( 0.0025)& ( 14.6913)& (0.0446) &      & &&  && \\
-                                                     \hline
-\end{tabular}
+MOGa-W$(a,\theta,\lambda,\gamma)$    &  0.9261 & 1.3796 & 33.3230 & 25.3988 & 0.0339 &  0.2376 \\                            &    (0.0262) & (0.2238) & (0.2853) & (0.0825)  & & \\
+
+ & & & & &  \\
+$\beta-$W$(a,\theta,\lambda,\gamma)$ &   9.9288 &  0.1700 & 9.7594 & 1.5305  & 0.0435 & 0.2594\\
+&    (0.0290) & (0.0204) & ($<$0.0001) & ($<$0.0001)  && \\
+                                                                                & & & & &  \\
+KW-W$(a,\theta,\lambda,\gamma)$ &    0.0498 & 99.9998 &  1.0760 & 23.4028 & 1.3309 & 6.7426\\
+ &    (0.0080) & (16.2259) &  (0.0031) &  (0.0146) && \\																						 & & & & &  \\
+MOE-W$(a,\theta,\lambda,\gamma)$  &  0.1366 & 2.0204 & 62.7220 & 4.2956  &0.0354 & 0.2579 \\
+ & (0.1599) & ($<$0.0001) &($<$0.0001) & (0.7365)    &  & \\
+                                                                              & & & & &  \\
+EGW$(a,b,\lambda,\gamma)$    &  5.6189 &  6.1833 &  1.2870  & 1.3798  &  0.0371 & 0.2518 \\
+& (0.0028) & (0.0009) & (0.1159) & (0.1480)    &  & \\
+                                                           & & & & &  \\
+MO-W$(a,\lambda,\gamma)$  & 0.1592  & - &  1.5860  & 4.2671  &  0.0345   & 0.2573\\
+&    (0.0717) & (-) & (0.1335) & (0.1665)  &  & \\
+
+ & & & & &  \\
+exp-W$(a,\lambda,\gamma)$   &    6.1102   & - &   4.4680 &  1.3858 &   0.0372   & 0.2523 \\
+&   (0.4222) & (-) & (0.3175) & (0.1677)   &  & \\
+
+ & & & & &  \\
+$\gamma$-W$(a,\lambda,\gamma)$    & 5.7515  & - &  10.0000 & 1.2087&  0.0879 & 0.6599  \\
+&  (0.0015)&  (-)&  (0.0001) &(0.0082)    &  & \\
+
+ & & & & &  \\
+\hline
+\end{tabular}}
 \end{table}
 
-As a second application, consider a data set collected in a pilot study about hypertension in the Dominican Republic
-in 1997. The observations are the systolic blood pressure of persons who came to medical clinics in
-several villages for a variety of complaints. 
-\textcolor{red}{ The data set in question has the following observations} 
+A data set collected in a pilot study about hypertension in the Dominican Republic in 1997 refers to the second application. The observations are the systolic blood pressure of persons who 
+came to medical clinics in several villages for a variety of complaints. 
+\textcolor{red}{The observations for the data set in question are:} 
          150,
@@
 
-\textcolor{red}{
- Table \ref{tabds2} represents the descriptive statistics for the second data.
-Considering that the systolic blood pressure represents the highest number presented in the pressure measuring equipment, the maximum found in table (236) must represent an individual with serious heart problems.
-This is due to the fact that the value considered normal for systolic pressure is 120.
-}
-
- \textcolor{red}{Regarding the minimum value (80), what we can conclude is that this observation must be from an individual who suffers from low blood pressure, probably.
+\textcolor{red}{Table \ref{tabds2} provides the descriptive statistics for the second data set.
+Consi\-dering that the systolic blood pressure represents the highest number presented in the pressure measuring equipment, the maximum (236) found in this
+table should represent an individual with serious heart problems. This is due to the fact that the normal systolic pressure is 120.}
+
+ \textcolor{red}{The minimum value (80) should be for 
+ an individual who probably suffers from low blood pressure.
 Also note that the data set has positive skewness.
-This indicates that few people have high pressure values  and, in this case, the mode is 120, which represents a good value for systolic pressure.
-}
-
- \textcolor{red}{Figure \ref{ttt2} represents TTT plot for the second data. As seen in the first data set, the hrf function is decreasing, conforming to the forms found for the model function.  }
+This indicates that few people have high pressure values and, in this case, the mode is 120, which represents a good value for systolic pressure.}
+
+ \textcolor{red}{Figure \ref{ttt2} provides the TTT plot 
+ for the second clinic data, which shows that the hazard function is decreasing, thus supporting the MOGa-W model.}
 
@@
 \begin{center}
-\includegraphics[scale =  1]{ttt2.eps}
-\caption{TTT plot for the second data.\label{ttt2}}
+\includegraphics[height=8cm, width=8cm]{TTT_app_2.pdf}
+\caption{TTT plot for the clinic data.\label{ttt2}}
 \end{center}
@@
 
-\begin{table}[!htb] 
+\begin{table}[H] 
+%\scriptsize
+\center
+\caption{Descriptive statistics for the clinic data.}
+\label{tabds2}
+\begin{tabular}{lr}
+\hline\noalign{\smallskip}
+   Minimum & 80\\
+   1st Qu.& 118\\
+   Median&  130\\
+   Mean& 133 \\
+   3rd  Qu.&  150 \\
+   Maximum &  236\\
+   Standard Deviation & 25.7157\\
+   Skewness & 0.7893\\
+   Kurtosis & 0.5908\\
+\hline
+\end{tabular}
+\end{table}
+
+The MLEs of the parameters, their SEs and the values of the adequacy measures for the fitted models to the clinic data 
+are reported in Table \ref{tab-ex2}. By comparing the measure values, the proposed distribution outperforms all other 
+fitted models.
+
+\begin{table}[H]
 \scriptsize
 \center
-\caption{Descriptive statistics for the second data}
-\label{tabds2}
-\begin{tabular}{ ccccccccc}
-\hline\noalign{\smallskip}
-   Min. & 1st Qu.&  Median&    Mean& 3rd  Qu.&    Max. & sd &skewness & kurtosis\\
-   \hline
- 80   &  118    & 130&     133 &    150 &    236  &25.71575 &0.7893591 & 0.5908937\\
-\hline
-\end{tabular}
-\end{table}
-
-The MLEs of the parameters, their SEs and the values of the statistics are
-listed in Table \ref{tab-ex2} for the previous distributions. By comparing the measures of these formal statistics,
-we conclude that the proposed distribution outperforms the rest of them.
-
-\begin{table}[htb!]
-\scriptsize
-\center
-\caption{  \small Application 2}
+\caption{\small Estimation results for clinic data.}
 \label{tab-ex2}
+\scalebox{1.1}{
 \begin{tabular}{lcccccc}
 \hline\noalign{\smallskip}
-Model & $a$ & $\theta$ & $\lambda$ & $\gamma$ &  $W^*$ & $A^*$   \\
-\hline
- & & & & &  \\
-MOGa-W$(a,\theta,\lambda,\gamma)$    &  9.629304 & 3.640779 & 6.260826 & 12.823429 &0.5093&  2.8076 \\
-                                       &    (0.006217876) & (0.182495785) & (0.024446563) & (0.007965221)  && \\
-
- & & & & &  \\
- $\beta-$W$(a,\theta,\lambda,\gamma)$ &   31.08471 &  47.14636 &   0.01698383 &  2.054037 & 0.7540428 & 4.279418\\
-&    (0.01279570) & ($<$0.0001) & (0.00014535) & ($<$0.0001)  && \\
-
- & & & & &  \\
-KW-W$(a,\theta,\lambda,\gamma)$ &   7363.281 & 0.03925762 &  1.467640 &   0.6146940 & 0.5351 & 2.9617\\
-                                       &    (0.04194304) & (0.0004194304)& ($<$0.0001)& ($<$0.0001) && \\
-
- & & & & &  \\
- MOE-W$(a,\theta,\lambda,\gamma)$  &  101.13471834 &  0.42386507  & 0.03095935 &  1.70240332  &1.14418 & 6.644617 \\
-                            & (46.782882038) &  (0.100832102) &  (0.003644092) &  (0.168142275)   &  & \\
-
- & & & & &  \\
- EGW$(a,b,\lambda,\gamma)$    &  0.2351691 &  140.0000 &   0.4576370 &   0.7425738 &  0.8925 & 5.3338 \\
-                            & (0.002540837) & (3.278565) & ($<$0.0001) & ($<$0.0001)   &  & \\
-
- & & & & &  \\
- MO-W$(a,\lambda,\gamma)$  & 173.2139  & - &  0.02125455 &  1.601970  &  1.476088   & 8.58705\\
-                                       &    (0.00016394) & (-) & (0.000212794) & (0.0001398109)  &  & \\
-
- & & & & &  \\
- exp-W$(a,\lambda,\gamma)$   &    69.02916  & - &   0.02405120 & 1.345536 &   0.8899261   & 5.094141 \\
-                          &   (0.08389090) & (-) & (0.0002249256) & ($<$0.0001)   &  & \\
-
- & & & & &  \\
- $\Gamma$-W$(a,\lambda,\gamma)$    & 9.11229459   & - &  0.02617729 & 1.74641178 &    0.6227098 & 3.488268  \\
-                             &  (0.96330688)&  (-)&  (0.00291875) & (0.08030313)     &  & \\
-
- & & & & &  \\
-
-%GammaBS$(a,b,\alpha)$     &  1.2354 & 40.4438 &  0.1379 &       & 0.4931 &   2.7656 &  0.3725 & $1.765x10^{-12}$\\
-                          %&  ( 0.0025)& ( 14.6913)& (0.0446) &      & &&  && \\
-                                                    \hline
-\end{tabular}
+Model & $\hat{a}$ & $\hat{\theta}$ & $\hat{\lambda}$ & $\hat{\gamma}$ &  $W^*$ & $A^*$   \\
+\hline
+ & & & & &  \\
+MOGa-W$(a,\theta,\lambda,\gamma)$    &  9.6293 & 3.6407 & 6.2608 & 12.8234 &0.5093&  2.8076 \\
+                                       &    (0.0062) & (0.1824) & (0.0244) & (0.0079)  && \\
+
+ & & & & &  \\
+ $\beta-$W$(a,\theta,\lambda,\gamma)$ &   31.0847 &  47.1463 &   0.0169 &  2.0540 & 0.7540 & 4.2794\\
+&    (0.0127) & ($<$0.0001) & (0.0001) & ($<$0.0001)  && \\
+
+ & & & & &  \\
+KW-W$(a,\theta,\lambda,\gamma)$ &   7363.2810 & 0.0392 &  1.4676 &   0.6146 & 0.5351 & 2.9617\\
+&    (0.0419) & (0.0004)& ($<$0.0001)& ($<$0.0001) && \\
+
+ & & & & &  \\
+ MOE-W$(a,\theta,\lambda,\gamma)$  &  101.1347 &  0.4238  & 0.0309 &  1.7024  &1.1441 & 6.6446 \\
+ & (46.7828) &  (0.1008) &  (0.0036) &  (0.1681)   &  & \\
+
+ & & & & &  \\
+ EGW$(a,b,\lambda,\gamma)$    &  0.2351&  140.0000 &   0.4576 &   0.7425 &  0.8925 & 5.3338 \\
+ & (0.0025) & (3.2785) & ($<$0.0001) & ($<$0.0001)   &  & \\
+
+ & & & & &  \\
+ MO-W$(a,\lambda,\gamma)$  & 173.2139  & - &  0.0212 &  1.6019  &  1.4760   & 8.5870\\                                &    (0.0001) & (-) & (0.0002) & (0.0001)  &  & \\
+
+ & & & & &  \\
+ exp-W$(a,\lambda,\gamma)$   &    69.0291  & - &   0.0240 & 1.3455 &   0.8899   & 5.0941 \\
+                          &   (0.0838) & (-) & (0.0002) & ($<$0.0001)   &  & \\
+
+ & & & & &  \\
+ $\Gamma$-W$(a,\lambda,\gamma)$    & 9.1122   & - &  0.0261 & 1.7464 &    0.6227 & 3.4882  \\
+                             &  (0.9633)&  (-)&  (0.0029) & (0.0803)     &  & \\
+
+ & & & & &  \\
+                          \hline
+\end{tabular}}
 \end{table}
@@
 
-In this section, some main mathematical properties are presented for the MOGa-G family
-based on a general linear representation for its density function, which are important
-to determine its mathematical properties from those of exponentiated-G (exp-G) distribution.
+Here, some mathematical properties for the MOGa-G family are presented based on a linear representation for its density 
+function in terms of ``exponentiated-G'' (exp-G) densities.
 
@@
 
-For an arbitrary CDF $G(x)$, the CDF and PDF of the exponentiated-G (exp-G) distribution with power parameter $a>0$ are
+For an arbitrary CDF $G(x)$, the CDF and PDF of the exp-G distribution with power parameter $a>0$ are
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-respectively. This class of distributions is quite useful in several applications. In fact, Tahir and Nadarajah (2015)
-cited more than seventy papers on exponentiated distributions in their Table 1.
-
-First, the MO-G cumulative distriution (\ref{densityMO}) admits the
-linear combination (Barreto-Souza \emph{et al.}, 2013)
+respectively. This class of distributions is quite useful 
+in several applications. In fact, Tahir and Nadarajah (2015)
+cited more than seventy papers on exponentiated distributions 
+in their Table 1.
+
+First, the CDF of the MO-G distribution (\ref{densityMO}) 
+admits the linear representation (Barreto-Souza et al., 2013)
 \begin{equation}
@@
 
-Second, the linear combination for the $\Gamma\text{-G}$ cumulative distribution (\ref{PDF_Ga}) follows from Castellares and Lemonte (2015) as
+Second, the linear combination for the $\Gamma\text{-G}$ cumulative distribution (\ref{PDF_Ga}) follows from Castellares and 
+Lemonte (2015) as
 \begin{equation}\label{EXP33}
@@
 
-By differentiating the last equation, the expansion for the MOGa-G density follows as
+By differentiating the last equation, the linear representation 
+for the MOGa-G density holds
 \begin{equation}\label{lcom}
@@
 So, some structural properties of the proposed family can be determined from the double linear combination (\ref{lcom})
-and those properties of the exp-G distribution. In most applications, the indices $i$ and $j$ can vary up to five.
+and those properties of the exp-G distribution. In most applications, the indices $i$ and $j$ can vary up to a small 
+number of terms.
 
@@
 
-Hereafter, let $T_{i,j}\sim$exp-G$[(i+1)a+j]$. The $n$th moment of $X$ can be obtained from (\ref{lcom}) as
+Hereafter, let $T_{i,j}\sim$exp-G$[(i+1)a+j]$. The $n$th moment of $X$ can be determined from (\ref{lcom}) as
 {\footnotesize
@@
 
-Expressions for moments of several exponentiated distributions can be found in the papers
-cited in Tahir and Nadarajah (2015, Table 1). We give just one example from Equation (\ref{moment})
+Expressions for moments of several exponentiated distributions can be found in the papers cited in Tahir and Nadarajah (2015, Table 1). We give just one example from Equation (\ref{moment})
 by taking the exponential distribution with rate $\lambda>0$ for the baseline G.
@@
 
-A general expansion for the moment generating function (MGF) $M(t)=E(\rm{e}^{t\,X})$ of $X$ can be expressed from (\ref{lcom})
+For empirical purposes, the shape of many distributions can be usefully described by the incomplete moments. These moments play an important role for measuring
+inequa\-lity. For example, the mean deviations and Lorenz and Bonferroni curves depend upon the first incomplete moment of the distribution.
+The $n$th incomplete moment of $X$ can be expressed as
+{\footnotesize
+\begin{eqnarray}\label{incomplete}
+\displaystyle
+\qquad
+m_{n}(y)=\int_{-\infty}^y x^n\,f_{X}(x) dx = \sum_{i,j=0}^{\infty} [(i+1)a+j]\,d_{i,j}\,\int_{0}^{G(y)}\,Q_G(u)^n\, u^{(i+1)a+j-1}\,du.
+\end{eqnarray}
+}
+The definite integral in (\ref{incomplete}) can be evaluated for most baseline G distributions.
+
+The moment generating function (MGF) $M(t)=E(\rm{e}^{t\,X})$ of $X$ can be expressed from (\ref{lcom})
 {\footnotesize
@@
 
-The MGFs of many MOGa-G distributions can be determined from Equation (\ref{mgf}).
-For example, the generating function of the MOGa-exponential with parameter $\lambda$
+The MGFs of several MOGa-G distributions can be determined from Equation (\ref{mgf}). For example, the generating function of the MOGa-exponential with parameter $\lambda$
 (if $t<\lambda^{-1}$) is
@@
 
-For empirical purposes, the shape of many distributions can be usefully described by
-the incomplete moments. These moments play an important role for measuring
-inequa\-lity. For example, the mean deviations and Lorenz and Bonferroni curves depend upon the first incomplete moment of the distribution.
-The $n$th incomplete moment of $X$ can be expressed as
-{\footnotesize
-\begin{eqnarray}\label{incomplete}
-\displaystyle
-\qquad
-m_{n}(y)=\int_{-\infty}^y x^n\,f_{X}(x) dx = \sum_{i,j=0}^{\infty} [(i+1)a+j]\,d_{i,j}\,\int_{0}^{G(y)}\,Q_G(u)^n\, u^{(i+1)a+j-1}\,du.
-\end{eqnarray}
-}
-The definite integral in (\ref{incomplete}) can be evaluated for most baseline G distributions.
-
 \section{CONCLUSIONS}\label{conclusions}
 
-A new family of distributions called the Marshall and Olkin-Gamma-G family with two shape parameters is introduced. The estimation of the unknown
-parameters is done via the maximum likelihood method and a simulation study is conducted to verify its adequacy. Additionally, the usefulness
-of the proposed family is shown empirically by means of two applications to real data.
+A new family of distributions called the Marshall and Olkin-Gamma-G family with two shape parameters is introduced.
+The estimation of the unknown parameters is done via the maximum likelihood method and a simulation study is conducted to verify its adequacy.
+Additionally, the usefulness of the proposed family is shown empirically by means of two applications to real data.
+In fact, the new family can generate very competitive distributions with the same number of parameters than others constructed by existing classes.
 
@@
 \item
-A. Alzaatreh, F. Famoye, C. Lee:
-A new method for generating families of continuous distributions.
-Metron {\bf 71}(1) 63-79 (2013).
-
-\item
-W. Barreto-Souza, A.J. Lemonte, G.M. Cordeiro:
-General results for the Marshall and Olkin's family of distributions.
-Anais da Academia Brasileira de Ci\^{e}ncias {\bf 85}(1) 3-21 (2013).
-
-\item
-Z.W. Birnbaum, S.C. Saunders:
-A new family of life distributions.
-Journal of Applied Probability {\bf 6}(2) 319-327 (1969).
-
-\item
-F. Castellares, A.J. Lemonte:
-A new generalized Weibull distribution gene\-rated by gamma random variables.
-Journal of the Egyptian Mathematical Society {\bf 23}(2) 382-390 (2015).
-
-\item
-G.M. Cordeiro, M. de Castro:
-A new family of generalized distributions.
-Journal of Statistical Computation and Simulation {\bf 81}(7) 883-898 (2011).
-
-\item
-N. Eugene, C. Lee, F. Famoye:
-Beta-normal distribution and its applications.
-Communications in Statistics -- Theory and Methods {\bf 31}(4) 497-512 (2002).
-
-\item
-
-Gradshteyn IS, Ryzhik IM: Table of Integrals, Series and Products. Sixth edition. San Diego: Academic Press (2000).
-
-\item
-R.C. Gupta, R.D. Gupta, P.L. Gupta:
-Modeling failure time data by Lehmann alternatives.
-Communications in Statistics -- Theory and Methods {\bf 27}(4) 887-904 (1998).
-
-\item
-R.D. Gupta, D. Kundu:
-Exponentiated exponential family: an alternative to gamma and Weibull distributions.
-Biometrical Journal {\bf 43}(1) 117-130 (2001).
-
-%\item
-%P. Kumaraswamy:
-%Generalized probability density-function for double-bounded
-%random-processes. Journal of Hydrology {\bf 46}(1-2) 79-88 (1980).
-
-\item
-A.J. Lemonte, G.M. Cordeiro, G. Moreno-Arenas:
-A new useful three-parameter extension of the exponential distribution.
-Statistics {\bf 50}(2) 312-337 (2016).
+M.H. Tahir, S. Nadarajah:
+Parameter induction in continuous univariate distributions: Well-established G families.
+Anais da Academia Brasileira de Ci\^{e}ncias {\bf 87} 539-568 (2015).
 
@@
 application to the exponential and Weibull families.
-Biometrika {\bf 84}(3) 641-652 (1997).
-
-\item
-G.S. Mudholkar, D.K. Srivastava:
-The exponentiated Weibull family: a reanalysis of the bus-motor-failure data.
-Technometrics {\bf 37}(4) 436-445 (1995).
+Biometrika {\bf 84} 641-652 (1997).
+
+\item
+K. Zografos, N. Balakrishnan:
+On families of beta-and generalized gamma-generated distribution and
+associate inference.  Statistical Methodology {\bf 6} 344-362 (2009).
+
+\item
+N. Eugene, C. Lee, F. Famoye:
+Beta-normal distribution and its applications.
+Communications in Statistics -- Theory and Methods {\bf 31} 497-512 (2002).
 
@@
 AdequacyModel: An R package for probability distributions and general purpose optimization.
-PloS one, {\bf 14}(8), e0221487 (2019).
+PloS one, {\bf 14}, e0221487 (2019).
 
@@
 R Core Team. R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL
-\url{https://www.R-project.org/} (2020).
-
-\item
-S. Nadarajah, G.M. Cordeiro, E.M.M. Ortega:
-Some general results for the beta-modified Weibull distribution.
-Journal of Statistical Computation and Simulation {\bf 81}(10) 1211-1232 (2011).
-
-\item
-S. Nadarajah, G.M. Cordeiro, E.M.M. Ortega:
-General results for the Kumaraswamy G distribution.
-Journal of Statistical Computation and Simulation {\bf 87}(7) 951-979 (2012).
-
-\item
-S. Nadarajah, A.K. Gupta:
-The exponentiated gamma distribution with application to drought data.
-Calcutta Statistical Association Bulletin {\bf 59}(1-2) 29-54 (2007).
-
-\item
-S. Nadarajah, F. Haghighi:
-An extension of the exponential distribution.
-Statistics {\bf 45}(6) 543-558 (2011).
-
-\item
-S. Nadarajah, S. Kotz:
-The exponentiated-type distributions.
-Acta Applicandae Mathematicae {\bf 92}(2) 97-111 (2006).
-
-\item
-M.D. Nichols, W.J. Padgett:
-A Bootstrap control chart for Weibull percentiles.
-Quality and Reliability Engineering International {\bf 22}(2) 141-151 (2006).
-
-\item
-F. Proschan:
-Theoretical explanation of observed decreasing failure rate.
-Technometrics {\bf 5}(3) 375-383 (1963).
-
-\item
-M.M. Risti\'{c}, N. Balakrishnan:
-The gamma-exponentiated exponential distribution.
-Journal of Statistical Computation and Simulation {\bf 82}(8) 1191-1206 (2012).
-
-\item
-E.W. Stacy: A Generalization of the Gamma Distribution. Annals of Mathematical Statistics {\bf 33}(3) 1187-1192 (1962).
-
-\item
-M.H. Tahir, S. Nadarajah:
-Parameter induction in continuous univariate distributions: Well-established G families.
-Anais da Academia Brasileira de Ci\^{e}ncias {\bf 87}(2) 539-568 (2015).
-
-\item
-K. Zografos, N. Balakrishnan:
-On families of beta-and generalized gamma-generated distribution and
-associate inference.  Statistical Methodology {\bf 6}(4) 344-362 (2009).
+\url{https://www.R-project.org/} (2022).
+
+\item 
+F. Famoye, C. Lee and O. Olumolade: The beta-Weibull distribution. Journal of Statistical Theory and Applications {\bf4} 121-136 (2005).
+
+\item G.M. Cordeiro, E. M. M. Ortega and S. Nadarajah: The Kumaraswamy Weibull distribution with application to failure data {\bf 347} \url{https://doi.org/10.1016/j.jfranklin.2010.06.010} (2010).
+
+\item 
+H. H. Ahmed, O. M. Bdair and M. Ahsanullah: On Marshall-Olkin Extended Weibull Distribution \textbf{16} 1-17 (2017).
+
+\item 
+G.
+S.
+Mudholkar and D.
+K.
+Srivastava: Exponentiated Weibull Family for Analyzing Bathtub Failure-Rate Data IEEE Transactions on Reliability \textbf{42} 299-302 \url{http://dx.doi.org/10.1109/24.229504} (1993)
+
+\item 
+G.
+M.
+Cordeiro, M.
+C.
+S.
+Lima, A.
+E.
+Gomes, C.
+Q.
+da Silva and E.
+M.
+M.
+Ortega: The gamma extended Weibull distribution Journal of Statistical Distributions and Applications Berlim \textbf{3} 1-19 (2016).
+
+\item 
+P.
+Oguntunde, O.
+Odetunmibi and A.
+O.
+Adejumo On the Exponentiated Generalized Weibull Distribution: A Generalization of the Weibull Distribution Indian Journal of Science and Technology \textbf{8} DOI: 10.17485/ijst/2015/v8i35/67611 (2015).
+
+\item C. J. P. Belisle: Convergence theorems for a class of simulated annealing algorithms on Rd J Applied Probability \textbf{29} 885-895 1992.
+
+\item
+W. Barreto-Souza, A.J. Lemonte, G.M. Cordeiro:
+General results for the Marshall and Olkin's family of distributions.
+Anais da Academia Brasileira de Ci\^{e}ncias {\bf 85} 3-21 (2013).
+
+\item
+F. Castellares, A.J. Lemonte:
+A new generalized Weibull distribution gene\-rated by gamma random variables.
+Journal of the Egyptian Mathematical Society {\bf 23} 382-390 (2015).
+
+\item
+Gradshteyn IS, Ryzhik IM: Table of Integrals, Series and Products. Sixth edition. San Diego: Academic Press (2000).
+
+%\item
+%A. Alzaatreh, F. Famoye, C. Lee:
+%A new method for generating families of continuous distributions.
+%Metron {\bf 71}(1) 63-79 (2013).
+
+%\item
+%Z.W. Birnbaum, S.C. Saunders:
+%A new family of life distributions.
+%Journal of Applied Probability {\bf 6}(2) 319-327 (1969).
+
+%\item
+%G.M. Cordeiro, M. de Castro:
+%A new family of generalized distributions.
+%Journal of Statistical Computation and Simulation {\bf 81}(7) 883-898 (2011).
+
+%\item
+%R.C. Gupta, R.D. Gupta, P.L. Gupta:
+%Modeling failure time data by Lehmann alternatives.
+%Communications in Statistics -- Theory and Methods {\bf 27}(4) 887-904 (1998).
+
+%\item
+%R.D. Gupta, D. Kundu:
+%Exponentiated exponential family: an alternative to gamma and Weibull distributions.
+%Biometrical Journal {\bf 43}(1) 117-130 (2001).
+
+%\item
+%P. Kumaraswamy:
+%Generalized probability density-function for double-bounded
+%random-processes. Journal of Hydrology {\bf 46}(1-2) 79-88 (1980).
+
+%\item
+%A.J. Lemonte, G.M. Cordeiro, G. Moreno-Arenas:
+%A new useful three-parameter extension of the exponential distribution.
+%Statistics {\bf 50}(2) 312-337 (2016).
+
+%\item
+%G.S. Mudholkar, D.K. Srivastava:
+%The exponentiated Weibull family: a reanalysis of the bus-motor-failure data.
+%Technometrics {\bf 37}(4) 436-445 (1995).
+
+%\item
+%S. Nadarajah, G.M. Cordeiro, E.M.M. Ortega:
+%Some general results for the beta-modified Weibull distribution.
+%Journal of Statistical Computation and Simulation {\bf 81}(10) 1211-1232 (2011).
+
+%\item
+%S. Nadarajah, G.M. Cordeiro, E.M.M. Ortega:
+%General results for the Kumaraswamy G distribution.
+%Journal of Statistical Computation and Simulation {\bf 87}(7) 951-979 (2012).
+
+%\item
+%S. Nadarajah, A.K. Gupta:
+%The exponentiated gamma distribution with application to drought data.
+%Calcutta Statistical Association Bulletin {\bf 59}(1-2) 29-54 (2007).
+
+%\item
+%S. Nadarajah, F. Haghighi:
+%An extension of the exponential distribution.
+%Statistics {\bf 45}(6) 543-558 (2011).
+
+%\item
+%S. Nadarajah, S. Kotz:
+%The exponentiated-type distributions.
+%Acta Applicandae Mathematicae {\bf 92}(2) 97-111 (2006).
+
+%\item
+%M.D. Nichols, W.J. Padgett:
+%A Bootstrap control chart for Weibull percentiles.
+%Quality and Reliability Engineering International {\bf 22}(2) 141-151 (2006).
+
+%\item
+%F. Proschan:
+%Theoretical explanation of observed decreasing failure rate.
+%Technometrics {\bf 5}(3) 375-383 (1963).
+
+%\item
+%M.M. Risti\'{c}, N. Balakrishnan:
+%The gamma-exponentiated exponential distribution.
+%Journal of Statistical Computation and Simulation {\bf 82}(8) 1191-1206 (2012).
+
+%\item
+%E.W. Stacy: A Generalization of the Gamma Distribution. Annals of Mathematical Statistics {\bf 33}(3) 1187-1192 (1962).
 

### 2022-06-17 paper/carta_resposta_segunda_rodada/letter_answers.tex
Ultimas modificações no paper

--- 2022-05-25 paper/letter_answers.tex
@@
 
+\textbf{EDITOR}:
+
+1 -  Just in case, check if you have used current "RevStat LaTeX Macros" (\url{https://www.ine.pt/revstat/late.html}) and followed scrupulously "Instructions to authors" (\url{https://www.ine.pt/revstat/info.html}).
+
+\emph{Response}: {\color{red} Yes, we are using the current \LaTeX\, macro provided in the links}.
+
+2 - Remove line numbering and change all color text/comment to black.
+
+\emph{Response}:  {\color{red} Done}.
+
+3 - Review the format of the reference list, especially for volume, issue, page, and year.
+
+\emph{Response}:  {\color{red} Done}.
+
 \textbf{REVIEW I}:
 
-1 -- The equality \(h(x)=f(x)/(1-F(x))\) is a well known relation
-between hazard, density and survival functions.
-It is not a definition of density or risk functions.
-Therefore, in page 3, line 12, the part of the sentence ``defined by \(h(x)=f(x)/(1-F(x))\)'' should be omitted.
+1 - I just recommend correcting the expression (3.1) because, as I pointed out before, I think where it is $\lambda^\gamma\sum_{i=1}^n \log(x_i)$, should be $\lambda^\gamma\sum_{i=1}^n x_i^\gamma$.
 
-\textcolor{red}{Thank you. Done}.
-
-\emph{Response}:
-
-2 -- The expression (3.1) in page 6 corresponds to the log-likelihood of the MO-\(\Gamma\)-\(G\) distribution, 
-thus considering a Weibull distribution
-for \(G\) (although there is an error in the last sum 
-of line 1), not a general distribution with a \(\eta\) 
-vector of parameters. Therefore, the text or the expression 
-should be written accordingly.
-
-\emph{Response}:
-
-3 -- It is not clear why it is considered the Weibull distribution (for \(G\)) in Figure 1, eventually in expression (3.1) and in 
-the applications, whereas for the simulations it is chosen the 
-Dagum distribution. These choices should be clarified.
-
-\emph{Response}:
-\textcolor{red}{Indeed, the way in which the application section was introduced suggests that an attempt was made to fit the $G\sim Weibull$ model as a suitable distribution to the current datasets.
-In order to remove some ambiguity, we opted to extend the simulation studies, where we now include the $G\sim Weibull$ in the simulations.}
-
-4 -- As the Dagum distribution is used in the simulations, the generated PDF should also be in Table 1.
-
-\emph{Response}:
-\textcolor{red}{Thank you for pointing that out. The Dagum distribution was now included in Table 1.}
-
-5 -- As the \texttt{goodness.fit} function gives several statistics, the authors should justify why they only chose the Anderson Darling and Cram\'er-von Mises statistics.
-
-\emph{Response}:
-\textcolor{red}{The use of the Anderson-Darling  $A^*$ and Cram\'er-von Mises $W^*$  statistics, corrected by Chen and Balakrishnan, in the paper entitled ``A General Purpose Approximate Goodness-of-Fit Test'' (see   \url{https://www.tandfonline.com/doi/abs/10.1080/00224065.1995.11979578}) is indicated for comparing mo\-dels that are not necessarily embedded.
-Hence, considering the statistics returned by the \texttt{goodness.fit} function and the distributions compared, we understand that these statistics are the most suitable ones for
-the comparisons.}
-
-\textcolor{red}{The \textbf{AdequacyModel} package was developed 
-by one of the authors of this paper and it was published at   \url{https://journals .plos.org/plosone/article?id=10.1371/journal.pone.0221487}. 
-A code inspection of the \texttt{goodness.fit} function can be done by looking at the link   \href{https://github.com/prdm0/AdequacyModel/blob/master/R/goodness.fit.R}{link} on GitHub, where it is hosted the development versioning of the package.}
-
-\emph{Minor points:}
-
-1 -- page 1, line 8 of Section 1, correct for ``vector''.
-
-\emph{Response}: \textcolor{red}{Done.}
-
-2 -- page 2: confirm the expressions of \(Q_{MO-G}(u)\) (line 9) and
-\(W\) (line22).
-
-\emph{Response}: \textcolor{red}{Done.}
-
-3 -- page 2, line -4 of Section 1, correct for ``are''.
-
-\emph{Response}: \textcolor{red}{Done.}
-
-4 -- page 3, line 4, where it is written ``gamma density unit scale and shape \(a>0\),'' I suggest replacing it by ``gamma density with unit scale parameter and shape parameter \(a>0\),''.
-
-\emph{Response}: \textcolor{red}{Done.}
-
-5 -- page 3, \(3^{rd}\) paragraph, replace ``Table 2'' by ``Table 1''.
-
-\emph{Response}: \textcolor{red}{Done.}
-
-6 -- page 3, line-8, correct for ``(0,1)''.
-
-\emph{Response}: \textcolor{red}{Done.}
-
-7 -- Figure 1: I suggest to change the lines to different types (even letting the colours as they are) so as to enable the interpretation in a black and white print.
-Also, the letters assigned to the parameters must agree with those in Table 1 (and, eventually, with those in expression (3.1)).
-
-\emph{Response}:
-\textcolor{red}{Thanks a lot for the suggestion. All changes have been made. In fact, in a black and white print, solid lines will not help to differentiate the graphics.}
-
-8 -- page 3, lines-8,-7, where it is written ``of the baseline \(Q_F\) \(Q_G(.)\).'' I suggest replacing it by ``of the \(Q_F\) of the baseline distribution \(G\), \(Q_G(.).\)''.
-
-\emph{Response}: \textcolor{red}{Done.}
-
-9 -- page 3, line-6, correct for ``(1.1) and''.
-
-\emph{Response}:
-
-10 -- page 7: the label of the table should be on the top, like the rest of the tables.
-
-\emph{Response}: \textcolor{red}{Done.}
-
-11 -- page 11, line 4, correct for ``distribution''.
-
-\emph{Response}: \textcolor{red}{Done.}
-
-12 -- In expressions (6.4) and (6.6), try to improve the output as the reference numbers are to close to the formulas.
-
-\emph{Response}: \textcolor{red}{Done.}
-
-13 -- I suggest to make the labels of Figure 1 and of tables in \LaTeX, not in R.
-
-\emph{Response}:
-\textcolor{red}{Thanks for the suggestion. The change suggestion has been implemented.}
-
-14 -- The references ``R Core Team. \ldots{}'' and ``Rizzo, \ldots{}'' are in the wrong order.
-
-\emph{Response}:
+\emph{Response}: {\color{red} Done}.
 
@@
 
-1 - The article is written in an overly summarized form and is sometimes unattractive to the reader of any journal.
-That alone could lead to your rejection.
-In addition, I do suggest reviewing the use of English carefully, and considerable rewording and pruning to make the paper more concise and precise.
+1 - Although I still have some doubt related to my second remark, in fact the revised article got better. So I will not point out more issues.
 
-\emph{Response}:
-
-\textcolor{red}{We have improved the English language of the article in all sections.}
-
-2 - When I see a new paper about a new distribution, I wonder if it is due to any interesting properties or it arises naturally in some
-observable process like natural phenomena. I would like to see these
-arguments defended more clearly in the article by the authors. Could you do that?
-
-\emph{Response}:
-
-\textcolor{red}{The Marshall and Olkin-G and Gamma-G generators, each with one more parameter, are often used to build new distributions.
-We empirically show through two real datasets that by combining these two generators, we obtain a new family of distributions that is better than two families widely used in the literature: beta and Kumarawamy (each one of the three with two parameters).
-In fact, the ``beta-G family of distributions" has over 3100 citations on google, whereas the ``Kumaraswamy-G family of distributions" has over 4500 citations  up to this date (May, 2022).
-Further, the properties of the proposed family are obtained similarly from the other two families using exponentiated distributions.}
-
-3 - The bibliography does not have many recent publications such as
-Martinez-Florez et al. (2020) and Magalhaes et al.~(2020). I also
-suggest authors to create the state-of-art related to this topic in the first section that definitively needs to be improved.
-
-\emph{Response}:
-
-4 - I expect to see more detailed discussion in the simulation study and real data analysis. Could you revise these sections, including the conclusion section that is actually weak?
-
-5 - Suggestions: (i) Rewrite the paper title since the current one is nothing enlightening.
-How about naming the proposed distribution?.
-(ii) Place section 6 (properties) before section 4 (simulation).
-(iii) Reorganize the presentation of the tables.
-(iv) Put the simulation code in Supplementary material.
-
-\emph{Response}:
-
-\begin{itemize}
-\item
-  \begin{enumerate}
-  \def\labelenumi{(\roman{enumi})}
-  \tightlist
-  \item
-    \textcolor{red}{ Really, the title of the paper was no good.
-We changed to \textbf{Marshall and Olkin-Gamma-G family of distributions: properties and applications}.
-We believe that the title now clarifies the paper's proposal better.
-It is worth mentioning that the new name is consistent with the sequential application of the MO family to the baseline Gamma-G.}
-  \end{enumerate}
-\item
-  \begin{enumerate}
-  \def\labelenumi{(\roman{enumi})}
-  \setcounter{enumi}{1}
-  \tightlist
-  \item
-    \textcolor{red}{Done. Thanks for the suggestion.}
-  \end{enumerate}
-\item
-  \begin{enumerate}
-  \def\labelenumi{(\roman{enumi})}
-  \setcounter{enumi}{2}
-  \tightlist
-  \item
-    \textcolor{red}{Thanks for this point. The presentation of the tables was reorganized.}
-  \end{enumerate}
-\item
-  \begin{enumerate}
-  \def\labelenumi{(\roman{enumi})}
-  \setcounter{enumi}{3}
-  \tightlist
-  \item
-    \textcolor{red}{Thanks for the suggestion.
-We chose to put the code for the simulations in a repository on GitHub.
-Thus, we considerably reduced the number of pages in the article and made it easier for readers of the material to reuse the code.
-With the code on GitHub it is also possible to verify the implementation and validate the simulations obtained.
-To access the codes, see the link
-    \url{https://github.com/prdm0/MOGG/tree/master/code/simulations}}.
-  \end{enumerate}
-\end{itemize}
+\emph{Response}:  {\color{red} Thank you very much for your contributions}.
 

### 2022-06-17 paper/paper.tex
Ultimas modificações no paper

@@
 
+\usepackage{hyperref}
+\hypersetup{
+	pdftoolbar=true,        % show Acrobat’s toolbar?
+	pdfmenubar=true,        % show Acrobat’s menu?
+	pdffitwindow=true,     % window fit to page when opened
+	pdfstartview={FitH},    % fits the width of the page to the window
+	pdftitle={title},    % title
+	pdfauthor={Salvatore Mazzarino},     % author
+	pdfsubject={Subject},   % subject of the document
+	pdfcreator={Salvatore Mazzarino},   % creator of the document
+	pdfproducer={Salvatore Mazzarino}, % producer of the document
+	pdfkeywords={Green Networking} {Mobile Cloud} {Network Coding} {Energy}, % list of keywords
+	pdfnewwindow=true,      % links in new window
+	colorlinks=true,       % false: boxed links; true: colored links
+	linkcolor=blue,          % color of internal links (change box color with linkbordercolor)
+	citecolor=blue,        % color of links to bibliography
+	filecolor=magenta,      % color of file links
+	urlcolor=magenta           % color of external links
+}
 \newcommand{\etn}{{\mbox{\boldmath $\eta$}}} 
@@
 \vspace{1.5cm}
-\title{\color{red}{The Marshall and Olkin-G and Gamma-G family of distributions: properties and applications
-	%\footnote{The opinions expressed in this text are those of the authors and do not necessarily reflect the views of any organization.}
-}}
+\title{The Marshall and Olkin-G and Gamma-G family of distributions: properties and applications}
+
 \renewcommand{\titleheading}
@@
         Pernambuco, Recife, Brazil
-		\ (maria@de.ufpe.br)}
+        \href{maria@de.ufpe.br}{maria@de.ufpe.br}}
 	\\
@@
 		Pernambuco, Recife, Brazil
-		\ (gauss@de.ufpe.br)}
+		\href{gauss@de.ufpe.br}{gauss@de.ufpe.br}}
 	\\
@@
 		Paraíba, João Pessoa, Brazil
-		\ (pedro.rafael.marinho@gmail.com)}
+		\href{pedro.rafael.marinho@gmail.com}{pedro.rafael.marinho@gmail.com}}
 }
@@
 \modulolinenumbers[1]
-\linenumbers
+%\linenumbers
 %%%%%%%%%%%%%%%%%%%%%%%%%% alteracao: Datas %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\textcolor{red}{The advances in the field of Data Science requires the search for new fa\-milies of distributions that adequately model real data has been increasing steadily in the last years.
+The advances in the field of Data Science requires the search for new fa\-milies of distributions that adequately model real data has been increasing steadily in the last years.
 The construction of different generation methods and even generators of families has made it difficult to compare new proposals.
-In the midst of a huge set of existing families in the literature of new distributions, to find a proposal that is in fact an excellent competitor when compared to other existing ones, in terms of adjustment to real data sets and also that does not present estimation problems, is a major challenge.}
-
-\textcolor{red}{The classes of distributions in the early 1980s were based on the simple idea of adding parameters to a baseline distribution.} The mechanism by adding shape parameters to a baseline distribution has proved to be useful to make the
-generated distributions more flexible especially for studying 
-tail properties than existing ones and for improving their goodness-of-fit statistics to real data. Many special 
-distributions in these families are discussed by Tahir and Nadarajah (2015).
-
-\textcolor{red}{The addition of parameters in the construction of new distributions/families was improved by the inclusion of mathematical functions known in the literature, such as beta and gamma functions, for example, which produce new generators
-with more flexible properties than their baselines. 
-Two well-known examples are the beta-G (Eugene et al., 2002) 
-and gamma-G (Zografos and Balakrishnan, 2009) generators.}
-
-\textcolor{red}{However, the inclusion of such functions for generating new families brought, in some cases, problems for parameter estimation.
-So, despite the fit being more suitable for some types of data and, therefore, having a superior performance when compared to other generators, the estimation process can
-often be a problem.}
-
-\textcolor{red}{In this context, this work presents a new family obtained by composing a very competitive class in the literature with another class that has the gamma function in its structure.}
-
-Let $G(x)$ be the cumulative distribution function (CDF) of a
-baseline distribution and $g(x)=dG(x)/dx$ be the corresponding  probability density function (PDF) depending on a
-parameter vector $\eta$. A generalized family is presented
-with two extra shape parameters by transforming the CDF $G(x)$
-according to two sequential important classes. 
-These classes, \textcolor{red}{called Marshall and Olkin-G
-and Gamma-G}, are important for modeling data in several areas,  \textcolor{red}{and they are reviewed below}.
-
-The CDF of the Marshall and Olkin's (1997) ($\text{MO-G}$) 
+In the midst of a huge set of existing families in the literature of new distributions, to find a proposal that is in fact an excellent competitor when compared to other existing ones, in terms of adjustment to real data sets and also that does not present estimation problems, is a major challenge.
+
+The classes of distributions in the early 1980s were based on the simple idea of adding parameters to a baseline distribution.
+The mechanism by adding shape parameters to a baseline distribution has proved to be useful to make the
+generated distributions more flexible especially for studying  tail properties than existing ones and for improving their goodness-of-fit statistics to real data.
+Many special  distributions in these families are discussed by Tahir and Nadarajah (2015) \cite{Tahir}.
+
+The addition of parameters in the construction of new distributions/families was improved by the inclusion of mathematical functions known in the literature, such as beta and gamma functions, for example, which produce new generators with more flexible properties than their baselines.
+Two well-known examples are the beta-G (Eugene et al., 2002)  \cite{Eugene} and gamma-G (Zografos and Balakrishnan, 2009) \cite{Zografos} generators.
+
+However, the inclusion of such functions for generating new families brought, in some cases, problems for parameter estimation.
+So, despite the fit being more suitable for some types of data and, therefore, having a superior performance when compared to other generators, the estimation process can  often be a problem.
+
+In this context, this work presents a new family obtained by composing a very competitive class in the literature with another class that has the gamma function in its structure.
+
+Let $G(x)$ be the cumulative distribution function (CDF) of a baseline distribution and $g(x)=dG(x)/dx$ be the corresponding  probability density function (PDF) depending on a parameter vector $\eta$.
+A generalized family is presented with two extra shape parameters by transforming the CDF $G(x)$ according to two sequential important classes.
+These classes, called Marshall and Olkin-G and Gamma-G, are important for modeling data in several areas,  and they are reviewed below.
+
+The CDF of the Marshall and Olkin's (1997) \cite{Marshall} ($\text{MO-G}$) 
 class (for $\theta>0$) is
@@
 
-Tahir and Nadarajah (2015, Table 2) presented thirty 
-distributions belonging to this family. It is easily generated 
-from the baseline quantile function (QF) by
-$Q_{\text{MO-G}}(u)=Q_{G}\left(\theta u / \left[\theta u+1-u\right]\right)$ for $u\in(0,1)$.
+Tahir and Nadarajah (2015, Table 2) \cite{Tahir} presented thirty  distributions belonging to this family.
+It is easily generated  from the baseline quantile function (QF) by $Q_{\text{MO-G}}(u)=Q_{G}\left(\theta u / \left[\theta u+1-u\right]\right)$ for $u\in(0,1)$.
 
@@
 
-The CDF of the gamma-G ($\Gamma$-G) class (Zografos and Balakrishnan, 2009) is
+The CDF of the gamma-G ($\Gamma$-G) class (Zografos and Balakrishnan, 2009) \cite{Zografos}  is
 \begin{eqnarray}\label{CDF_Ga}
@@
 
-The MOGa-G family can be fitted to real data using the {\bf AdequacyModel} package ({\color{red}Marinho et al., 2019}) 
-in the {\sf R} software. This packa\-ge does not require to 
-define the log-likelihood function, and it computes the MLEs, 
-their standard errors (SEs), and the formal statistics defined 
-in Section \ref{applications}. It is only necessary to provide the
-PDF and CDF of the distribution to be fitted to a data set.
-
-For example, if $x_i$ is one observation from (\ref{PDF_MO-Gamma-G}) and $\etn$ is a $q$-parameter vector specifying $G(\cdot)$ \textcolor{red}{as the Weibull CDF}, the log-likelihood function for $\boldsymbol{\theta}^\top=(a,\theta,\etn^\top)$ from $n$ observations can be expressed as
+The MOGa-G family can be fitted to real data using the {\bf AdequacyModel} package (Marinho et al., 2019)  \cite{Marinho} in the {\sf R} software.
+This packa\-ge does not require to  define the log-likelihood function, and it computes the MLEs,  their standard errors (SEs), and the formal statistics defined  in Section \ref{applications}.
+It is only necessary to provide the PDF and CDF of the distribution to be fitted to a data set.
+
+For example, if $x_i$ is one observation from (\ref{PDF_MO-Gamma-G}) and $\etn$ is a $q$-parameter vector specifying $G(\cdot)$ as the Weibull CDF, the log-likelihood function for $\boldsymbol{\theta}^\top=(a,\theta,\etn^\top)$ from $n$ observations can be expressed as
 \begin{align}\label{loglik}
-\ell (\boldsymbol{\theta})=&\,n\log (\theta)+n\log(\gamma)+n\, a\, \gamma \log(\lambda)+(a\gamma-1)\sum_{i=1}^n{\log(x_i)}-\lambda^\gamma\sum_{i=1}^n{\log(x_i)}\nonumber \\ &
+\ell (\boldsymbol{\theta})=&\,n\log (\theta)+n\log(\gamma)+n\, a\, \gamma \log(\lambda)+(a\gamma-1)\sum_{i=1}^n{\log(x_i)}-\lambda^\gamma\sum_{i=1}^n x_i^\gamma\nonumber \\ &
 -n\log[\Gamma(a)]-2\sum_{i=1}^n{\log\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x_i)^\gamma]\}}.
@@
 
-The {\bf AdequacyModel} package of the programming language {\sf R} is used to obtain the MLEs, see R Core Team (2020). This library, created and maintained by one of the authors of this paper,
+The {\bf AdequacyModel} package of the programming language {\sf R} is used to obtain the MLEs, see R Core Team (2020) \cite{Team}.
+This library, created and maintained by one of the authors of this paper,
 is widely cited by several works in statistics, and serves as 
 a basis for other library implementations available on the Comprehensive R Archive Network (CRAN). By using the goodness.fit function, it is possible to provide an implementation  
-of (\ref {PDF_MO-Gamma-G}), and obtain $\ell(\cdot)$ by returning the MLEs, and some measures of adequacy of fit. Further details regarding this package can be obtained from Marinho et al. (2019).
+of (\ref {PDF_MO-Gamma-G}), and obtain $\ell(\cdot)$ by returning the MLEs, and some measures of adequacy of fit.
+Further details regarding this package can be obtained from Marinho et al.
+(2019) \cite{Marinho}.
 
@@
 
-{\color{red}Due to the probable absence of MLEs in closed-form for distributions belonging to the MOGa-G family, it is necessary to examine the precision of the estimates calculated numerically.
+Due to the probable absence of MLEs in closed-form for distributions belonging to the MOGa-G family, it is necessary to examine the precision of the estimates calculated numerically.
 
@@
 and 4.9688 hours for the MOGa-Weibull($\theta, a, \lambda, \gamma$) distribution. Tables \ref{tab:bias1} and  \ref{tab:bias2} 
-reveal that the average biases of the MLEs could be very small for $n>2,000$.}
+reveal that the average biases of the MLEs could be very small for $n>2,000$.
 
@@
 Thus, to minimize the computational cost of generating observations from $X$ through the generated observations from $Y$, $c$ is chosen as the lowest possible value to maximize the likelihood of acceptance.
-Further details of this method can be found in Rizzo (2019).
+Further details of this method can be found in Rizzo (2019) \cite{Rizzo}.
 
@@
 \centering
-\caption{\textcolor{red}{Average biases of the MLEs of the MOGa-Dagum($\theta, a, \alpha, \beta, p$) distri\-bu\-tion 
-calculated by the BFGS method from simulations.}}\label{tab:bias1}
+\caption{Average biases of the MLEs of the MOGa-Dagum($\theta, a, \alpha, \beta, p$) distri\-bu\-tion 
+calculated by the BFGS method from simulations.}\label{tab:bias1}
 	\begin{tabular}{rrrrrrr}
@@
 	\centering
-\caption{\textcolor{red}{Average biases of the MLEs of the MOGa-Weibull($\theta, a, \lambda, \gamma$) distribution calculated 
-by the BFGS method from simulations.}}\label{tab:bias2}
+\caption{Average biases of the MLEs of the MOGa-Weibull($\theta, a, \lambda, \gamma$) distribution calculated 
+by the BFGS method from simulations.}\label{tab:bias2}
 	\begin{tabular}{rrrrrr}
@@
 model with seven extended Weibull distributions: the 
-beta-Weibull ($\beta$-W) (Famoye et al., 2005), 
-Kumaraswamy Weibull (Kw-W) (Cordeiro et al., 2010), 
-Marshall-Olkin Weibull (MO-W) (Ahmed et al., 2017), 
-Marshall-Olkin Extended Weibull (MOE-W) (Cordeiro et al., 2019), exponentiated Weibull (exp-W) (Mudholkar and Srivastava, 1993), gamma Weibull ($\Gamma$-W) (Cordeiro et al., 2016), 
+beta-Weibull ($\beta$-W) (Famoye et al., 2005) \cite{Famoye}, 
+Kumaraswamy Weibull (Kw-W) (Cordeiro et al., 2010) \cite{Cordeiro_2010}, 
+Marshall-Olkin Weibull (MO-W) (Ahmed et al., 2017) \cite{Ahmad}, 
+Marshall-Olkin Extended Weibull (MOE-W) (Cordeiro et al., 2019) \cite{Cordeiro_2019}, exponentiated Weibull (exp-W) (Mudholkar and Srivastava, 1993) \cite{Mudholkar}, gamma Weibull ($\Gamma$-W) (Cordeiro et al., 2016) \cite{Cordeiro_2016},
 and exponentiated generalized Weibull 
-(EG-W) (Oguntunde et al., 2015) (with $a=1$). Some of 
+(EG-W) (Oguntunde et al., 2015) \cite{Oguntunde} (with $a=1$). Some of 
 these distributions are widely used in practice.
@@
 The {\bf AdequacyModel} package is used to fit the 
-previous distributions to two real data sets. The SANN method, which is a variant of simulated annealing algorithm (Belisle, 1992), is used here. The distributions are compared 
-via the Anderson Darling (A$^{*}$) and Cram\'er Von Mises (W$^{*}$) statistics reported in the {\tt goodness.fit} function.
+previous distributions to two real data sets. The SANN method, which is a variant of simulated annealing algorithm (Belisle, 1992) \cite{Belisle}, is used here. The distributions are compared 
+via the Anderson Darling (A$^{*}$) and Cram\'er von Mises (W$^{*}$) statistics reported in the {\tt goodness.fit} function.
 
@@
 where $FoodExpenditure_{food}$ is the random variable 
-corresponding to the household expenditures for food, and $\#(\cdot)$ indicates the number of observations on this variable. \textcolor{red}{The observations for the first data set are given bellow:\\
+corresponding to the household expenditures for food, and $\#(\cdot)$ indicates the number of observations on this variable. The observations for the first data set are given bellow:\\
   0.4210000, 0.4382105, 0.5721316, 0.1955526, 0.2758158, 0.3565263,
@@
   0.5050526, 0.6820526, 0.7587632, 0.4176053, 0.3923684, 0.2513158,
-  0.6070000, 0.3881842.}
-
-\textcolor{red}{Some descriptive statistics are reported in Table \ref{tabds}. The minimum value refers to a family of 3 people and income of 39,151, which does not represent the lowest family 
+  0.6070000, 0.3881842.
+
+Some descriptive statistics are reported in Table \ref{tabds}. The minimum value refers to a family of 3 people and income of 39,151, which does not represent the lowest family 
 income for the current data, as expected, occupying only the 
@@
 The maximum value corresponds to a family of 6 people with an income of 69,929, the second-largest number among the number of people per family in the group in question.
-Furthermore, we can note that the current data  present positive asymmetry and negative kurtosis.}
-
-\textcolor{red}{In addition, the standard deviation is relatively low.
+Furthermore, we can note that the current data  present positive asymmetry and negative kurtosis.
+
+In addition, the standard deviation is relatively low.
 Figure \ref{ttt} displays the total time on test (TTT) plot for the first data set, which shows that the failure function is decreasing.
 So, the MOGa-W distribution is appropriate to fit
-these data, since its  hazard function presents this shape (see,  Figure \ref{fig:hazard}).}
+these data, since its  hazard function presents this shape (see,  Figure \ref{fig:hazard}).
 
@@
 
-A data set collected in a pilot study about hypertension in the Dominican Republic in 1997 refers to the second application. The observations are the systolic blood pressure of persons who 
-came to medical clinics in several villages for a variety of complaints. 
-\textcolor{red}{The observations for the data set in question are:} 
+A data set collected in a pilot study about hypertension in the Dominican Republic in 1997 refers to the second application.
+The observations are the systolic blood pressure of persons who came to medical clinics in several villages for a variety of complaints.
+The observations for the data set in question are:
          150,
@@
 
-\textcolor{red}{Table \ref{tabds2} provides the descriptive statistics for the second data set.
+Table \ref{tabds2} provides the descriptive statistics for the second data set.
 Consi\-dering that the systolic blood pressure represents the highest number presented in the pressure measuring equipment, the maximum (236) found in this
-table should represent an individual with serious heart problems. This is due to the fact that the normal systolic pressure is 120.}
-
- \textcolor{red}{The minimum value (80) should be for 
- an individual who probably suffers from low blood pressure.
+table should represent an individual with serious heart problems. This is due to the fact that the normal systolic pressure is 120.
+
+The minimum value (80) should be for an individual who probably suffers from low blood pressure.
 Also note that the data set has positive skewness.
-This indicates that few people have high pressure values and, in this case, the mode is 120, which represents a good value for systolic pressure.}
-
- \textcolor{red}{Figure \ref{ttt2} provides the TTT plot 
- for the second clinic data, which shows that the hazard function is decreasing, thus supporting the MOGa-W model.}
+This indicates that few people have high pressure values and, in this case, the mode is 120, which represents a good value for systolic pressure.
+
+Figure \ref{ttt2} provides the TTT plot for the second clinic data, which shows that the hazard function is decreasing, thus supporting the MOGa-W model.
 
@@
 First, the CDF of the MO-G distribution (\ref{densityMO}) 
-admits the linear representation (Barreto-Souza et al., 2013)
+admits the linear representation (Barreto-Souza et al., 2013) \cite{Barreto-Souza}
 \begin{equation}
@@
 
-Second, the linear combination for the $\Gamma\text{-G}$ cumulative distribution (\ref{PDF_Ga}) follows from Castellares and 
-Lemonte (2015) as
+Second, the linear combination for the $\Gamma\text{-G}$ cumulative distribution (\ref{PDF_Ga}) follows from Castellares and Lemonte (2015) \cite{Castellares} as
 \begin{equation}\label{EXP33}
@@
 
-By inserting \eqref{EXP33} in Equation \eqref{EXP44} and via a result for a power series raised to a positive integer (Gradshteyn and
-Ryzhik, 2000), the expansion for the cdf of the MOGa-G distribution reduces to
+By inserting \eqref{EXP33} in Equation \eqref{EXP44} and via a result for a power series raised to a positive integer (Gradshteyn and Ryzhik, 2000) \cite{Gradshteyn}, the expansion for the cdf of the MOGa-G distribution reduces to
 \begin{align*}
@@
 
-\item
-M.H. Tahir, S. Nadarajah:
+\bibitem{Tahir} Tahir, M.
+H., Nadarajah, S.
+(2015).
 Parameter induction in continuous univariate distributions: Well-established G families.
-Anais da Academia Brasileira de Ci\^{e}ncias {\bf 87} 539-568 (2015).
-
-\item
-A.W. Marshall, I. Olkin:
-A new method for adding a parameter to a family of distributions with
-application to the exponential and Weibull families.
-Biometrika {\bf 84} 641-652 (1997).
-
-\item
-K. Zografos, N. Balakrishnan:
-On families of beta-and generalized gamma-generated distribution and
-associate inference.  Statistical Methodology {\bf 6} 344-362 (2009).
-
-\item
-N. Eugene, C. Lee, F. Famoye:
-Beta-normal distribution and its applications.
-Communications in Statistics -- Theory and Methods {\bf 31} 497-512 (2002).
-
-\item 
-P.
+\textit{Anais da Academia Brasileira de Ciências}, {\bf 87}, 539--568.
+
+\bibitem{Eugene} Eugene, N., Lee, C.,  Famoye, F. (2002). Beta-normal distribution and its applications. \textit{Communications in Statistics-Theory and methods}, {\bf 31}, 4, 497--512.
+
+\bibitem{Zografos} Zografos, K., Balakrishnan, N.
+(2009).
+On families of beta-and generalized gamma-generated distributions and associated inference.
+\textit{Statistical methodology}, {\bf 6}, 4, 344--362.
+
+\bibitem{Marshall} Marshall, A.
+W.,  Olkin, I.
+(1997).
+A new method for adding a parameter to a family of distributions with application to the exponential and Weibull families.
+\textit{Biometrika}, {\bf 84}, 3, 641--652.
+
+\bibitem{Marinho} Marinho, P.
 R.
-D.
-Marinho,  R.
-B.
-Silva,  M.
-Bourguignon, G.
+D., Silva, R.
+B., Bourguignon, M., Cordeiro, G.
+M.,  Nadarajah, S.
+(2019).
+AdequacyModel: An R package for probability distributions and general purpose optimization.
+\textit{PloS one}, {\bf 14}, 8, e0221487.
+
+\bibitem{Team} Team, R. C. (2022). R: A language and environment for statistical computing. \textit{R Foundation for Statistical Computing}, Vienna, Austria. \url{http://www. R-project. org/}.
+
+\bibitem{Rizzo} Rizzo, Maria L. (2019). Statistical computing with R. \textit{CRC Press}.
+
+\bibitem{Famoye} Famoye, F., Lee, C., Olumolade, O. (2005). The beta-Weibull distribution. \textit{Journal of Statistical Theory and Applications}, {\bf 4}, 2, 121--136.
+
+\bibitem{Cordeiro_2010} Cordeiro, G.
+M., Ortega, E.
+M., Nadarajah, S.
+(2010).
+The Kumaraswamy Weibull distribution with application to failure data.
+\textit{Journal of the Franklin Institute}, {\bf 347}, 8, 1399--1429.
+
+\bibitem{Ahmad} Ahmad, H. H., Bdair, O. M., Ahsanullah, M.,  Ahsanullah, M. (2017). On Marshall-Olkin Extended Weibull Distribution. \textit{J. Stat. Theory Appl.}, {\bf 16}, 1, 1--17.
+
+\bibitem{Cordeiro_2019} Cordeiro, G.
+M., Prataviera, F., do Carmo S Lima, M., Ortega, E.
 M.
-Cordeiro,  S.
-Nadarajah.
-AdequacyModel: An R package for probability distributions and general purpose optimization.
-PloS one, {\bf 14}, e0221487 (2019).
-
-\item
-R Core Team. R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL
-\url{https://www.R-project.org/} (2022).
-
-\item 
-F. Famoye, C. Lee and O. Olumolade: The beta-Weibull distribution. Journal of Statistical Theory and Applications {\bf4} 121-136 (2005).
-
-\item G.M. Cordeiro, E. M. M. Ortega and S. Nadarajah: The Kumaraswamy Weibull distribution with application to failure data {\bf 347} \url{https://doi.org/10.1016/j.jfranklin.2010.06.010} (2010).
-
-\item 
-H. H. Ahmed, O. M. Bdair and M. Ahsanullah: On Marshall-Olkin Extended Weibull Distribution \textbf{16} 1-17 (2017).
-
-\item 
-G.
-S.
-Mudholkar and D.
-K.
-Srivastava: Exponentiated Weibull Family for Analyzing Bathtub Failure-Rate Data IEEE Transactions on Reliability \textbf{42} 299-302 \url{http://dx.doi.org/10.1109/24.229504} (1993)
-
-\item 
-G.
+(2019).
+The Marshall-Olkin extended flexible Weibull regression model for censored lifetime data.
+\textit{Model Assisted Statistics and Applications}, {\bf 14}, 1, 1--17.
+
+\bibitem{Mudholkar} Mudholkar, G. S., Srivastava, D. K. (1993). Exponentiated Weibull family for analyzing bathtub failure-rate data. \textit{IEEE transactions on reliability}, {\bf 42}, 2, 299--302.
+
+\bibitem{Cordeiro_2016} Cordeiro, G.
+M., Maria do Carmo, S.
+L., Gomes, A.
+E., da-Silva, C.
+Q.,  Ortega, E.
 M.
-Cordeiro, M.
-C.
-S.
-Lima, A.
-E.
-Gomes, C.
-Q.
-da Silva and E.
+(2016).
+The gamma extended Weibull distribution.
+\textit{Journal of Statistical Distributions and Applications}, {\bf 3}, 1, 1--19.
+
+\bibitem{Oguntunde} Oguntunde, P.
+E., Odetunmibi, O.
+A., Adejumo, A.
+O.
+(2015).
+On the exponentiated generalized Weibull distribution: A generalization of the Weibull distribution.
+\textit{Indian Journal of Science and Technology}, {\bf 8}, 35, 1--7.
+
+\bibitem{Belisle} Bélisle, C. J. (1992). Convergence theorems for a class of simulated annealing algorithms on Rd. \textit{Journal of Applied Probability}, {\bf 29}, 4, 885--895.
+
+\bibitem{Barreto-Souza} Barreto-Souza, W., Lemonte, A.
+J.,  Cordeiro, G.
 M.
-M.
-Ortega: The gamma extended Weibull distribution Journal of Statistical Distributions and Applications Berlim \textbf{3} 1-19 (2016).
-
-\item 
-P.
-Oguntunde, O.
-Odetunmibi and A.
-O.
-Adejumo On the Exponentiated Generalized Weibull Distribution: A Generalization of the Weibull Distribution Indian Journal of Science and Technology \textbf{8} DOI: 10.17485/ijst/2015/v8i35/67611 (2015).
-
-\item C. J. P. Belisle: Convergence theorems for a class of simulated annealing algorithms on Rd J Applied Probability \textbf{29} 885-895 1992.
-
-\item
-W. Barreto-Souza, A.J. Lemonte, G.M. Cordeiro:
+(2013).
 General results for the Marshall and Olkin's family of distributions.
-Anais da Academia Brasileira de Ci\^{e}ncias {\bf 85} 3-21 (2013).
-
-\item
-F. Castellares, A.J. Lemonte:
-A new generalized Weibull distribution gene\-rated by gamma random variables.
-Journal of the Egyptian Mathematical Society {\bf 23} 382-390 (2015).
-
-\item
-Gradshteyn IS, Ryzhik IM: Table of Integrals, Series and Products. Sixth edition. San Diego: Academic Press (2000).
-
-%\item
-%A. Alzaatreh, F. Famoye, C. Lee:
-%A new method for generating families of continuous distributions.
-%Metron {\bf 71}(1) 63-79 (2013).
-
-%\item
-%Z.W. Birnbaum, S.C. Saunders:
-%A new family of life distributions.
-%Journal of Applied Probability {\bf 6}(2) 319-327 (1969).
-
-%\item
-%G.M. Cordeiro, M. de Castro:
-%A new family of generalized distributions.
-%Journal of Statistical Computation and Simulation {\bf 81}(7) 883-898 (2011).
-
-%\item
-%R.C. Gupta, R.D. Gupta, P.L. Gupta:
-%Modeling failure time data by Lehmann alternatives.
-%Communications in Statistics -- Theory and Methods {\bf 27}(4) 887-904 (1998).
-
-%\item
-%R.D. Gupta, D. Kundu:
-%Exponentiated exponential family: an alternative to gamma and Weibull distributions.
-%Biometrical Journal {\bf 43}(1) 117-130 (2001).
-
-%\item
-%P. Kumaraswamy:
-%Generalized probability density-function for double-bounded
-%random-processes. Journal of Hydrology {\bf 46}(1-2) 79-88 (1980).
-
-%\item
-%A.J. Lemonte, G.M. Cordeiro, G. Moreno-Arenas:
-%A new useful three-parameter extension of the exponential distribution.
-%Statistics {\bf 50}(2) 312-337 (2016).
-
-%\item
-%G.S. Mudholkar, D.K. Srivastava:
-%The exponentiated Weibull family: a reanalysis of the bus-motor-failure data.
-%Technometrics {\bf 37}(4) 436-445 (1995).
-
-%\item
-%S. Nadarajah, G.M. Cordeiro, E.M.M. Ortega:
-%Some general results for the beta-modified Weibull distribution.
-%Journal of Statistical Computation and Simulation {\bf 81}(10) 1211-1232 (2011).
-
-%\item
-%S. Nadarajah, G.M. Cordeiro, E.M.M. Ortega:
-%General results for the Kumaraswamy G distribution.
-%Journal of Statistical Computation and Simulation {\bf 87}(7) 951-979 (2012).
-
-%\item
-%S. Nadarajah, A.K. Gupta:
-%The exponentiated gamma distribution with application to drought data.
-%Calcutta Statistical Association Bulletin {\bf 59}(1-2) 29-54 (2007).
-
-%\item
-%S. Nadarajah, F. Haghighi:
-%An extension of the exponential distribution.
-%Statistics {\bf 45}(6) 543-558 (2011).
-
-%\item
-%S. Nadarajah, S. Kotz:
-%The exponentiated-type distributions.
-%Acta Applicandae Mathematicae {\bf 92}(2) 97-111 (2006).
-
-%\item
-%M.D. Nichols, W.J. Padgett:
-%A Bootstrap control chart for Weibull percentiles.
-%Quality and Reliability Engineering International {\bf 22}(2) 141-151 (2006).
-
-%\item
-%F. Proschan:
-%Theoretical explanation of observed decreasing failure rate.
-%Technometrics {\bf 5}(3) 375-383 (1963).
-
-%\item
-%M.M. Risti\'{c}, N. Balakrishnan:
-%The gamma-exponentiated exponential distribution.
-%Journal of Statistical Computation and Simulation {\bf 82}(8) 1191-1206 (2012).
-
-%\item
-%E.W. Stacy: A Generalization of the Gamma Distribution. Annals of Mathematical Statistics {\bf 33}(3) 1187-1192 (1962).
-
-\item 
-Rizzo, Maria L. Statistical computing with R. CRC Press (2019).
-
+\textit{Anais da Academia Brasileira de Ciências}, {\bf 85}, 1, 3--21.
+
+\bibitem{Castellares} Castellares, F., Lemonte, A.
+J.
+(2015).
+A new generalized Weibull distribution generated by gamma random variables.
+\textit{Journal of the Egyptian Mathematical Society}, {\bf 23}, 2, 382--390.
+
+\bibitem{Gradshteyn} Gradshteyn, I. S.,  Ryzhik, I. M. (2014). Table of integrals, series, and products. \textit{Academic press}.
 \end{thebibliography}
